---
title: "Tracing New Filtered NWs"
author: "Greg Cary"
date: "`r Sys.Date()`"
output: 
  html_document: 
    fig_width: 5
    fig_height: 4
  html_notebook:
    code_folding: hide
    theme: spacelab
    css: style.css
    toc: true
    toc_float: true
---
# Setup

```{r setup}
# Package names
packages <- c(
  # 'paxtoolsr','org.Hs.eg.db','HotNetvieweR','clusterProfiler', 
  'synapser','igraph','tidygraph','ggraph','tidyverse'
  )

# Load packages
invisible(lapply(packages, library, character.only = TRUE))

source('/projects/carter-lab/caryg/treatAD_biodomains/scripts/biodom_tally.R')
# source(paste0(here::here(),'/../biodom_enr.R'))
source('/projects/carter-lab/caryg/treatAD_biodomains/scripts/biodom_enr_plots.R')
source('/projects/carter-lab/caryg/treatAD_biodomains/scripts/annotate_enr_term_biodomains.R')

theme_set(theme_bw())
```

# Data
Grab relevant data from synapse, including:
1) Target Risk Scores ([syn25575156](https://www.synapse.org/#!Synapse:syn25575156){target="_blank"}) and Omics Scores ([syn22758536](https://www.synapse.org/#!Synapse:syn22758536){target="_blank"})  
2) Biodomain Definitions ([syn25428992](https://www.synapse.org/#!Synapse:syn25428992){target="_blank"})  
2) Risk-enriched Biodomain Terms ([syn45824995](https://www.synapse.org/#!Synapse:syn45824995){target="_blank"})
3) Base Network ([syn51110930](https://www.synapse.org/#!Synapse:syn51110930){target="_blank"})  
4) Synapse IDs of path-traced NW objects  
5) Synapse IDs of wKDA results 
6) CRISPRbrain simple phenotype screen data  

```{r}
synLogin()

# target risk scores
scores <- read_csv(
  synTableQuery('select * from syn25575156', includeRowIdAndRowVersion = F)$filepath
  , col_types = cols())
omics <- read_csv(
  synTableQuery('select * from syn22758536', includeRowIdAndRowVersion = F)$filepath
  , col_types = cols())

# biological domain annotations
biodom <- full_join(
  # biodomains
  readRDS(synGet('syn25428992')$path),
  # domain labels
  read_csv(synGet('syn26856828')$path, col_types = cols()),
  by = c('Biodomain'='domain')
) %>%
  mutate(Biodomain = case_when(Biodomain == 'none' ~ NA_character_, T ~ Biodomain))

# enriched biodomain terms
enr.bd <- read_csv( synGet('syn45824995')$path, col_types = cols() ) %>% 
  mutate(leadingEdge_genes = str_split(leadingEdge_genes, '\\|'))

# base network
base_net <- igraph::read_graph(synGet('syn51110930')$path, format = 'graphml') 

# specify directed edge types
directed_edge_types = c("catalysis-precedes",
                        "controls-expression-of",
                        "controls-phosphorylation-of",
                        "controls-state-change-of",
                        "controls-transport-of"
                        )

# read NW results dir on Synapse
nw.dirs <- map_dfr(
  synGetChildren('syn51117833')$asList() %>% 
    tibble(f = .) %>% unnest_wider(f) %>% 
    filter(name!='nanostring_induced_subgraph.graphml') %>% 
    pull(id),
  ~{ synGetChildren(  parent = .x  )$asList() %>% 
      tibble(f = .) %>% unnest_wider(f) %>% 
      filter(grepl('graphml', name)) %>% 
      mutate(
        bd = str_extract(name, '^(?<=[bdFiltered_]{0,1}).+(?=_[un]*directed)') %>% 
          str_remove_all('bdFiltered_') %>% str_replace_all('_',' '),
        bd.filt = if_else(grepl('bdFiltered',name),T,F),
        filt = str_extract(name, '(?<=_filt_).+(?=\\.graphml)'),
        dir = str_extract(name, '[un]*directed') 
        ) %>% 
      relocate(bd, bd.filt, filt, dir)
    }
)

# read KDA results dir on Synapse
kda.dirs <- map_dfr(
  synGetChildren('syn51117833')$asList() %>% 
    tibble(f = .) %>% unnest_wider(f) %>% 
    filter(name!='nanostring_induced_subgraph.graphml') %>% 
    pull(id),
  ~{ id = synGetChildren( parent = .x )$asList() %>% 
      tibble(f = .) %>% unnest_wider(f) %>% 
      filter(grepl('kda', name)) %>% pull(id)
  
     bd = synGet(.x)$properties$name

     synGetChildren(id)$asList() %>% 
       tibble(f = .) %>% unnest_wider(f) %>% 
       filter(grepl('results',name)) %>% 
       mutate(
          bd = bd %>% str_replace_all('_' ,' '),
          filt = str_extract(name, '(?<=_filt_).+(?=_addWeights)'),
          dir = str_extract(name, '[un]*directed'), 
          ef = str_extract(name, '(?<=_edgeFactor_)[0|1]')
          ) %>% 
        relocate(bd, filt, dir, ef)
    }
)

```

pre-filtered NWs    
```{r}
undir <- base_net

# filt node & edge
tmp <- igraph::delete_vertices(
  base_net,
  igraph::V(base_net)[ igraph::V(base_net)$brain_exp == 0 ]
)
undir_node_edge <- igraph::subgraph.edges(
  tmp,
  igraph::E(tmp)[ igraph::E(tmp)$n_edge_evidence > 1 ],
  delete.vertices = T 
)

# filt node
undir_node <- igraph::delete_vertices(
    base_net,
    igraph::V(base_net)[ igraph::V(base_net)$brain_exp == 0 ]
  )

# filt edge
undir_edge <- igraph::subgraph.edges(
    base_net,
    igraph::E(base_net)[ igraph::E(base_net)$n_edge_evidence > 1 ],
    delete.vertices = T 
  )

# dir
dir <- igraph::subgraph.edges( 
    base_net, 
    igraph::E(base_net)[ igraph::E(base_net)$directed == 1 ],
    delete.vertices = T 
  ) %>% 
    as.directed(mode = 'arbitrary')

# dir node edge
dir_node_edge <- igraph::subgraph.edges( 
    undir_node_edge, 
    igraph::E(undir_node_edge)[ igraph::E(undir_node_edge)$directed == 1 ],
    delete.vertices = T 
  ) %>% 
    as.directed(mode = 'arbitrary')

# dir node
dir_node <- igraph::subgraph.edges( 
    undir_node, 
    igraph::E(undir_node)[ igraph::E(undir_node)$directed == 1 ],
    delete.vertices = T 
  ) %>% 
    as.directed(mode = 'arbitrary')

# dir edge
dir_edge <- igraph::subgraph.edges( 
    undir_edge, 
    igraph::E(undir_edge)[ igraph::E(undir_edge)$directed == 1 ],
    delete.vertices = T 
  ) %>% 
    as.directed(mode = 'arbitrary')

```


CRISPRbrain phenotype data
```{r}
synLogin()

# CRISPRbrain data
syn.dir <- synGetChildren('syn51183357')$asList() %>% 
  tibble(f = .) %>% 
  unnest_wider(f)

# Simple Screens
simple <- map_dfr(
  syn.dir %>% with(which( !grepl('RNA|CROP',name) )),
  ~ { 
    id = syn.dir$id[.x]
    n = syn.dir$name[.x]
    synGet(id)$path %>% 
      read_csv( col_types = cols() ) %>% 
      mutate(cell = n %>% str_split_fixed(.,'-(?!M)', 2) %>% .[,1],
             mode = n %>% str_extract('CRISPR[ain]'),
             expt = n %>% str_remove_all('-CRISPR[ain].csv') %>% 
               str_split_fixed('-(?!M)',2) %>% .[,2] ) %>% 
      relocate(cell, mode, expt)
  }
  ) %>% 
  rename(pval = `P Value`, pheno = `Phenotype`, gene_score = `Gene Score`)

simple <- tibble(expt = simple$expt %>% unique() %>% sort(),
                 phenotype = c('Expansion (CD34 Staining)',
                                'Reactive Oxygen Species (CellRox Intensity)',
                                'Proliferation (CFSE Staining)',
                                'Survival (14 day)', 'Survival (21 day)', 'Survival (28 day)',
                                'Labile Iron (FeRhoNox Intensity)',
                                'Immune Activation (CD38 levels)',
                                'Lysosome Exocytosis (cell surface LAMP1), +IL1a +TNF +C1q',
                                'Lysosome Exocytosis (cell surface LAMP1), Vehicle',
                                'Peroxidized Lipids (Liperfluo intensity)',
                                'Lysosome (LysoTracker intensity)',
                                'Lysosome Mass or pH (LysoTracker staining), +IL1a +TNF +C1q',
                                'Lysosome Mass or pH (LysoTracker staining), Vehicle',
                                'Survival, no antioxidants',
                                'Phagocytosis (pHRodo-rat synaptosomes)',
                                'Phagocytosis (pHRodo-labeled synaptosomes), +IL1a +TNF +C1q',
                                'Phagocytosis (pHRodo-labeled synaptosomes), Vehicle',
                                'Survival, PSAP KO & no antioxidants',
                                'Survival, PSAP KO',
                                'Survival',
                                'Survival-Proliferation',
                                'Inflammatory activation (cell-surface VCAM1 levels), +IL1a +TNF +C1q')
                 ) %>% left_join(simple, . , by = 'expt')

# filter(cell %in% c('iAstrocyte','Glutamatergic Neuron','iTF-Microglia','iPSC')) # don't consider HSPC or T-cell
```

functions to read KDA results and plot sub-networks from identified key drivers
```{r}
read_kda_res <- function(ef0_synID, ef1_synID){
  bind_rows(
    read_tsv(synGet(ef0_synID)$path, col_types = cols()) %>% mutate(ef = 'ef0_fdr'),
    read_tsv(synGet(ef1_synID)$path, col_types = cols()) %>% mutate(ef = 'ef1_fdr')
  ) %>%
  mutate(FDR = -log10(FDR)) %>%
  pivot_wider(id_cols = c(MODULE, NODE, MEMBER), names_from = ef, values_from = FDR) %>%
  mutate(across(contains('_fdr'), ~ if_else(is.na(.x), 0, .x))) %>% 
  mutate(delta_fdr = ef1_fdr - ef0_fdr) %>% arrange(desc(delta_fdr))
}
plot_kd_subnet <- function(nw, kd, term) {
  
  vert_num <- match(kd, V(nw)$name)
  
  vert_neigh <- neighbors(nw, vert_num)
  
  term_num <- biodom %>%
    filter(GOterm_Name == term) %>%
    pull(symbol) %>% unlist() %>%
    match(., V(nw)$name) %>% .[!is.na(.)]
  
  g2 <- induced_subgraph(nw, c(vert_num, intersect(term_num, vert_neigh)))
  g3 <- induced_subgraph(nw, c(vert_num, term_num))
  
  cowplot::plot_grid(
    
    ggraph(g3, layout = 'linear', circular = TRUE) +
      geom_edge_arc(alpha = .3, color = 'grey75') +
      geom_node_point( shape = 21, color = "black", alpha = .3,
        aes(size = TargetRiskScore, fill = Pro_EffectScore, filter= .N()$name != kd)  )+
      geom_node_point( shape = 23, color = "black", alpha = .3,
        aes(size = TargetRiskScore, fill = Pro_EffectScore, filter = .N()$name == kd) )+
      geom_node_text(aes(label = name), size = 2) +
      coord_fixed() +
      scale_size_continuous( range = c(.5, 10), limits = c(0, 5), trans = 'exp')+
      scale_fill_gradient2(
        low = 'purple', mid = 'black', high = 'green', na.value = 'grey85',
        limits = c(-2.5,2.5) )+ #approx: range(omics$Pro_TE, na.rm = T)
      labs( title = 'All term genes in NW',
            subtitle = paste0('KD: ', kd, '\nTerm: ', term) )+
      theme_graph(background = 'white')
    ,
    ggraph(g2, layout = 'linear', circular = TRUE) +
            geom_edge_arc(alpha = .3, color = 'grey75') +
      geom_node_point( shape = 21, color = "black", alpha = .3,
        aes(size = TargetRiskScore, fill = Pro_EffectScore, filter= .N()$name != kd)  )+
      geom_node_point( shape = 23, color = "black", alpha = .3,
        aes(size = TargetRiskScore, fill = Pro_EffectScore, filter = .N()$name == kd) )+
      geom_node_text(aes(label = name), size = 2) +
      coord_fixed() +
      scale_size_continuous( range = c(.5, 10), limits = c(0, 5), trans = 'exp')+
      scale_fill_gradient2(
        low = 'purple', mid = 'black', high = 'green', na.value = 'grey85',
        limits = c(-2.5,2.5) )+ #approx: range(omics$Pro_TE, na.rm = T)
      labs( title = 'Term genes & KD neighbors in NW',
            subtitle = paste0('KD: ', kd, '\nTerm: ', term) )+
      theme_graph(background = 'white')
    ,
    ncol = 2
    
  )
}
```


The Biodomains with traced NW analyzed by wKDA include:  
1) APP Metabolism  [2]
2) Endolysosome [6] 
3) Tau Homeostasis [18]
== vv KDA results not yet complete vv ==
•) Immune Response [8] 
•) Lipid Metabolism [9]  
•) Synapse [17] 
•) Mitochondrial Metabolism [11]

Explore the effects of NW filters on traces & KDs for these sets:
• node & edge filtering effects
• direct edge filter before vs after trace
• nodes added by trace
• common vs unique nodes across BD
• KDA on full (i.e. not BD filtered) NW objects

# Biodom NW analyses
## Cross NW comparisions
```{r}
nw.dat = nw.dirs %>% 
  filter(bd.filt) %>% 
  select(bd:id) 

x = map_dfr(
  nw.dat$id,
  ~{
    nw = synGet(.x) %>% .$path %>% read_graph(., format = 'graphml' )
    tibble(
      nodes = V(nw) %>% names() %>% unique() %>% list(),
      edges = E(nw)$edge %>% unique() %>% list
    )
  }
)

nw.dat = bind_cols(nw.dat, x)

nw.dat$le_genes <- map(
  1:nrow(nw.dat),
  ~ enr.bd %>% 
  filter(
    Biodomain == nw.dat$bd[.x],
    padj < 0.01,
    NES > 1.7
  ) %>% 
  pull(leadingEdge_genes) %>% 
  unlist() %>% 
  unique()
)

nw.dat <- nw.dat %>% 
  rowwise() %>% 
  mutate(
    input_genes = case_when(
      (dir == 'undirected' & filt == 'none') ~ intersect( unlist(le_genes), names(V(undir)) ) %>% list(),
      (dir == 'undirected' & filt == 'node') ~ intersect( unlist(le_genes), names(V(undir_node)) ) %>% list(),
      (dir == 'undirected' & filt == 'edge') ~ intersect( unlist(le_genes), names(V(undir_edge)) ) %>% list(),
      (dir == 'undirected' & filt == 'node_edge') ~ intersect( unlist(le_genes), names(V(undir_node_edge)) ) %>% list(),
      
      (dir == 'directed' & filt == 'none') ~ intersect( unlist(le_genes), names(V(!! dir)) ) %>% list(),
      (dir == 'directed' & filt == 'node') ~ intersect( unlist(le_genes), names(V(dir_node)) ) %>% list(),
      (dir == 'directed' & filt == 'edge') ~ intersect( unlist(le_genes), names(V(dir_edge)) ) %>% list(),
      (dir == 'directed' & filt == 'node_edge') ~ intersect( unlist(le_genes), names(V(dir_node_edge)) ) %>% list(),
      T ~ list(NA_character_)
    )
  )

nw.dat$added_genes <- map(
  1:nrow(nw.dat),
  ~ setdiff( nw.dat$nodes[[.x]], nw.dat$input_genes[[.x]] ) 
)

# -common nodes
# V(nw) %>% names() %>% unique() %>% length()
# -common edges
# E(nw)$edge %>% head()
#  by filt, direction
```

### Input Overlap
LE genes
```{r fig.width=9, fig.height=6}

olap = map_dfr(
  unique('none'),
  ~{
    tmp <- nw.dat %>% 
      filter(dir == 'undirected', 
             filt == .x)
    
    olap <- crossing(nw1 = tmp$bd, nw2 = tmp$bd) %>% 
      group_by(nw1,nw2) %>% 
      mutate(.keep = 'all', 
             intersect = length(intersect(
               tmp %>% filter(bd == nw1) %>% pull(le_genes) %>% unlist(),
               tmp %>% filter(bd == nw2) %>% pull(le_genes) %>% unlist()
               ))
             ) %>% 
      ungroup() %>% group_by(nw1) %>% 
      mutate(.keep = 'all', pct_overlap = intersect / intersect[which(nw2 == nw1)]) %>% 
      ungroup() %>% 
      mutate(filt = .x)
  }
)


olap %>%
  mutate(
    filt = fct_relevel(filt, c('none','node','edge','node_edge')),
    nw1 = fct_relevel(nw1, 
                      nw.dat %>% select(bd, le_genes) %>% distinct() %>% mutate(len = length(unlist(le_genes))) %>% arrange(len) %>% pull(bd)
                      ),
    nw2 = fct_relevel(nw2, 
                      nw.dat %>% select(bd, le_genes) %>% distinct() %>% mutate(len = length(unlist(le_genes))) %>% arrange(desc(len)) %>% pull(bd)
                      )
  ) %>% 
  ggplot(., aes(x = nw2, y = nw1)) +
  geom_tile(aes(fill=pct_overlap)) + theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  # theme(axis.text.x = element_blank(), legend.position = 'bottom') +
  scale_fill_gradient2('% Total', low = 'white', high = '4a66ac', na.value = 'grey90') +
  # scale_x_discrete(position = "top") +
  geom_text(aes(label = intersect ), size = 2.5) +
  labs(x='',y='', title = 'Leading Edge Genes') 



```

input genes (overlap with base net)
```{r fig.width=9, fig.height=6}

olap = map_dfr(
  unique(nw.dat$filt),
  ~{
    tmp <- nw.dat %>% 
      filter(dir == 'undirected', 
             filt == .x)
    
    olap <- crossing(nw1 = tmp$bd, nw2 = tmp$bd) %>% 
      group_by(nw1,nw2) %>% 
      mutate(.keep = 'all', 
             intersect = length(intersect(
               tmp %>% filter(bd == nw1) %>% pull(input_genes) %>% unlist(),
               tmp %>% filter(bd == nw2) %>% pull(input_genes) %>% unlist()
               )),
               len_nw1 = tmp %>% filter(bd == nw1) %>% pull(input_genes) %>% unlist() %>% length(),
               len_nw2 = tmp %>% filter(bd == nw1) %>% pull(input_genes) %>% unlist() %>% length()
             ) %>% 
      ungroup() %>% group_by(nw1) %>% 
      mutate(.keep = 'all', pct_overlap = intersect / intersect[which(nw2 == nw1)]) %>% 
      ungroup() %>% 
      mutate(filt = .x)
  }
)

olap %>%
  mutate(
    filt = fct_relevel(filt, c('none','node','edge','node_edge')),
    nw1 = fct_relevel(nw1, olap %>% filter(filt == 'none') %>% select(nw1, len_nw1) %>% distinct() %>% arrange(len_nw1) %>% pull(nw1)),
    nw2 = fct_relevel(nw2, olap %>% filter(filt == 'none') %>% select(nw1, len_nw1) %>% distinct() %>% arrange(desc(len_nw1)) %>% pull(nw1))
  ) %>% 
  ggplot(., aes(x = nw2, y = nw1)) +
  geom_tile(aes(fill=pct_overlap)) + theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  # theme(axis.text.x = element_blank(), legend.position = 'bottom') +
  scale_fill_gradient2('% Total', low = 'white', high = '4a66ac', na.value = 'grey90') +
  # scale_x_discrete(position = "top") +
  geom_text(aes(label = intersect ), size = 2.5) +
  labs(x='',y='', title = 'input genes', subtitle = 'leading edge overlap with filtered base network nodes') + 
  facet_wrap(~filt)

```

input genes (overlap with base net)
```{r fig.width=9, fig.height=6}

olap = map_dfr(
  unique(nw.dat$filt),
  ~{
    tmp <- nw.dat %>% 
      filter(dir == 'directed', 
             filt == .x)
    
    olap <- crossing(nw1 = tmp$bd, nw2 = tmp$bd) %>% 
      group_by(nw1,nw2) %>% 
      mutate(.keep = 'all', 
             intersect = length(intersect(
               tmp %>% filter(bd == nw1) %>% pull(input_genes) %>% unlist(),
               tmp %>% filter(bd == nw2) %>% pull(input_genes) %>% unlist()
               )),
               len_nw1 = tmp %>% filter(bd == nw1) %>% pull(input_genes) %>% unlist() %>% length(),
               len_nw2 = tmp %>% filter(bd == nw1) %>% pull(input_genes) %>% unlist() %>% length()
             ) %>% 
      ungroup() %>% group_by(nw1) %>% 
      mutate(.keep = 'all', pct_overlap = intersect / intersect[which(nw2 == nw1)]) %>% 
      ungroup() %>% 
      mutate(filt = .x)
  }
)

olap %>%
  mutate(
    filt = fct_relevel(filt, c('none','node','edge','node_edge')),
    nw1 = fct_relevel(nw1, olap %>% filter(filt == 'none') %>% select(nw1, len_nw1) %>% distinct() %>% arrange(len_nw1) %>% pull(nw1)),
    nw2 = fct_relevel(nw2, olap %>% filter(filt == 'none') %>% select(nw1, len_nw1) %>% distinct() %>% arrange(desc(len_nw1)) %>% pull(nw1))
  ) %>% 
  ggplot(., aes(x = nw2, y = nw1)) +
  geom_tile(aes(fill=pct_overlap)) + theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  theme(axis.text.x = element_blank(), legend.position = 'bottom') +
  scale_fill_gradient2('% Total', low = 'white', high = '4a66ac', na.value = 'grey90') +
  # scale_x_discrete(position = "top") +
  geom_text(aes(label = intersect ), size = 2.5) +
  labs(x='',y='', title = 'input genes', subtitle = 'leading edge overlap with *DIRECTED* 
       filtered base network nodes') + 
  facet_wrap(~filt)

```

### Common Nodes
undirected
```{r fig.width=9, fig.height=6}

olap = map_dfr(
  unique(nw.dat$filt),
  ~{
    tmp <- nw.dat %>% 
      filter(dir == 'undirected', 
             filt == .x)
    
    olap <- crossing(nw1 = tmp$bd, nw2 = tmp$bd) %>% 
      group_by(nw1,nw2) %>% 
      mutate(.keep = 'all', 
             intersect = length(intersect(
               tmp %>% filter(bd == nw1) %>% pull(nodes) %>% unlist(),
               tmp %>% filter(bd == nw2) %>% pull(nodes) %>% unlist()
               ))
             ) %>% 
      ungroup() %>% group_by(nw1) %>% 
      mutate(.keep = 'all', pct_overlap = intersect / intersect[which(nw2 == nw1)]) %>% 
      ungroup() %>% 
      mutate(filt = .x)
  }
)


olap %>%
  mutate(
    filt = fct_relevel(filt, c('none','node','edge','node_edge')),
    nw1 = fct_relevel(nw1, c('Tau Homeostasis','APP Metabolism', 'Endolysosome',
                             'Immune Response','Lipid Metabolism','Synapse',
                             'Mitochondrial Metabolism')),
    nw2 = fct_relevel(nw2, c('Mitochondrial Metabolism',
                             'Synapse','Lipid Metabolism','Immune Response',
                             'Endolysosome', 'APP Metabolism', 'Tau Homeostasis'
                             ))
  ) %>% 
  ggplot(., aes(x = nw2, y = nw1)) +
  geom_tile(aes(fill=pct_overlap)) + theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  # theme(axis.text.x = element_blank(), legend.position = 'bottom') +
  scale_fill_gradient2('% Total', low = 'white', high = '4a66ac', na.value = 'grey90') +
  # scale_x_discrete(position = "top") +
  geom_text(aes(label = intersect ), size = 2.5) +
  labs(x='',y='', title = 'common nodes, undirected NWs') + 
  facet_wrap(~filt)

```

common nodes, directed
```{r fig.width=9, fig.height=6}

olap = map_dfr(
  unique(nw.dat$filt),
  ~{
    tmp <- nw.dat %>% 
      filter(dir == 'directed', 
             filt == .x)
    
    olap <- crossing(nw1 = tmp$bd, nw2 = tmp$bd) %>% 
      group_by(nw1,nw2) %>% 
      mutate(.keep = 'all', 
             intersect = length(intersect(
               tmp %>% filter(bd == nw1) %>% pull(nodes) %>% unlist(),
               tmp %>% filter(bd == nw2) %>% pull(nodes) %>% unlist()
               ))
             ) %>% 
      ungroup() %>% group_by(nw1) %>% 
      mutate(.keep = 'all', pct_overlap = intersect / intersect[which(nw2 == nw1)]) %>% 
      ungroup() %>% 
      mutate(filt = .x)
  }
)

olap %>%
  mutate(
    filt = fct_relevel(filt, c('none','node','edge','node_edge')),
    nw1 = fct_relevel(nw1, c('Tau Homeostasis','APP Metabolism', 'Endolysosome',
                             'Immune Response','Lipid Metabolism','Synapse',
                             'Mitochondrial Metabolism')),
    nw2 = fct_relevel(nw2, c('Mitochondrial Metabolism',
                             'Synapse','Lipid Metabolism','Immune Response',
                             'Endolysosome', 'APP Metabolism', 'Tau Homeostasis'
                             ))
  ) %>% 
  ggplot(., aes(x = nw2, y = nw1)) +
  geom_tile(aes(fill=pct_overlap)) + theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  # theme(axis.text.x = element_blank(), legend.position = 'bottom') +
  scale_fill_gradient2('% Total', low = 'white', high = '4a66ac', na.value = 'grey90') +
  # scale_x_discrete(position = "top") +
  geom_text(aes(label = intersect ), size = 2.5) +
  labs(x='',y='', title = 'common nodes, undirected NWs') + 
  facet_wrap(~filt)

```

### Common Edges
common edges, undirected
```{r fig.width=9, fig.height=6}

olap = map_dfr(
  unique(nw.dat$filt),
  ~{
    tmp <- nw.dat %>% 
      filter(dir == 'undirected', 
             filt == .x)
    
    olap <- crossing(nw1 = tmp$bd, nw2 = tmp$bd) %>% 
      group_by(nw1,nw2) %>% 
      mutate(.keep = 'all', 
             intersect = length(intersect(
               tmp %>% filter(bd == nw1) %>% pull(edges) %>% unlist(),
               tmp %>% filter(bd == nw2) %>% pull(edges) %>% unlist()
               ))
             ) %>% 
      ungroup() %>% group_by(nw1) %>% 
      mutate(.keep = 'all', pct_overlap = intersect / intersect[which(nw2 == nw1)]) %>% 
      ungroup() %>% 
      mutate(filt = .x)
  }
)

olap %>%
  mutate(
    filt = fct_relevel(filt, c('none','node','edge','node_edge')),
    nw1 = fct_relevel(nw1, c('Tau Homeostasis','APP Metabolism', 'Endolysosome',
                             'Immune Response','Lipid Metabolism','Synapse',
                             'Mitochondrial Metabolism')),
    nw2 = fct_relevel(nw2, c('Mitochondrial Metabolism',
                             'Synapse','Lipid Metabolism','Immune Response',
                             'Endolysosome', 'APP Metabolism', 'Tau Homeostasis'
                             ))
  ) %>% 
  ggplot(., aes(x = nw2, y = nw1)) +
  geom_tile(aes(fill=pct_overlap)) + theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  # theme(axis.text.x = element_blank(), legend.position = 'bottom') +
  scale_fill_gradient2('% Total', low = 'white', high = '4a66ac', na.value = 'grey90') +
  # scale_x_discrete(position = "top") +
  geom_text(aes(label = intersect ), size = 2.5) +
  labs(x='',y='', title = 'common edges, undirected NWs') + 
  facet_wrap(~filt)
```

common edges, directed
```{r fig.width=9, fig.height=6}

olap = map_dfr(
  unique(nw.dat$filt),
  ~{
    tmp <- nw.dat %>% 
      filter(dir == 'directed', 
             filt == .x)
    
    olap <- crossing(nw1 = tmp$bd, nw2 = tmp$bd) %>% 
      group_by(nw1,nw2) %>% 
      mutate(.keep = 'all', 
             intersect = length(intersect(
               tmp %>% filter(bd == nw1) %>% pull(edges) %>% unlist(),
               tmp %>% filter(bd == nw2) %>% pull(edges) %>% unlist()
               ))
             ) %>% 
      ungroup() %>% group_by(nw1) %>% 
      mutate(.keep = 'all', pct_overlap = intersect / intersect[which(nw2 == nw1)]) %>% 
      ungroup() %>% 
      mutate(filt = .x)
  }
)

olap %>%
  mutate(
    filt = fct_relevel(filt, c('none','node','edge','node_edge')),
    nw1 = fct_relevel(nw1, c('Tau Homeostasis','APP Metabolism', 'Endolysosome',
                             'Immune Response','Lipid Metabolism','Synapse',
                             'Mitochondrial Metabolism')),
    nw2 = fct_relevel(nw2, c('Mitochondrial Metabolism',
                             'Synapse','Lipid Metabolism','Immune Response',
                             'Endolysosome', 'APP Metabolism', 'Tau Homeostasis'
                             ))
  ) %>% 
  ggplot(., aes(x = nw2, y = nw1)) +
  geom_tile(aes(fill=pct_overlap)) + theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  # theme(axis.text.x = element_blank(), legend.position = 'bottom') +
  scale_fill_gradient2('% Total', low = 'white', high = '4a66ac', na.value = 'grey90') +
  # scale_x_discrete(position = "top") +
  geom_text(aes(label = intersect ), size = 2.5) +
  labs(x='',y='', title = 'common edges, directed NWs') + 
  facet_wrap(~filt)
```

### Added Nodes
```{r fig.width=9, fig.height=6}

olap = map_dfr(
  unique(nw.dat$filt),
  ~{
    tmp <- nw.dat %>% 
      filter(dir == 'undirected', 
             filt == .x)
    
    olap <- crossing(nw1 = tmp$bd, nw2 = tmp$bd) %>% 
      group_by(nw1,nw2) %>% 
      mutate(.keep = 'all', 
             intersect = length(intersect(
             setdiff( tmp %>% filter(bd == nw1) %>% pull(nodes) %>% unlist(), 
                        tmp %>% filter(bd == nw1) %>% pull(le_genes) %>% unlist() ),
             setdiff( tmp %>% filter(bd == nw2) %>% pull(nodes) %>% unlist(), 
                        tmp %>% filter(bd == nw2) %>% pull(le_genes) %>% unlist() )
               ))
             ) %>% 
      ungroup() %>% group_by(nw1) %>% 
      mutate(.keep = 'all', pct_overlap = intersect / intersect[which(nw2 == nw1)]) %>% 
      ungroup() %>% 
      mutate(filt = .x)
  }
)

olap %>%
  mutate(
    filt = fct_relevel(filt, c('none','node','edge','node_edge')),
    nw1 = fct_relevel(nw1, c('Tau Homeostasis','APP Metabolism', 'Endolysosome',
                             'Immune Response','Lipid Metabolism','Synapse',
                             'Mitochondrial Metabolism')),
    nw2 = fct_relevel(nw2, c('Mitochondrial Metabolism',
                             'Synapse','Lipid Metabolism','Immune Response',
                             'Endolysosome', 'APP Metabolism', 'Tau Homeostasis'
                             ))
  ) %>% 
  ggplot(., aes(x = nw2, y = nw1)) +
  geom_tile(aes(fill=pct_overlap)) + theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  # theme(axis.text.x = element_blank(), legend.position = 'bottom') +
  scale_fill_gradient2('% Total', low = 'white', high = '4a66ac', na.value = 'grey90') +
  # scale_x_discrete(position = "top") +
  geom_text(aes(label = intersect ), size = 2.5) +
  labs(x='',y='', title = 'nodes added by path trace, undirected NW') + 
  facet_wrap(~filt)
```

nodes added by trace, directed NWs
```{r fig.width=9, fig.height=6}

olap = map_dfr(
  unique(nw.dat$filt),
  ~{
    tmp <- nw.dat %>% 
      filter(dir == 'directed', 
             filt == .x)
    
    olap <- crossing(nw1 = tmp$bd, nw2 = tmp$bd) %>% 
      group_by(nw1,nw2) %>% 
      mutate(.keep = 'all', 
             intersect = length(intersect(
             setdiff( tmp %>% filter(bd == nw1) %>% pull(nodes) %>% unlist(), 
                        tmp %>% filter(bd == nw1) %>% pull(le_genes) %>% unlist() ),
             setdiff( tmp %>% filter(bd == nw2) %>% pull(nodes) %>% unlist(), 
                        tmp %>% filter(bd == nw2) %>% pull(le_genes) %>% unlist() )
               ))
             ) %>% 
      ungroup() %>% group_by(nw1) %>% 
      mutate(.keep = 'all', pct_overlap = intersect / intersect[which(nw2 == nw1)]) %>% 
      ungroup() %>% 
      mutate(filt = .x)
  }
)

olap %>%
  mutate(
    filt = fct_relevel(filt, c('none','node','edge','node_edge')),
    nw1 = fct_relevel(nw1, c('Tau Homeostasis','APP Metabolism', 'Endolysosome',
                             'Immune Response','Lipid Metabolism','Synapse',
                             'Mitochondrial Metabolism')),
    nw2 = fct_relevel(nw2, c('Mitochondrial Metabolism',
                             'Synapse','Lipid Metabolism','Immune Response',
                             'Endolysosome', 'APP Metabolism', 'Tau Homeostasis'
                             ))
  ) %>% 
  ggplot(., aes(x = nw2, y = nw1)) +
  geom_tile(aes(fill=pct_overlap)) + theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  # theme(axis.text.x = element_blank(), legend.position = 'bottom') +
  scale_fill_gradient2('% Total', low = 'white', high = '4a66ac', na.value = 'grey90') +
  # scale_x_discrete(position = "top") +
  geom_text(aes(label = intersect ), size = 2.5) +
  labs(x='',y='', title = 'nodes added by path trace, directed NW') + 
  facet_wrap(~filt)
```



### Score Comparisons (LE genes vs Added genes)
```{r}
tmp <- nw.dat %>% 
  select(bd, filt, dir, input_genes, added_genes) %>% 
  pivot_longer(cols = c(input_genes, added_genes)) %>% 
  unnest(value) %>% 
  left_join(
    .,
    scores %>% select(value = GeneName, Overall, 
                      GeneticsScore, OmicsScore, LiteratureScore),
    by = 'value', na_matches = 'never'
  )
```


```{r fig.width=4, fig.height=2}
tmp %>% 
  rename(set = name, gene = value) %>% 
  mutate(filt = fct_relevel(filt, c('none','node','edge','node_edge'))) %>%
  ggplot(aes(Overall))+
  theme(legend.position = 'top') + 
  # geom_density(aes(fill = set, color = set), alpha = .3)+
  geom_histogram(aes(fill = set), alpha = .8, position='dodge')+
  facet_grid(dir~filt, scales = 'free')
```

```{r fig.width=4, fig.height=4}
tmp %>% 
  rename(set = name, gene = value) %>% 
  pivot_longer(Overall:OmicsScore) %>% 
  mutate(filt = fct_relevel(filt, c('none','node','edge','node_edge'))) %>%
  filter(value >0) %>% 
  ggplot(aes(value))+
  theme(legend.position = 'top') + 
  # geom_density(aes(fill = set, color = set), alpha = .3)+
  geom_histogram(aes(fill = set), alpha = .8, position='dodge')+
  facet_grid(filt~name, scales = 'free')
```

```{r fig.width=4, fig.height=7}
tmp %>% 
  rename(set = name, gene = value) %>% 
  pivot_longer(Overall:OmicsScore) %>% 
  mutate(filt = fct_relevel(filt, c('none','node','edge','node_edge'))) %>%
  filter(value > 0) %>% 
  ggplot(aes(value))+
  theme(legend.position = 'top') + 
  # geom_density(aes(fill = set, color = set), alpha = .3)+
  geom_histogram(aes(fill = set), alpha = .8, position='dodge')+
  facet_grid(bd~name, scales = 'free')
```

### Biodom Enrichment - NW nodes

```{r}
gl <- nw.dat %>% 
    filter(
        bd == 'APP Metabolism',
        filt == 'node',
        dir == 'undirected'
    ) %>% select(-name) %>% 
    pivot_longer(nodes:input_genes) %>% 
    rowwise() %>% 
    mutate(
        enr = gseGO( unlist(value),)
    )
```


## APP Metabolism
```{r}
# leading edge genes that were traced
input.gene.list <- enr.bd %>% 
  filter(
    Biodomain == 'APP Metabolism',
    padj < 0.01,
    NES > 1.7
  ) %>% 
  pull(leadingEdge_genes) %>% 
  unlist() %>% 
  unique()

# synIDs of BD-specific NWs
nw.tbl = nw.dirs %>% 
  filter(bd == 'APP Metabolism') %>% 
  select(bd, bd.filt, filt, dir, id)
nw.tbl <- tibble(
  base_nw = c('undir','undir_node','undir_edge','undir_node_edge',
              'dir','dir_node','dir_edge','dir_node_edge'),
  dir = c('undirected','undirected','undirected','undirected',
          'directed','directed','directed','directed'),
  filt = c('none','node','edge','node_edge',
           'none','node','edge','node_edge')
  ) %>% 
  left_join(nw.tbl, ., by = c('dir','filt'))

# synIDs of BD-specific wKDA results
kda.tbl = kda.dirs %>% 
  filter(bd == 'APP Metabolism') %>% 
  select(bd, filt, dir, ef, id)

```

### NW properties
```{r}
# summarize NW properties
nw.tbl = bind_cols(
  nw.tbl,
  map_dfr(
    1:nrow(nw.tbl),
    ~ {
      nw = read_graph( synGet(nw.tbl$id[.x])$path, format = 'graphml' )
      tibble(
        n_nodes = nw %>% V %>% length,
        n_edges = nw %>% E %>% length,
        edge_per_node = n_edges/n_nodes,
        avg_node_degree = degree(nw, V(nw)) %>% mean(),
        avg_path_length = nw %>% average.path.length,
        assortativity_coef = nw %>% assortativity(., types1 = V(.)),
        connected_components = nw %>% no.clusters,
        missing = setdiff( input.gene.list, names(V( eval(parse(text = nw.tbl$base_nw[.x])) )) ) %>% list(),
        added = setdiff( names(V(nw)), input.gene.list ) %>% list()
      )
      }
    )
) 
```

Global properties of biodomain-filtered path traced networks
```{r fig.width=7, fig.height=8}
nw.tbl %>%
  filter(bd.filt) %>%
  mutate(
    network = paste( dir, filt, sep = '_') # bd.filt,
  ) %>% 
  rowwise() %>%
  mutate( missing = length(unique(unlist(missing))),
          added = length(unique(unlist(added)))
  ) %>% 
  select(network, n_nodes:added) %>% 
  pivot_longer(cols = c(-network), 
               names_to = 'properties', 
               values_to = 'val') %>% 
  mutate(network = factor(network, 
                       levels = c('undirected_none',
                                  'undirected_node',
                                  'undirected_edge',
                                  'undirected_node_edge',
                                  'directed_none',
                                  'directed_node',
                                  'directed_edge',
                                  'directed_node_edge')) ,
         properties = factor(properties, 
                             levels = c('n_nodes',
                                        'n_edges',
                                        'missing',
                                        'added',
                                        'edge_per_node', 
                                        'avg_node_degree',
                                        'avg_path_length',
                                        'assortativity_coef',
                                        'connected_components'
                                        )) 
         ) %>% 
  ggplot(aes(network, val)) +
  geom_bar(stat = 'identity', position = 'dodge')+
  theme(legend.position = 'top',
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))+
  labs(y = '',x = '')+
  # scale_y_log10()+
  facet_wrap(~properties, scales = 'free_y', ncol = 2)

```
### KDA results
```{r}
kd.res = kda.tbl %>% 
  # filter(dir == 'undirected') %>% 
  group_by(bd,filt,dir) %>%
  summarise( kd = list(read_kda_res(id[ef == 0],id[ef == 1])) ) %>% 
  unnest(kd) %>%  
  left_join(., 
            biodom %>% select(MODULE = GOterm_Name, Biodomain, color, abbr, label), 
            by = 'MODULE') %>% 
  ungroup() %>% 
  group_by(bd, filt, dir) %>% 
  arrange(MODULE, desc(ef1_fdr)) %>% 
  mutate(top_kd = if_else( duplicated(MODULE) , 0, 1)) %>% 
  relocate(top_kd, .after = 'MEMBER') %>% 
  ungroup()

am.kd.res <- kd.res
```

```{r fig.width=16,fig.height=8}
# p2 = 
kd.res %>% 
  # filter( ef1_fdr > -log10(0.05)
  #        # , MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
  #        , delta_fdr > 0
  #        ) %>%
  mutate(dir = fct_relevel(dir, c('undirected','directed')),
         filt = fct_relevel(filt, c('none','node','edge','node_edge'))) %>% 
  ggplot(aes( ef1_fdr, delta_fdr ))+
  labs(x = 'wKDA FDR ef1, -log10', y = '\u0394 FDR, ef1 - ef0', title = unique(kd.res$bd))+
  # geom_abline(intercept = 0, slope =1, lty= 2, lwd = .5)+
  geom_smooth(method = 'glm', lty = 2, lwd = .5, color = 'grey20')+
  geom_vline(xintercept = 0, lwd = .5)+ geom_hline(yintercept = 0, lwd = .5) +
  geom_point(alpha = .2, size = 1, aes(color = color) )+
  geom_point(data = subset(kd.res, ef1_fdr > -log10(0.05) & top_kd == 1 & delta_fdr > 0)
             , alpha = .6, size = 2, aes(color = color))+
  ggrepel::geom_label_repel(
    data = subset( kd.res, ef1_fdr > -log10(0.05)
                   & top_kd == 1
                   & MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
                   & delta_fdr > 0
                   ), 
    aes(label = paste0(NODE, '\n', MODULE, '\n', Biodomain)),
    size = 2, alpha = .7, min.segment.length = 0)+
  facet_wrap(dir~filt, scales = 'free', ncol = 4)+ #, scales = 'free'
  scale_color_identity(guide = 'none') #; plotly::ggplotly(p)

# plotly::ggplotly(p2)
```

### KD ~ Biodomains

```{r, fig.width=10}
kd.res %>% 
  filter(ef1_fdr > -log10(0.05)
         # , MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
         , delta_fdr > 0
         , top_kd == 1
         ) %>%
  mutate(pair = paste0(NODE,':',MODULE)) %>% 
  group_by(filt, dir, Biodomain) %>% 
  summarise(n_term = length(unique(MODULE)),
            n_node = length(unique(NODE)),
            n_kd = length(unique(pair)),
            # terms = list(unique(MODULE)),
            min_fdr = signif( 10^-max(ef1_fdr), digits = 3),
            max_delta = signif( max(delta_fdr), digits = 3) ) %>% 
  full_join(., 
            biodom %>% group_by(Biodomain) %>% mutate(n_go = length(unique(GO_ID))) %>% 
              select(Biodomain, n_go, abbr:color) %>% distinct(), 
            by = 'Biodomain') %>% 
  ungroup() %>%
  mutate(fxn_bd_term = n_term / n_go) %>% 
  filter(!is.na(filt), !is.na(dir)) %>% 
  mutate(#dir = fct_relevel(dir, c('undirected','directed')),
         filt = fct_relevel(filt, c('none','node','edge','node_edge')),
         Biodomain = fct_reorder(Biodomain, n_term)) %>% 
  arrange(Biodomain, desc(n_term), desc(max_delta)) %>% 
  ggplot(aes(n_term, Biodomain))+
  geom_segment(aes(yend=Biodomain, xend=0), color = 'grey50')+
  geom_point(aes(size = max_delta, color = color))+
  scale_color_identity()+
  labs(y='', 
       title = paste0(unique(kd.res$bd), ' Network Key Drivers'),
       subtitle = 'Biodomain GO terms')+ 
  theme(legend.position = 'bottom')+
  facet_wrap(dir~filt, ncol = 4)
```


```{r, fig.width=10}
kd.res %>% 
  filter(ef1_fdr > -log10(0.05)
         # , MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
         , delta_fdr > 0
         , top_kd == 1
         ) %>%
  mutate(pair = paste0(NODE,':',MODULE)) %>% 
  group_by(filt, dir, Biodomain) %>% 
  summarise(n_term = length(unique(MODULE)),
            n_node = length(unique(NODE)),
            n_kd = length(unique(pair)),
            # terms = list(unique(MODULE)),
            min_fdr = signif( 10^-max(ef1_fdr), digits = 3),
            max_delta = signif( max(delta_fdr), digits = 3) ) %>% 
  full_join(., 
            biodom %>% select(Biodomain, abbr:color) %>% distinct(), 
            by = 'Biodomain') %>% 
  arrange(desc(n_node), desc(max_delta), .by_group = T) %>% 
  ungroup() %>% 
  filter(!is.na(filt), !is.na(dir)) %>% 
  mutate(#dir = fct_relevel(dir, c('undirected','directed')),
         filt = fct_relevel(filt, c('none','node','edge','node_edge')),
         Biodomain = fct_reorder(Biodomain, n_node)) %>%
  ggplot(aes(n_node, Biodomain))+
  geom_segment(aes(yend=Biodomain, xend=0), color = 'grey50')+
  geom_point(aes(size = max_delta, color = color))+
  scale_color_identity()+
  labs(y='', 
       title = paste0(unique(kd.res$bd), ' Network Key Drivers'),
       subtitle = 'Nodes')+ 
  theme(legend.position = 'bottom')+
  facet_wrap(dir~filt, ncol = 4)
```

```{r fig.width=10,fig.height=10}
tmp <- kd.res %>% 
  filter( 
    ef1_fdr > -log10(0.05)
    , MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
    , delta_fdr > 0 ,
    dir == 'undirected'
    , filt == 'node'
         )

ggplot(tmp, aes( ef1_fdr, delta_fdr ))+
  labs(x = 'wKDA FDR ef1, -log10', y = '\u0394 FDR, ef1 - ef0', 
       title = paste0(unique(tmp$bd), ': ', unique(tmp$dir),', ',unique(tmp$filt)),
       subtitle = 'signif KDs (EF1 FDR < 0.05), \u0394 FDR > 0, for GSEA-enriched terms'
       )+
  # geom_abline(intercept = 0, slope =1, lty= 2, lwd = .5)+
  geom_smooth(method = 'glm', lty = 2, lwd = .5, color = 'grey20')+
  geom_vline(xintercept = 0, lwd = .5)+ geom_hline(yintercept = 0, lwd = .5) +
  geom_point(alpha = .2, size = 1, aes(color = color) )+
  geom_point(data = subset(kd.res, ef1_fdr > -log10(0.05) & top_kd == 1 & delta_fdr > 0)
             , alpha = .6, size = 2, aes(color = color))+
  ggrepel::geom_label_repel(
    data = subset( kd.res, ef1_fdr > -log10(0.05)
                   & top_kd == 1
                   & MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
                   & delta_fdr > 0
                   ),
    aes(label = paste0(NODE, '\n', MODULE, '\n', Biodomain)),
    size = 2, alpha = .7, min.segment.length = 0)+
  facet_wrap(~Biodomain)+ #, scales = 'free'
  scale_color_identity(guide = 'none') #; plotly::ggplotly(p)

# plotly::ggplotly(p2)
```

```{r}
kd.res %>% 
  filter(ef1_fdr > -log10(0.05)
         # , MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
         , delta_fdr > 0
         , top_kd == 1
         ) %>% 
  group_by(filt, dir, Biodomain) %>% 
  summarise(n_term = length(unique(MODULE)),
            # terms = list(unique(MODULE)),
            min_fdr = signif( 10^-max(ef1_fdr), digits = 3),
            max_delta = signif( max(delta_fdr), digits = 3) ) %>% 
  arrange(desc(n_term), desc(max_delta), .by_group = T) %>%
  DT::datatable(rownames = F, filter = 'top')
```

### Top KDs
```{r}
kd.summary = kd.res %>% 
  filter(ef1_fdr > -log10(0.05)
         , MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
         , delta_fdr > 0
         ) %>% 
  group_by(NODE, filt, dir) %>% 
  summarise(n_bd = length(unique(Biodomain)),
            bds = list(unique(Biodomain)),
            n_term = length(unique(MODULE)),
            terms = list(unique(MODULE)),
            min_fdr = signif( 10^-max(ef1_fdr), digits = 3),
            max_delta = signif( max(delta_fdr), digits = 3) ) %>% 
  arrange(desc(n_bd), desc(max_delta)) %>% 
  mutate(LE_gene = if_else(NODE %in% input.gene.list, 'Y', 'N')) %>% 
  relocate(LE_gene, .after = 'NODE')

DT::datatable(kd.summary %>% select(-bds, -terms), rownames = F, filter = 'top')
```

```{r}
kd.res %>% 
  filter(ef1_fdr > -log10(0.05)
         , top_kd == 1
         , MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
         , delta_fdr > 0
         ) %>% 
  select(bd, dir, filt, NODE, MODULE, MEMBER, contains('fdr')) %>% 
  arrange(desc(delta_fdr), desc(ef1_fdr)) %>% 
  mutate(LE_gene = if_else(NODE %in% input.gene.list, 'Y', 'N')) %>% 
  relocate(LE_gene, .after = 'NODE') %>% 
  DT::datatable(., rownames = F, filter = 'top') %>% 
  DT::formatSignif(columns = c('ef0_fdr','ef1_fdr','delta_fdr'))
```

### KD subnetworks
pull NW to view subgraphs
```{r}
nw = nw.tbl %>% 
  filter(
    dir == 'undirected', 
    filt == 'node_edge', 
    bd.filt == T
    ) %>% 
  pull(id) %>% 
  synGet(.) %>% 
  .$path %>% 
  read_graph(., format = 'graphml' )
```

```{r fig.width=12,fig.height=8}
p = suppressWarnings( plot_kd_subnet(nw, kd = 'GRIN2B',term = 'postsynaptic density') )
p
```

```{r fig.width=12,fig.height=8}
p = suppressWarnings( plot_kd_subnet(nw, kd = 'APP', term = 'regulation of apoptotic process') )
p
```

```{r fig.width=12,fig.height=8}
p = suppressWarnings( plot_kd_subnet(nw, kd = 'MAPT', term = 'positive regulation of neuron death') )
p
```

```{r fig.width=12,fig.height=8}
p = suppressWarnings( plot_kd_subnet(nw, kd = 'DLG1', term = 'neuron to neuron synapse') )
p
```

<!-- ```{r} -->
<!-- kd = 'DLG1' -->
<!-- term = 'neuron to neuron synapse' -->

<!-- vert_num <- match(kd, V(nw)$name) -->
<!-- vert_neigh <- neighbors(nw, vert_num) %>% names() -->
<!-- vert_neigh_num <- match(vert_neigh, V(nw)$name) -->

<!-- term_num <- biodom %>% -->
<!--   filter(GOterm_Name == term) %>% -->
<!--   pull(symbol) %>% unlist() %>% -->
<!--   match(., V(nw)$name) %>% .[!is.na(.)] -->

<!-- term_neigh <- map_chr(1:length(term_num), -->
<!--                       ~ neighbors(nw, term_num[.x]) %>% names()) -->
<!-- term_neigh_num <- match(term_neigh, V(nw)$name) -->

<!-- g2 <- induced_subgraph(nw, c(vert_num, intersect(term_neigh, vert_neigh))) -->
<!-- g3 <- induced_subgraph(nw, c(vert_num, term_neigh)) -->

<!-- cowplot::plot_grid( -->

<!--   ggraph(g3, layout = 'linear', circular = TRUE) + -->
<!--     geom_edge_arc(alpha = .3, color = 'grey75') + -->
<!--     geom_node_point( shape = 21, color = "black", alpha = .3, -->
<!--       aes(size = TargetRiskScore, fill = Pro_EffectScore, filter= .N()$name != kd)  )+ -->
<!--     geom_node_point( shape = 23, color = "black", alpha = .3, -->
<!--       aes(size = TargetRiskScore, fill = Pro_EffectScore, filter = .N()$name == kd) )+ -->
<!--     geom_node_text(aes(label = name), size = 2) + -->
<!--     coord_fixed() + -->
<!--     scale_size_continuous( range = c(.5, 10), limits = c(0, 5), trans = 'exp')+ -->
<!--     scale_fill_gradient2( -->
<!--       low = 'purple', mid = 'black', high = 'green', na.value = 'grey85', -->
<!--       limits = c(-2.5,2.5) )+ #approx: range(omics$Pro_TE, na.rm = T) -->
<!--     labs( title = 'All term genes in NW', -->
<!--           subtitle = paste0('KD: ', kd, '\nTerm: ', term) )+ -->
<!--     theme_graph(background = 'white') -->
<!--   , -->
<!--   ggraph(g2, layout = 'linear', circular = TRUE) + -->
<!--           geom_edge_arc(alpha = .3, color = 'grey75') + -->
<!--     geom_node_point( shape = 21, color = "black", alpha = .3, -->
<!--       aes(size = TargetRiskScore, fill = Pro_EffectScore, filter= .N()$name != kd)  )+ -->
<!--     geom_node_point( shape = 23, color = "black", alpha = .3, -->
<!--       aes(size = TargetRiskScore, fill = Pro_EffectScore, filter = .N()$name == kd) )+ -->
<!--     geom_node_text(aes(label = name), size = 2) + -->
<!--     coord_fixed() + -->
<!--     scale_size_continuous( range = c(.5, 10), limits = c(0, 5), trans = 'exp')+ -->
<!--     scale_fill_gradient2( -->
<!--       low = 'purple', mid = 'black', high = 'green', na.value = 'grey85', -->
<!--       limits = c(-2.5,2.5) )+ #approx: range(omics$Pro_TE, na.rm = T) -->
<!--     labs( title = 'Term genes & KD neighbors in NW', -->
<!--           subtitle = paste0('KD: ', kd, '\nTerm: ', term) )+ -->
<!--     theme_graph(background = 'white') -->
<!--   , -->
<!--   ncol = 2 -->

<!-- ) -->

<!-- ``` -->


### KDs ~ CBrain phenotypes
```{r fig.width=10, fig.height=5}
# crispr brain phenotype hits (any) vs non-hits
cb.hits = simple %>% filter(`Hit Class` != 'Non-Hit') %>% 
  pull(Gene) %>% unique()
cb.nonhits = simple %>% filter( (Gene %in% cb.hits)==F ) %>% 
  pull(Gene) %>% unique()

# ID key drivers from different parameter sets
comb = kd.res %>% select(filt, dir) %>% distinct() %>% arrange(dir,filt)
comb$kd.hits = map(
  1:nrow(comb),
  ~ kd.res %>% filter(ef1_fdr > -log10(0.05), 
                      filt == comb$filt[.x],
                      dir == comb$dir[.x]) %>% pull(NODE) %>% unique()
)
comb$kd.nonhits = map(
  1:nrow(comb),
  ~ kd.res %>% filter( (NODE %in% comb$kd.hits[[.x]])==F ) %>% 
    pull(NODE) %>% unique()
)

# calculate fisher stats 
comb = map_dfr(
  1:nrow(comb),
  ~ bind_cols(
      pheno_kd = intersect(cb.hits, comb$kd.hits[[.x]]) %>% length(),
      noPheno_kd = intersect(cb.nonhits, comb$kd.hits[[.x]]) %>% length(),
      pheno_nokd = intersect(cb.hits, comb$kd.nonhits[[.x]]) %>% length(),
      noPheno_nokd = intersect(cb.nonhits, comb$kd.nonhits[[.x]]) %>% length()
    ) %>% 
    rowwise() %>% mutate(
      fisher.p = matrix(c(pheno_kd, noPheno_kd, pheno_nokd, noPheno_nokd), 
                        nrow = 2) %>% 
      fisher.test( ., alt = 'g') %>% broom::tidy() %>% pull(p.value)
    )
) %>% 
  bind_cols(comb, .)

# make plots for each comb
plist = map(
  1:nrow(comb),
  ~ plot( eulerr::euler(
    c(pheno = length(cb.hits),
      kd = length(comb$kd.hits[[.x]]), 
      'pheno&kd' = comb$pheno_kd[.x])
    , quantities = T )
    ) %>% 
    ggplotify::as.ggplot() + 
    ggtitle(label = kd.res$bd %>% unique,
            subtitle = paste0(
            'dir: ', comb$dir[.x],', filt: ', comb$filt[.x],
            '\nFisher p = ', comb$fisher.p[.x] %>% signif(digits = 2) )
            ) 
)

cowplot::plot_grid(plotlist = plist, ncol = 4)


```

linear regression  ~ KDA FDR
```{r}
tmp <- kd.res %>% inner_join( simple,., by =c('Gene'='NODE')) %>% 
  group_by(cell,mode,expt, bd, filt, dir) %>% 
  mutate(lm = lm(abs(gene_score)~ef1_fdr) %>% broom::tidy() %>% 
           filter(term != '(Intercept)') %>% 
           mutate(r.squared = lm(abs(gene_score)~ef1_fdr) %>% 
                    broom::glance() %>% pull(r.squared)) %>% list()) %>% 
  unnest(lm)  %>% 
  select(cell, mode, expt, bd.nw = bd, nw.filt = filt, nw.dir=dir, term:r.squared) %>% distinct() %>% 
  filter(p.value < 0.05) %>% 
  arrange(desc(statistic),p.value)

tmp %>% 
  DT::datatable(rownames = F, filter = 'top', caption = 'abs(gene_score) ~ ef1_fdr', options = list(pageLength = 6)) %>% #
  DT::formatSignif(columns = c('statistic', 'std.error','r.squared', 'p.value', 'estimate'))
```

```{r fig.width=10, fig.height=5}
c = 'Glutamatergic Neuron'
m = 'CRISPRi'
e = 'Liperfluo'

kd.res %>% inner_join( simple,., by =c('Gene'='NODE')) %>%
  filter(
    cell == c,
    mode == m,
    expt == e,
    # ef1_fdr > -log10(0.2)
    ) %>% 
  ggplot( aes( ef1_fdr, abs(gene_score) )) +
  geom_point(#data = subset(tmp, d > 0),
             aes(color = color,  size = delta_fdr), alpha = .5) +
  geom_hline(yintercept = 0, lwd = 0.5)+
  geom_vline(xintercept = 0, lwd = 0.5)+
  scale_size_continuous(name = 'KDA \u0394 FDR\nef1-ef0', range = c(.5,3))+ 
  # ggrepel::geom_label_repel(
  #   data = subset(tmp, d > 0), aes(label = paste0(Gene,'\n', go)),
  #   min.segment.length = 0, size = 2.5, max.overlaps = 12)+
  scale_color_identity(guide = 'none')+
  geom_smooth(method = 'lm', color = 'grey20',lty=2)+
  labs(y = 'CRISPRbrain phenotype score, absolute value',
       x = 'KDA FDR, -log10',
       title = paste0(c,', ',m,', ',e)) + 
  facet_grid(dir~filt, scales = 'free_x')
```

linear regression ~  KDA delta FDR e1/e0
```{r}
tmp <- kd.res %>% inner_join( simple,., by =c('Gene'='NODE')) %>% 
  group_by(cell,mode,expt, bd, filt, dir) %>% 
  mutate(lm = lm(abs(gene_score)~delta_fdr) %>% broom::tidy() %>% 
           filter(term != '(Intercept)') %>% 
           mutate(r.squared = lm(abs(gene_score)~delta_fdr) %>% 
                    broom::glance() %>% pull(r.squared)) %>% list()) %>% 
  unnest(lm) %>% 
  select(cell, mode, expt, bd, filt, dir, term:r.squared) %>% distinct() %>% 
  filter(p.value < 0.05) %>% 
  arrange(desc(statistic),p.value) 

tmp %>% 
  DT::datatable(rownames = F, filter = 'top', caption = 'abs(gene_score) ~ \u0394 fdr (ef1-ef0)', options = list(pageLength = 6)) %>% #
  DT::formatSignif(columns = c('statistic', 'std.error','r.squared', 'p.value', 'estimate'))
```

```{r fig.width=10, fig.height=5}
c = 'iAstrocyte'
m = 'CRISPRi'
e = 'Phagocytosis-Veh'

kd.res %>% inner_join( simple,., by =c('Gene'='NODE')) %>%
  filter(
    cell == c,
    mode == m,
    expt == e,
    ef1_fdr > -log10(0.2)
    ) %>% 
  ggplot( aes( delta_fdr, abs(gene_score) )) +
  geom_point(#data = subset(tmp, d > 0),
             aes(color = color,  size = ef1_fdr), alpha = .5) +
  geom_hline(yintercept = 0, lwd = 0.5)+
  geom_vline(xintercept = 0, lwd = 0.5)+
  scale_size_continuous(name = 'KDA \u0394 FDR\nef1-ef0', range = c(.5,3))+ 
  # ggrepel::geom_label_repel(
  #   data = subset(tmp, d > 0), aes(label = paste0(Gene,'\n', go)),
  #   min.segment.length = 0, size = 2.5, max.overlaps = 12)+
  scale_color_identity(guide = 'none')+
  geom_smooth(method = 'lm', color = 'grey20',lty=2)+
  labs(y = 'CRISPRbrain phenotype score, absolute value',
       x = 'KDA FDR, -log10',
       title = paste0(c,', ',m,', ',e)) + 
  facet_grid(dir~filt, scales = 'free_x')
```

## Tau Homeostasis
```{r}
# leading edge genes that were traced
input.gene.list <- enr.bd %>% 
  filter(
    Biodomain == 'Tau Homeostasis',
    padj < 0.01,
    NES > 1.7
  ) %>% 
  pull(leadingEdge_genes) %>% 
  unlist() %>% 
  unique()

# synIDs of BD-specific NWs
nw.tbl = nw.dirs %>% 
  filter(bd == 'APP Metabolism') %>% 
  select(bd, bd.filt, filt, dir, id)
nw.tbl <- tibble(
  base_nw = c('undir','undir_node','undir_edge','undir_node_edge',
              'dir','dir_node','dir_edge','dir_node_edge'),
  dir = c('undirected','undirected','undirected','undirected',
          'directed','directed','directed','directed'),
  filt = c('none','node','edge','node_edge',
           'none','node','edge','node_edge')
  ) %>% 
  left_join(nw.tbl, ., by = c('dir','filt'))

# synIDs of BD-specific wKDA results
kda.tbl = kda.dirs %>% 
  filter(bd == 'Tau Homeostasis') %>% 
  select(bd, filt, dir, ef, id)

```

### NW properties
```{r}
# summarize NW properties
nw.tbl = bind_cols(
  nw.tbl,
  map_dfr(
    1:nrow(nw.tbl),
    ~ {
      nw = read_graph( synGet(nw.tbl$id[.x])$path, format = 'graphml' )
      tibble(
        n_nodes = nw %>% V %>% length,
        n_edges = nw %>% E %>% length,
        edge_per_node = n_edges/n_nodes,
        avg_node_degree = degree(nw, V(nw)) %>% mean(),
        avg_path_length = nw %>% average.path.length,
        assortativity_coef = nw %>% assortativity(., types1 = V(.)),
        connected_components = nw %>% no.clusters,
        missing = setdiff( input.gene.list, names(V( eval(parse(text = nw.tbl$base_nw[.x])) )) ) %>% list(),
        added = setdiff( names(V(nw)), input.gene.list ) %>% list()
      )
      }
    )
) 
```

Global properties of biodomain-filtered path traced networks
```{r fig.width=7, fig.height=8}
nw.tbl %>%
  filter(bd.filt) %>%
  mutate(
    network = paste( dir, filt, sep = '_') # bd.filt,
  ) %>% 
  rowwise() %>%
  mutate( missing = length(unique(unlist(missing))),
          added = length(unique(unlist(added)))
  ) %>% 
  select(network, n_nodes:added) %>% 
  pivot_longer(cols = c(-network), 
               names_to = 'properties', 
               values_to = 'val') %>% 
  mutate(network = factor(network, 
                       levels = c('undirected_none',
                                  'undirected_node',
                                  'undirected_edge',
                                  'undirected_node_edge',
                                  'directed_none',
                                  'directed_node',
                                  'directed_edge',
                                  'directed_node_edge')) ,
         properties = factor(properties, 
                             levels = c('n_nodes',
                                        'n_edges',
                                        'missing',
                                        'added',
                                        'edge_per_node', 
                                        'avg_node_degree',
                                        'avg_path_length',
                                        'assortativity_coef',
                                        'connected_components'
                                        )) 
         ) %>% 
  ggplot(aes(network, val)) +
  geom_bar(stat = 'identity', position = 'dodge')+
  theme(legend.position = 'top',
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))+
  labs(y = '',x = '')+
  # scale_y_log10()+
  facet_wrap(~properties, scales = 'free_y', ncol = 2)

```
### KDA results
```{r}
kd.res = kda.tbl %>% 
  # filter(dir == 'undirected') %>% 
  group_by(bd,filt,dir) %>%
  summarise( kd = list(read_kda_res(id[ef == 0],id[ef == 1])) ) %>% 
  unnest(kd) %>%  
  left_join(., 
            biodom %>% select(MODULE = GOterm_Name, Biodomain, color, abbr, label), 
            by = 'MODULE') %>% 
  ungroup() %>% 
  group_by(bd, filt, dir) %>% 
  arrange(MODULE, desc(ef1_fdr)) %>% 
  mutate(top_kd = if_else( duplicated(MODULE) , 0, 1)) %>% 
  relocate(top_kd, .after = 'MEMBER') %>% 
  ungroup()

th.kd.res <- kd.res
```

```{r fig.width=16,fig.height=8}
# p2 = 
kd.res %>% 
  # filter( ef1_fdr > -log10(0.05)
  #        # , MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
  #        , delta_fdr > 0
  #        ) %>%
  mutate(dir = fct_relevel(dir, c('undirected','directed')),
         filt = fct_relevel(filt, c('none','node','edge','node_edge'))) %>% 
  ggplot(aes( ef1_fdr, delta_fdr ))+
  labs(x = 'wKDA FDR ef1, -log10', y = '\u0394 FDR, ef1 - ef0', title = unique(kd.res$bd))+
  # geom_abline(intercept = 0, slope =1, lty= 2, lwd = .5)+
  geom_smooth(method = 'glm', lty = 2, lwd = .5, color = 'grey20')+
  geom_vline(xintercept = 0, lwd = .5)+ geom_hline(yintercept = 0, lwd = .5) +
  geom_point(alpha = .2, size = 1, aes(color = color) )+
  geom_point(data = subset(kd.res, 
                           # ef1_fdr > -log10(0.05) & 
                             top_kd == 1 & delta_fdr > 0)
             , alpha = .6, size = 2, aes(color = color))+
  ggrepel::geom_label_repel(
    data = subset( kd.res, 
                   # ef1_fdr > -log10(0.05) &
                   top_kd == 1
                   # & MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
                   & delta_fdr > 0
                   ), 
    aes(label = paste0(NODE, '\n', MODULE, '\n', Biodomain)),
    size = 2, alpha = .7, min.segment.length = 0)+
  facet_wrap(dir~filt, scales = 'free', ncol = 4)+ #, scales = 'free'
  scale_color_identity(guide = 'none') #; plotly::ggplotly(p)

# plotly::ggplotly(p2)
```

### KD ~ Biodomains

```{r, fig.width=10}
kd.res %>% 
  filter(
    # ef1_fdr > -log10(0.05)
    # , MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
    # , 
    delta_fdr > 0
    , top_kd == 1
         ) %>%
  mutate(pair = paste0(NODE,':',MODULE)) %>% 
  group_by(filt, dir, Biodomain) %>% 
  summarise(n_term = length(unique(MODULE)),
            n_node = length(unique(NODE)),
            n_kd = length(unique(pair)),
            # terms = list(unique(MODULE)),
            min_fdr = signif( 10^-max(ef1_fdr), digits = 3),
            max_delta = signif( max(delta_fdr), digits = 3) ) %>% 
  full_join(., 
            biodom %>% group_by(Biodomain) %>% mutate(n_go = length(unique(GO_ID))) %>% 
              select(Biodomain, n_go, abbr:color) %>% distinct(), 
            by = 'Biodomain') %>% 
  ungroup() %>%
  mutate(fxn_bd_term = n_term / n_go) %>% 
  filter(!is.na(filt), !is.na(dir)) %>% 
  mutate(#dir = fct_relevel(dir, c('undirected','directed')),
         filt = fct_relevel(filt, c('none','node','edge','node_edge')),
         Biodomain = fct_reorder(Biodomain, n_term)) %>% 
  arrange(Biodomain, desc(n_term), desc(max_delta)) %>% 
  ggplot(aes(n_term, Biodomain))+
  geom_segment(aes(yend=Biodomain, xend=0), color = 'grey50')+
  geom_point(aes(size = max_delta, color = color))+
  scale_color_identity()+
  labs(y='', 
       title = paste0(unique(kd.res$bd), ' Network Key Drivers'),
       subtitle = 'Biodomain GO terms')+ 
  theme(legend.position = 'bottom')+
  facet_wrap(dir~filt, ncol = 4)
```


```{r, fig.width=10}
kd.res %>% 
  filter(#ef1_fdr > -log10(0.05)
         # , MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
         # , 
         delta_fdr > 0
         , top_kd == 1
         ) %>%
  mutate(pair = paste0(NODE,':',MODULE)) %>% 
  group_by(filt, dir, Biodomain) %>% 
  summarise(n_term = length(unique(MODULE)),
            n_node = length(unique(NODE)),
            n_kd = length(unique(pair)),
            # terms = list(unique(MODULE)),
            min_fdr = signif( 10^-max(ef1_fdr), digits = 3),
            max_delta = signif( max(delta_fdr), digits = 3) ) %>% 
  full_join(., 
            biodom %>% select(Biodomain, abbr:color) %>% distinct(), 
            by = 'Biodomain') %>% 
  arrange(desc(n_node), desc(max_delta), .by_group = T) %>% 
  ungroup() %>% 
  filter(!is.na(filt), !is.na(dir)) %>% 
  mutate(#dir = fct_relevel(dir, c('undirected','directed')),
         filt = fct_relevel(filt, c('none','node','edge','node_edge')),
         Biodomain = fct_reorder(Biodomain, n_node)) %>%
  ggplot(aes(n_node, Biodomain))+
  geom_segment(aes(yend=Biodomain, xend=0), color = 'grey50')+
  geom_point(aes(size = max_delta, color = color))+
  scale_color_identity()+
  labs(y='', 
       title = paste0(unique(kd.res$bd), ' Network Key Drivers'),
       subtitle = 'Nodes')+ 
  theme(legend.position = 'bottom')+
  facet_wrap(dir~filt, ncol = 4)
```

```{r fig.width=10,fig.height=10}
tmp <- kd.res %>% 
  filter( 
    # ef1_fdr > -log10(0.05)
    # , MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
    # , 
    delta_fdr > 0 ,
    dir == 'undirected'
    , filt == 'none'
         )

ggplot(tmp, aes( ef1_fdr, delta_fdr ))+
  labs(x = 'wKDA FDR ef1, -log10', y = '\u0394 FDR, ef1 - ef0', 
       title = paste0(unique(tmp$bd), ': ', unique(tmp$dir),', ',unique(tmp$filt)),
       subtitle = 'signif KDs (EF1 FDR < 0.05), \u0394 FDR > 0, for GSEA-enriched terms'
       )+
  # geom_abline(intercept = 0, slope =1, lty= 2, lwd = .5)+
  geom_smooth(method = 'glm', lty = 2, lwd = .5, color = 'grey20')+
  geom_vline(xintercept = 0, lwd = .5)+ geom_hline(yintercept = 0, lwd = .5) +
  geom_point(alpha = .2, size = 1, aes(color = color) )+
  geom_point(data = subset(kd.res, #ef1_fdr > -log10(0.05) & 
                             top_kd == 1 & delta_fdr > 0)
             , alpha = .6, size = 2, aes(color = color))+
  ggrepel::geom_label_repel(
    data = subset( kd.res, #ef1_fdr > -log10(0.05)
                   # & 
                     top_kd == 1
                   # & MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
                   & delta_fdr > 0
                   ),
    aes(label = paste0(NODE, '\n', MODULE, '\n', Biodomain)),
    size = 2, alpha = .7, min.segment.length = 0)+
  facet_wrap(~Biodomain)+ #, scales = 'free'
  scale_color_identity(guide = 'none') #; plotly::ggplotly(p)

# plotly::ggplotly(p2)
```

```{r}
kd.res %>% 
  filter(
    # ef1_fdr > -log10(0.05)
    # , MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
    # , 
    delta_fdr > 0
    , top_kd == 1
         ) %>% 
  group_by(filt, dir, Biodomain) %>% 
  summarise(n_term = length(unique(MODULE)),
            # terms = list(unique(MODULE)),
            min_fdr = signif( 10^-max(ef1_fdr), digits = 3),
            max_delta = signif( max(delta_fdr), digits = 3) ) %>% 
  arrange(desc(n_term), desc(max_delta), .by_group = T) %>%
  DT::datatable(rownames = F, filter = 'top')
```

### Top KDs
```{r}
kd.summary = kd.res %>% 
  filter(
    # ef1_fdr > -log10(0.05)
    # , MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
    # , 
    delta_fdr > 0
         ) %>% 
  group_by(NODE, filt, dir) %>% 
  summarise(n_bd = length(unique(Biodomain)),
            bds = list(unique(Biodomain)),
            n_term = length(unique(MODULE)),
            terms = list(unique(MODULE)),
            min_fdr = signif( 10^-max(ef1_fdr), digits = 3),
            max_delta = signif( max(delta_fdr), digits = 3) ) %>% 
  arrange(desc(n_bd), desc(max_delta)) %>% 
  mutate(LE_gene = if_else(NODE %in% input.gene.list, 'Y', 'N')) %>% 
  relocate(LE_gene, .after = 'NODE')

DT::datatable(kd.summary %>% select(-bds, -terms), rownames = F, filter = 'top')
```

```{r}
kd.res %>% 
  filter(
    # ef1_fdr > -log10(0.05)
    #      , 
    top_kd == 1
         # , MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
         ,
    delta_fdr > 0
         ) %>% 
  select(bd, dir, filt, NODE, MODULE, MEMBER, contains('fdr')) %>% 
  arrange(desc(delta_fdr), desc(ef1_fdr)) %>% 
  mutate(LE_gene = if_else(NODE %in% input.gene.list, 'Y', 'N')) %>% 
  relocate(LE_gene, .after = 'NODE') %>% 
  DT::datatable(., rownames = F, filter = 'top') %>% 
  DT::formatSignif(columns = c('ef0_fdr','ef1_fdr','delta_fdr'))
```

### KD subnetworks
pull NW to view subgraphs
```{r}
nw = nw.tbl %>% 
  filter(
    dir == 'undirected', 
    filt == 'none', 
    bd.filt == T
    ) %>% 
  pull(id) %>% 
  synGet(.) %>% 
  .$path %>% 
  read_graph(., format = 'graphml' )
```

```{r fig.width=12,fig.height=8}
p = suppressWarnings( plot_kd_subnet(nw, kd = 'MAPT',term = 'somatodendritic compartment') )
p
```

### KDs ~ CBrain phenotypes
```{r fig.width=10, fig.height=5}
# crispr brain phenotype hits (any) vs non-hits
cb.hits = simple %>% filter(`Hit Class` != 'Non-Hit') %>% 
  pull(Gene) %>% unique()
cb.nonhits = simple %>% filter( (Gene %in% cb.hits)==F ) %>% 
  pull(Gene) %>% unique()

# ID key drivers from different parameter sets
comb = kd.res %>% select(filt, dir) %>% distinct() %>% arrange(dir,filt)
comb$kd.hits = map(
  1:nrow(comb),
  ~ kd.res %>% filter(ef1_fdr > -log10(0.05), 
                      filt == comb$filt[.x],
                      dir == comb$dir[.x]) %>% pull(NODE) %>% unique()
)
comb$kd.nonhits = map(
  1:nrow(comb),
  ~ kd.res %>% filter( (NODE %in% comb$kd.hits[[.x]])==F ) %>% 
    pull(NODE) %>% unique()
)

# calculate fisher stats 
comb = map_dfr(
  1:nrow(comb),
  ~ bind_cols(
      pheno_kd = intersect(cb.hits, comb$kd.hits[[.x]]) %>% length(),
      noPheno_kd = intersect(cb.nonhits, comb$kd.hits[[.x]]) %>% length(),
      pheno_nokd = intersect(cb.hits, comb$kd.nonhits[[.x]]) %>% length(),
      noPheno_nokd = intersect(cb.nonhits, comb$kd.nonhits[[.x]]) %>% length()
    ) %>% 
    rowwise() %>% mutate(
      fisher.p = matrix(c(pheno_kd, noPheno_kd, pheno_nokd, noPheno_nokd), 
                        nrow = 2) %>% 
      fisher.test( ., alt = 'g') %>% broom::tidy() %>% pull(p.value)
    )
) %>% 
  bind_cols(comb, .)

# make plots for each comb
plist = map(
  1:nrow(comb),
  ~ plot( eulerr::euler(
    c(pheno = length(cb.hits),
      kd = length(comb$kd.hits[[.x]]), 
      'pheno&kd' = comb$pheno_kd[.x])
    , quantities = T )
    ) %>% 
    ggplotify::as.ggplot() + 
    ggtitle(label = kd.res$bd %>% unique,
            subtitle = paste0(
            'dir: ', comb$dir[.x],', filt: ', comb$filt[.x],
            '\nFisher p = ', comb$fisher.p[.x] %>% signif(digits = 2) )
            ) 
)

cowplot::plot_grid(plotlist = plist, ncol = 4)


```

Lysotracker phenotypes only
```{r fig.width=10, fig.height=5}
# crispr brain phenotype hits (any) vs non-hits
cb.hits = simple %>% 
  filter( expt %in% c('Lysotracker','LysoTracker-ITC','LysoTracker-Veh'), `Hit Class` != 'Non-Hit') %>% 
  pull(Gene) %>% unique()
cb.nonhits = simple %>% 
  filter( expt %in% c('Lysotracker','LysoTracker-ITC','LysoTracker-Veh'),  (Gene %in% cb.hits)==F ) %>% 
  pull(Gene) %>% unique()

# ID key drivers from different parameter sets
comb = kd.res %>% select(filt, dir) %>% distinct() %>% arrange(dir,filt)
comb$kd.hits = map(
  1:nrow(comb),
  ~ kd.res %>% filter(ef1_fdr > -log10(0.05), 
                      filt == comb$filt[.x],
                      dir == comb$dir[.x]) %>% pull(NODE) %>% unique()
)
comb$kd.nonhits = map(
  1:nrow(comb),
  ~ kd.res %>% filter( (NODE %in% comb$kd.hits[[.x]])==F ) %>% 
    pull(NODE) %>% unique()
)

# calculate fisher stats 
comb = map_dfr(
  1:nrow(comb),
  ~ bind_cols(
      pheno_kd = intersect(cb.hits, comb$kd.hits[[.x]]) %>% length(),
      noPheno_kd = intersect(cb.nonhits, comb$kd.hits[[.x]]) %>% length(),
      pheno_nokd = intersect(cb.hits, comb$kd.nonhits[[.x]]) %>% length(),
      noPheno_nokd = intersect(cb.nonhits, comb$kd.nonhits[[.x]]) %>% length()
    ) %>% 
    rowwise() %>% mutate(
      fisher.p = matrix(c(pheno_kd, noPheno_kd, pheno_nokd, noPheno_nokd), 
                        nrow = 2) %>% 
      fisher.test( ., alt = 'g') %>% broom::tidy() %>% pull(p.value)
    )
) %>% 
  bind_cols(comb, .)

# make plots for each comb
plist = map(
  1:nrow(comb),
  ~ plot( eulerr::euler(
    c(pheno = length(cb.hits),
      kd = length(comb$kd.hits[[.x]]), 
      'pheno&kd' = comb$pheno_kd[.x])
    , quantities = T )
    ) %>% 
    ggplotify::as.ggplot() + 
    ggtitle(label = kd.res$bd %>% unique,
            subtitle = paste0(
            'dir: ', comb$dir[.x],', filt: ', comb$filt[.x],
            '\nFisher p = ', comb$fisher.p[.x] %>% signif(digits = 2) )
            ) 
)

cowplot::plot_grid(plotlist = plist, ncol = 4)


```


linear regression  ~ KDA FDR
```{r}
tmp <- kd.res %>% inner_join( simple,., by =c('Gene'='NODE')) %>% 
  group_by(cell,mode,expt, bd, filt, dir) %>% 
  mutate(lm = lm(abs(gene_score)~ef1_fdr) %>% broom::tidy() %>% 
           filter(term != '(Intercept)') %>% 
           mutate(r.squared = lm(abs(gene_score)~ef1_fdr) %>% 
                    broom::glance() %>% pull(r.squared)) %>% list()) %>% 
  unnest(lm)  %>% 
  select(cell, mode, expt, bd.nw = bd, nw.filt = filt, nw.dir=dir, term:r.squared) %>% distinct() %>% 
  filter(p.value < 0.05) %>% 
  arrange(desc(statistic),p.value)

tmp %>% 
  DT::datatable(rownames = F, filter = 'top', caption = 'abs(gene_score) ~ ef1_fdr', options = list(pageLength = 6)) %>% #
  DT::formatSignif(columns = c('statistic', 'std.error','r.squared', 'p.value', 'estimate'))
```

<!-- ```{r fig.width=10, fig.height=5} -->
<!-- c = 'Glutamatergic Neuron' -->
<!-- m = 'CRISPRi' -->
<!-- e = 'FeRhoNox' -->

<!-- kd.res %>% inner_join( simple,., by =c('Gene'='NODE')) %>% -->
<!--   filter( -->
<!--     cell == c, -->
<!--     mode == m, -->
<!--     expt == e, -->
<!--     ef1_fdr > -log10(0.2) -->
<!--     ) %>%  -->
<!--   ggplot( aes( ef1_fdr, abs(gene_score) )) + -->
<!--   geom_point(#data = subset(tmp, d > 0), -->
<!--              aes(color = color,  size = delta_fdr), alpha = .5) + -->
<!--   geom_hline(yintercept = 0, lwd = 0.5)+ -->
<!--   geom_vline(xintercept = 0, lwd = 0.5)+ -->
<!--   scale_size_continuous(name = 'KDA \u0394 FDR\nef1-ef0', range = c(.5,3))+  -->
<!--   # ggrepel::geom_label_repel( -->
<!--   #   data = subset(tmp, d > 0), aes(label = paste0(Gene,'\n', go)), -->
<!--   #   min.segment.length = 0, size = 2.5, max.overlaps = 12)+ -->
<!--   scale_color_identity(guide = 'none')+ -->
<!--   geom_smooth(method = 'lm', color = 'grey20',lty=2)+ -->
<!--   labs(y = 'CRISPRbrain phenotype score, absolute value', -->
<!--        x = 'KDA FDR, -log10', -->
<!--        title = paste0(c,', ',m,', ',e)) +  -->
<!--   facet_grid(dir~filt, scales = 'free_x') -->
<!-- ``` -->
<!-- ```{r fig.width=10, fig.height=5} -->
<!-- c = 'Glutamatergic Neuron' -->
<!-- m = 'CRISPRi' -->
<!-- e = 'Lysotracker' -->

<!-- kd.res %>% inner_join( simple,., by =c('Gene'='NODE')) %>% -->
<!--   filter( -->
<!--     cell == c, -->
<!--     mode == m, -->
<!--     expt == e, -->
<!--     ef1_fdr > -log10(0.2) -->
<!--     ) %>%  -->
<!--   ggplot( aes( ef1_fdr, abs(gene_score) )) + -->
<!--   geom_point(#data = subset(tmp, d > 0), -->
<!--              aes(color = color,  size = delta_fdr), alpha = .5) + -->
<!--   geom_hline(yintercept = 0, lwd = 0.5)+ -->
<!--   geom_vline(xintercept = 0, lwd = 0.5)+ -->
<!--   scale_size_continuous(name = 'KDA \u0394 FDR\nef1-ef0', range = c(.5,3))+  -->
<!--   # ggrepel::geom_label_repel( -->
<!--   #   data = subset(tmp, d > 0), aes(label = paste0(Gene,'\n', go)), -->
<!--   #   min.segment.length = 0, size = 2.5, max.overlaps = 12)+ -->
<!--   scale_color_identity(guide = 'none')+ -->
<!--   geom_smooth(method = 'lm', color = 'grey20',lty=2)+ -->
<!--   labs(y = 'CRISPRbrain phenotype score, absolute value', -->
<!--        x = 'KDA FDR, -log10', -->
<!--        title = paste0(c,', ',m,', ',e)) +  -->
<!--   facet_grid(dir~filt, scales = 'free_x') -->
<!-- ``` -->

linear regression ~  KDA delta FDR e1/e0
```{r}
tmp <- kd.res %>% inner_join( simple,., by =c('Gene'='NODE')) %>% 
  group_by(cell,mode,expt, bd, filt, dir) %>% 
  mutate(lm = lm(abs(gene_score)~delta_fdr) %>% broom::tidy() %>% 
           filter(term != '(Intercept)') %>% 
           mutate(r.squared = lm(abs(gene_score)~delta_fdr) %>% 
                    broom::glance() %>% pull(r.squared)) %>% list()) %>% 
  unnest(lm) %>% 
  select(cell, mode, expt, bd, filt, dir, term:r.squared) %>% distinct() %>% 
  filter(p.value < 0.05) %>% 
  arrange(desc(statistic),p.value) 

tmp %>% 
  DT::datatable(rownames = F, filter = 'top', caption = 'abs(gene_score) ~ \u0394 fdr (ef1-ef0)', options = list(pageLength = 6)) %>% #
  DT::formatSignif(columns = c('statistic', 'std.error','r.squared', 'p.value', 'estimate'))
```

## Endolysosome
```{r}
# leading edge genes that were traced
input.gene.list <- enr.bd %>% 
  filter(
    Biodomain == 'Endolysosome',
    padj < 0.01,
    NES > 1.7
  ) %>% 
  pull(leadingEdge_genes) %>% 
  unlist() %>% 
  unique()

# synIDs of BD-specific NWs
nw.tbl = nw.dirs %>% 
  filter(bd == 'Endolysosome') %>% 
  select(bd, bd.filt, filt, dir, id)
nw.tbl <- tibble(
  base_nw = c('undir','undir_node','undir_edge','undir_node_edge',
              'dir','dir_node','dir_edge','dir_node_edge'),
  dir = c('undirected','undirected','undirected','undirected',
          'directed','directed','directed','directed'),
  filt = c('none','node','edge','node_edge',
           'none','node','edge','node_edge')
  ) %>% 
  left_join(nw.tbl, ., by = c('dir','filt'))

# synIDs of BD-specific wKDA results
kda.tbl = kda.dirs %>% 
  filter(bd == 'Endolysosome') %>% 
  select(bd, filt, dir, ef, id)

```

### NW properties
```{r}
# summarize NW properties
nw.tbl = bind_cols(
  nw.tbl,
  map_dfr(
    1:nrow(nw.tbl),
    ~ {
      nw = read_graph( synGet(nw.tbl$id[.x])$path, format = 'graphml' )
      tibble(
        n_nodes = nw %>% V %>% length,
        n_edges = nw %>% E %>% length,
        edge_per_node = n_edges/n_nodes,
        avg_node_degree = degree(nw, V(nw)) %>% mean(),
        avg_path_length = nw %>% average.path.length,
        assortativity_coef = nw %>% assortativity(., types1 = V(.)),
        connected_components = nw %>% no.clusters,
        missing = setdiff( input.gene.list, names(V( eval(parse(text = nw.tbl$base_nw[.x])) )) ) %>% list(),
        added = setdiff( names(V(nw)), input.gene.list ) %>% list()
      )
      }
    )
) 
```

Global properties of biodomain-filtered path traced networks
```{r fig.width=7, fig.height=8}
nw.tbl %>%
  filter(bd.filt) %>%
  mutate(
    network = paste( dir, filt, sep = '_') # bd.filt,
  ) %>% 
  rowwise() %>%
  mutate( missing = length(unique(unlist(missing))),
          added = length(unique(unlist(added)))
  ) %>% 
  select(network, n_nodes:added) %>% 
  pivot_longer(cols = c(-network), 
               names_to = 'properties', 
               values_to = 'val') %>% 
  mutate(network = factor(network, 
                       levels = c('undirected_none',
                                  'undirected_node',
                                  'undirected_edge',
                                  'undirected_node_edge',
                                  'directed_none',
                                  'directed_node',
                                  'directed_edge',
                                  'directed_node_edge')) ,
         properties = factor(properties, 
                             levels = c('n_nodes',
                                        'n_edges',
                                        'missing',
                                        'added',
                                        'edge_per_node', 
                                        'avg_node_degree',
                                        'avg_path_length',
                                        'assortativity_coef',
                                        'connected_components'
                                        )) 
         ) %>% 
  ggplot(aes(network, val)) +
  geom_bar(stat = 'identity', position = 'dodge')+
  theme(legend.position = 'top',
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))+
  labs(y = '',x = '')+
  # scale_y_log10()+
  facet_wrap(~properties, scales = 'free_y', ncol = 2)

```

### KDA results
```{r}
kd.res = kda.tbl %>% 
  # filter(dir == 'undirected') %>% 
  group_by(bd,filt,dir) %>%
  summarise( kd = list(read_kda_res(id[ef == 0],id[ef == 1])) ) %>% 
  unnest(kd) %>%  
  left_join(., 
            biodom %>% select(MODULE = GOterm_Name, Biodomain, color, abbr, label), 
            by = 'MODULE') %>% 
  ungroup() %>% 
  group_by(bd, filt, dir) %>% 
  arrange(MODULE, desc(ef1_fdr)) %>% 
  mutate(top_kd = if_else( duplicated(MODULE) , 0, 1)) %>% 
  relocate(top_kd, .after = 'MEMBER') %>% 
  ungroup()

en.kd.res <- kd.res
```

```{r fig.width=16,fig.height=8}
# p2 = 
kd.res %>% 
  # filter( ef1_fdr > -log10(0.05)
  #        # , MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
  #        , delta_fdr > 0
  #        ) %>%
  mutate(dir = fct_relevel(dir, c('undirected','directed')),
         filt = fct_relevel(filt, c('none','node','edge','node_edge'))) %>% 
  ggplot(aes( ef1_fdr, delta_fdr ))+
  labs(x = 'wKDA FDR ef1, -log10', y = '\u0394 FDR, ef1 - ef0', title = unique(kd.res$bd))+
  # geom_abline(intercept = 0, slope =1, lty= 2, lwd = .5)+
  geom_smooth(method = 'glm', lty = 2, lwd = .5, color = 'grey20')+
  geom_vline(xintercept = 0, lwd = .5)+ geom_hline(yintercept = 0, lwd = .5) +
  geom_point(alpha = .2, size = 1, aes(color = color) )+
  geom_point(data = subset(kd.res, ef1_fdr > -log10(0.05) & top_kd == 1 & delta_fdr > 0)
             , alpha = .6, size = 2, aes(color = color))+
  ggrepel::geom_label_repel(
    data = subset( kd.res, ef1_fdr > -log10(0.05)
                   & top_kd == 1
                   & MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
                   & delta_fdr > 0
                   ), 
    aes(label = paste0(NODE, '\n', MODULE, '\n', Biodomain)),
    size = 2, alpha = .7, min.segment.length = 0)+
  facet_wrap(dir~filt, scales = 'free', ncol = 4)+ #, scales = 'free'
  scale_color_identity(guide = 'none') #; plotly::ggplotly(p)

# plotly::ggplotly(p2)
```

### KD ~ Biodomains

```{r, fig.width=10}
kd.res %>% 
  filter(ef1_fdr > -log10(0.05)
         # , MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
         , delta_fdr > 0
         , top_kd == 1
         ) %>%
  mutate(pair = paste0(NODE,':',MODULE)) %>% 
  group_by(filt, dir, Biodomain) %>% 
  summarise(n_term = length(unique(MODULE)),
            n_node = length(unique(NODE)),
            n_kd = length(unique(pair)),
            # terms = list(unique(MODULE)),
            min_fdr = signif( 10^-max(ef1_fdr), digits = 3),
            max_delta = signif( max(delta_fdr), digits = 3) ) %>% 
  full_join(., 
            biodom %>% group_by(Biodomain) %>% mutate(n_go = length(unique(GO_ID))) %>% 
              select(Biodomain, n_go, abbr:color) %>% distinct(), 
            by = 'Biodomain') %>% 
  ungroup() %>%
  mutate(fxn_bd_term = n_term / n_go) %>% 
  filter(!is.na(filt), !is.na(dir)) %>% 
  mutate(#dir = fct_relevel(dir, c('undirected','directed')),
         filt = fct_relevel(filt, c('none','node','edge','node_edge')),
         Biodomain = fct_reorder(Biodomain, n_term)) %>% 
  arrange(Biodomain, desc(n_term), desc(max_delta)) %>% 
  ggplot(aes(n_term, Biodomain))+
  geom_segment(aes(yend=Biodomain, xend=0), color = 'grey50')+
  geom_point(aes(size = max_delta, color = color))+
  scale_color_identity()+
  labs(y='', 
       title = paste0(unique(kd.res$bd), ' Network Key Drivers'),
       subtitle = 'Biodomain GO terms')+ 
  theme(legend.position = 'bottom')+
  facet_wrap(dir~filt, ncol = 4)
```


```{r, fig.width=10}
kd.res %>% 
  filter(ef1_fdr > -log10(0.05)
         # , MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
         , delta_fdr > 0
         , top_kd == 1
         ) %>%
  mutate(pair = paste0(NODE,':',MODULE)) %>% 
  group_by(filt, dir, Biodomain) %>% 
  summarise(n_term = length(unique(MODULE)),
            n_node = length(unique(NODE)),
            n_kd = length(unique(pair)),
            # terms = list(unique(MODULE)),
            min_fdr = signif( 10^-max(ef1_fdr), digits = 3),
            max_delta = signif( max(delta_fdr), digits = 3) ) %>% 
  full_join(., 
            biodom %>% select(Biodomain, abbr:color) %>% distinct(), 
            by = 'Biodomain') %>% 
  arrange(desc(n_node), desc(max_delta), .by_group = T) %>% 
  ungroup() %>% 
  filter(!is.na(filt), !is.na(dir)) %>% 
  mutate(#dir = fct_relevel(dir, c('undirected','directed')),
         filt = fct_relevel(filt, c('none','node','edge','node_edge')),
         Biodomain = fct_reorder(Biodomain, n_node)) %>%
  ggplot(aes(n_node, Biodomain))+
  geom_segment(aes(yend=Biodomain, xend=0), color = 'grey50')+
  geom_point(aes(size = max_delta, color = color))+
  scale_color_identity()+
  labs(y='', 
       title = paste0(unique(kd.res$bd), ' Network Key Drivers'),
       subtitle = 'Nodes')+ 
  theme(legend.position = 'bottom')+
  facet_wrap(dir~filt, ncol = 4)
```

```{r fig.width=10,fig.height=10}
tmp <- kd.res %>% 
  filter( 
    ef1_fdr > -log10(0.05)
    # , MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
    , delta_fdr > 0 ,
    dir == 'undirected'
    , filt == 'node'
         )

ggplot(tmp, aes( ef1_fdr, delta_fdr ))+
  labs(x = 'wKDA FDR ef1, -log10', y = '\u0394 FDR, ef1 - ef0', 
       title = paste0(unique(tmp$bd), ': ', unique(tmp$dir),', ',unique(tmp$filt)),
       subtitle = 'signif KDs (EF1 FDR < 0.05), \u0394 FDR > 0, for GSEA-enriched terms'
       )+
  # geom_abline(intercept = 0, slope =1, lty= 2, lwd = .5)+
  geom_vline(xintercept = 0, lwd = .5)+ geom_hline(yintercept = 0, lwd = .5) +
  geom_point(alpha = .2, size = 1, aes(color = color) )+
  geom_point(data = subset(kd.res, ef1_fdr > -log10(0.05) & top_kd == 1 & delta_fdr > 0)
             , alpha = .6, size = 2, aes(color = color))+
  geom_smooth(method = 'glm', lty = 2, lwd = .5, color = 'grey20')+
  ggrepel::geom_label_repel(
    data = subset( kd.res, ef1_fdr > -log10(0.05)
                   & top_kd == 1
                   & MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
                   & delta_fdr > 0
                   ),
    aes(label = paste0(NODE, '\n', MODULE, '\n', Biodomain)),
    size = 2, alpha = .7, min.segment.length = 0)+
  facet_wrap(~Biodomain, scales = 'free')+ #, scales = 'free'
  scale_color_identity(guide = 'none') #; plotly::ggplotly(p)

# plotly::ggplotly(p2)
```

```{r}
kd.res %>% 
  filter(ef1_fdr > -log10(0.05)
         # , MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
         , delta_fdr > 0
         , top_kd == 1
         ) %>% 
  group_by(filt, dir, Biodomain) %>% 
  summarise(n_term = length(unique(MODULE)),
            # terms = list(unique(MODULE)),
            min_fdr = signif( 10^-max(ef1_fdr), digits = 3),
            max_delta = signif( max(delta_fdr), digits = 3) ) %>% 
  arrange(desc(n_term), desc(max_delta), .by_group = T) %>%
  DT::datatable(rownames = F, filter = 'top')
```

### Top KDs
```{r}
kd.summary = kd.res %>% 
  filter(ef1_fdr > -log10(0.05)
         , MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
         , delta_fdr > 0
         ) %>% 
  group_by(NODE, filt, dir) %>% 
  summarise(n_bd = length(unique(Biodomain)),
            bds = list(unique(Biodomain)),
            n_term = length(unique(MODULE)),
            terms = list(unique(MODULE)),
            min_fdr = signif( 10^-max(ef1_fdr), digits = 3),
            max_delta = signif( max(delta_fdr), digits = 3) ) %>% 
  arrange(desc(n_bd), desc(max_delta)) %>% 
  mutate(LE_gene = if_else(NODE %in% input.gene.list, 'Y', 'N')) %>% 
  relocate(LE_gene, .after = 'NODE')

DT::datatable(kd.summary %>% select(-bds, -terms), rownames = F, filter = 'top')
```

```{r}
kd.res %>% 
  filter(ef1_fdr > -log10(0.05)
         , top_kd == 1
         , MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
         , delta_fdr > 0
         ) %>% 
  select(bd, dir, filt, NODE, MODULE, MEMBER, contains('fdr')) %>% 
  arrange(desc(delta_fdr), desc(ef1_fdr)) %>% 
  mutate(LE_gene = if_else(NODE %in% input.gene.list, 'Y', 'N')) %>% 
  relocate(LE_gene, .after = 'NODE') %>% 
  DT::datatable(., rownames = F, filter = 'top') %>% 
  DT::formatSignif(columns = c('ef0_fdr','ef1_fdr','delta_fdr'))
```

### KD subnetworks
pull NW to view subgraphs
```{r}
nw = nw.tbl %>% 
  filter(
    dir == 'undirected', 
    filt == 'node_edge', 
    bd.filt == T
    ) %>% 
  pull(id) %>% 
  synGet(.) %>% 
  .$path %>% 
  read_graph(., format = 'graphml' )
```


```{r fig.width=12,fig.height=8}
p = suppressWarnings( plot_kd_subnet(nw, kd = 'IL1B', term = 'positive regulation of leukocyte migration') )
p
```


```{r fig.width=12,fig.height=8}
p = suppressWarnings( plot_kd_subnet(nw, kd = 'CAT', term = 'response to interleukin-1') )
p
```

```{r fig.width=12,fig.height=8}
p = suppressWarnings( plot_kd_subnet(nw, kd = 'CXCL8', term = 'positive regulation of inflammatory response') )
p
```

```{r fig.width=12,fig.height=8}
p = suppressWarnings( plot_kd_subnet(nw, kd = 'SNX9',term = 'clathrin-coated endocytic vesicle membrane') )
p
```

```{r fig.width=12,fig.height=8}
p = suppressWarnings( plot_kd_subnet(nw, kd = 'VCP', term = 'ubiquitin protein ligase binding') )
p
```

```{r fig.width=12,fig.height=8}
p = suppressWarnings( plot_kd_subnet(nw, kd = 'HIP1R', term = 'clathrin-coated endocytic vesicle') )
p
```

```{r fig.width=12,fig.height=8}
p = suppressWarnings( plot_kd_subnet(nw, kd = 'RAB3A', term = 'regulation of synaptic plasticity') )
p
```

### KDs ~ CBrain phenotypes
```{r fig.width=10, fig.height=5}
# crispr brain phenotype hits (any) vs non-hits
cb.hits = simple %>% filter(`Hit Class` != 'Non-Hit') %>% 
  pull(Gene) %>% unique()
cb.nonhits = simple %>% filter( (Gene %in% cb.hits)==F ) %>% 
  pull(Gene) %>% unique()

# ID key drivers from different parameter sets
comb = kd.res %>% select(filt, dir) %>% distinct() %>% arrange(dir,filt)
comb$kd.hits = map(
  1:nrow(comb),
  ~ kd.res %>% filter(ef1_fdr > -log10(0.05), 
                      filt == comb$filt[.x],
                      dir == comb$dir[.x]) %>% pull(NODE) %>% unique()
)
comb$kd.nonhits = map(
  1:nrow(comb),
  ~ kd.res %>% filter( (NODE %in% comb$kd.hits[[.x]])==F ) %>% 
    pull(NODE) %>% unique()
)

# calculate fisher stats 
comb = map_dfr(
  1:nrow(comb),
  ~ bind_cols(
      pheno_kd = intersect(cb.hits, comb$kd.hits[[.x]]) %>% length(),
      noPheno_kd = intersect(cb.nonhits, comb$kd.hits[[.x]]) %>% length(),
      pheno_nokd = intersect(cb.hits, comb$kd.nonhits[[.x]]) %>% length(),
      noPheno_nokd = intersect(cb.nonhits, comb$kd.nonhits[[.x]]) %>% length()
    ) %>% 
    rowwise() %>% mutate(
      fisher.p = matrix(c(pheno_kd, noPheno_kd, pheno_nokd, noPheno_nokd), 
                        nrow = 2) %>% 
      fisher.test( ., alt = 'g') %>% broom::tidy() %>% pull(p.value)
    )
) %>% 
  bind_cols(comb, .)

# make plots for each comb
plist = map(
  1:nrow(comb),
  ~ plot( eulerr::euler(
    c(pheno = length(cb.hits),
      kd = length(comb$kd.hits[[.x]]), 
      'pheno&kd' = comb$pheno_kd[.x])
    , quantities = T )
    ) %>% 
    ggplotify::as.ggplot() + 
    ggtitle(label = kd.res$bd %>% unique,
            subtitle = paste0(
            'dir: ', comb$dir[.x],', filt: ', comb$filt[.x],
            '\nFisher p = ', comb$fisher.p[.x] %>% signif(digits = 2) )
            ) 
)

cowplot::plot_grid(plotlist = plist, ncol = 4)


```

Lysotracker phenotypes only
```{r fig.width=10, fig.height=5}
# crispr brain phenotype hits (any) vs non-hits
cb.hits = simple %>% 
  filter( expt %in% c('Lysotracker','LysoTracker-ITC','LysoTracker-Veh'), `Hit Class` != 'Non-Hit') %>% 
  pull(Gene) %>% unique()
cb.nonhits = simple %>% 
  filter( expt %in% c('Lysotracker','LysoTracker-ITC','LysoTracker-Veh'),  (Gene %in% cb.hits)==F ) %>% 
  pull(Gene) %>% unique()

# ID key drivers from different parameter sets
comb = kd.res %>% select(filt, dir) %>% distinct() %>% arrange(dir,filt)
comb$kd.hits = map(
  1:nrow(comb),
  ~ kd.res %>% filter(ef1_fdr > -log10(0.05), 
                      filt == comb$filt[.x],
                      dir == comb$dir[.x]) %>% pull(NODE) %>% unique()
)
comb$kd.nonhits = map(
  1:nrow(comb),
  ~ kd.res %>% filter( (NODE %in% comb$kd.hits[[.x]])==F ) %>% 
    pull(NODE) %>% unique()
)

# calculate fisher stats 
comb = map_dfr(
  1:nrow(comb),
  ~ bind_cols(
      pheno_kd = intersect(cb.hits, comb$kd.hits[[.x]]) %>% length(),
      noPheno_kd = intersect(cb.nonhits, comb$kd.hits[[.x]]) %>% length(),
      pheno_nokd = intersect(cb.hits, comb$kd.nonhits[[.x]]) %>% length(),
      noPheno_nokd = intersect(cb.nonhits, comb$kd.nonhits[[.x]]) %>% length()
    ) %>% 
    rowwise() %>% mutate(
      fisher.p = matrix(c(pheno_kd, noPheno_kd, pheno_nokd, noPheno_nokd), 
                        nrow = 2) %>% 
      fisher.test( ., alt = 'g') %>% broom::tidy() %>% pull(p.value)
    )
) %>% 
  bind_cols(comb, .)

# make plots for each comb
plist = map(
  1:nrow(comb),
  ~ plot( eulerr::euler(
    c(pheno = length(cb.hits),
      kd = length(comb$kd.hits[[.x]]), 
      'pheno&kd' = comb$pheno_kd[.x])
    , quantities = T )
    ) %>% 
    ggplotify::as.ggplot() + 
    ggtitle(label = kd.res$bd %>% unique,
            subtitle = paste0(
            'dir: ', comb$dir[.x],', filt: ', comb$filt[.x],
            '\nFisher p = ', comb$fisher.p[.x] %>% signif(digits = 2) )
            ) 
)

cowplot::plot_grid(plotlist = plist, ncol = 4)


```


linear regression  ~ KDA FDR
```{r}
tmp <- kd.res %>% inner_join( simple,., by =c('Gene'='NODE')) %>% 
  group_by(cell,mode,expt, bd, filt, dir) %>% 
  mutate(lm = lm(abs(gene_score)~ef1_fdr) %>% broom::tidy() %>% 
           filter(term != '(Intercept)') %>% 
           mutate(r.squared = lm(abs(gene_score)~ef1_fdr) %>% 
                    broom::glance() %>% pull(r.squared)) %>% list()) %>% 
  unnest(lm)  %>% 
  select(cell, mode, expt, bd.nw = bd, nw.filt = filt, nw.dir=dir, term:r.squared) %>% distinct() %>% 
  filter(p.value < 0.05) %>% 
  arrange(desc(statistic),p.value)

tmp %>% 
  DT::datatable(rownames = F, filter = 'top', caption = 'abs(gene_score) ~ ef1_fdr', options = list(pageLength = 6)) %>% #
  DT::formatSignif(columns = c('statistic', 'std.error','r.squared', 'p.value', 'estimate'))
```

```{r fig.width=10, fig.height=5}
c = 'Glutamatergic Neuron'
m = 'CRISPRi'
e = 'FeRhoNox'

kd.res %>% inner_join( simple,., by =c('Gene'='NODE')) %>%
  filter(
    cell == c,
    mode == m,
    expt == e,
    ef1_fdr > -log10(0.2)
    ) %>% 
  ggplot( aes( ef1_fdr, abs(gene_score) )) +
  geom_point(#data = subset(tmp, d > 0),
             aes(color = color,  size = delta_fdr), alpha = .5) +
  geom_hline(yintercept = 0, lwd = 0.5)+
  geom_vline(xintercept = 0, lwd = 0.5)+
  scale_size_continuous(name = 'KDA \u0394 FDR\nef1-ef0', range = c(.5,3))+ 
  # ggrepel::geom_label_repel(
  #   data = subset(tmp, d > 0), aes(label = paste0(Gene,'\n', go)),
  #   min.segment.length = 0, size = 2.5, max.overlaps = 12)+
  scale_color_identity(guide = 'none')+
  geom_smooth(method = 'lm', color = 'grey20',lty=2)+
  labs(y = 'CRISPRbrain phenotype score, absolute value',
       x = 'KDA FDR, -log10',
       title = paste0(c,', ',m,', ',e)) + 
  facet_grid(dir~filt, scales = 'free_x')
```
```{r fig.width=10, fig.height=5}
c = 'Glutamatergic Neuron'
m = 'CRISPRi'
e = 'Lysotracker'

kd.res %>% inner_join( simple,., by =c('Gene'='NODE')) %>%
  filter(
    cell == c,
    mode == m,
    expt == e,
    ef1_fdr > -log10(0.2)
    ) %>% 
  ggplot( aes( ef1_fdr, abs(gene_score) )) +
  geom_point(#data = subset(tmp, d > 0),
             aes(color = color,  size = delta_fdr), alpha = .5) +
  geom_hline(yintercept = 0, lwd = 0.5)+
  geom_vline(xintercept = 0, lwd = 0.5)+
  scale_size_continuous(name = 'KDA \u0394 FDR\nef1-ef0', range = c(.5,3))+ 
  # ggrepel::geom_label_repel(
  #   data = subset(tmp, d > 0), aes(label = paste0(Gene,'\n', go)),
  #   min.segment.length = 0, size = 2.5, max.overlaps = 12)+
  scale_color_identity(guide = 'none')+
  geom_smooth(method = 'lm', color = 'grey20',lty=2)+
  labs(y = 'CRISPRbrain phenotype score, absolute value',
       x = 'KDA FDR, -log10',
       title = paste0(c,', ',m,', ',e)) + 
  facet_grid(dir~filt, scales = 'free_x')
```
linear regression ~  KDA delta FDR e1/e0
```{r}
tmp <- kd.res %>% inner_join( simple,., by =c('Gene'='NODE')) %>% 
  group_by(cell,mode,expt, bd, filt, dir) %>% 
  mutate(lm = lm(abs(gene_score)~delta_fdr) %>% broom::tidy() %>% 
           filter(term != '(Intercept)') %>% 
           mutate(r.squared = lm(abs(gene_score)~delta_fdr) %>% 
                    broom::glance() %>% pull(r.squared)) %>% list()) %>% 
  unnest(lm) %>% 
  select(cell, mode, expt, bd, filt, dir, term:r.squared) %>% distinct() %>% 
  filter(p.value < 0.05) %>% 
  arrange(desc(statistic),p.value) 

tmp %>% 
  DT::datatable(rownames = F, filter = 'top', caption = 'abs(gene_score) ~ \u0394 fdr (ef1-ef0)', options = list(pageLength = 6)) %>% #
  DT::formatSignif(columns = c('statistic', 'std.error','r.squared', 'p.value', 'estimate'))
```


```{r fig.width=10, fig.height=5}
c = 'Glutamatergic Neuron'
m = 'CRISPRi'
e = 'Lysotracker'

kd.res %>% inner_join( simple,., by =c('Gene'='NODE')) %>%
  filter(
    cell == c,
    mode == m,
    expt == e,
    ef1_fdr > -log10(0.2)
    ) %>% 
  ggplot( aes( delta_fdr, abs(gene_score) )) +
  geom_point(#data = subset(tmp, d > 0),
             aes(color = color,  size = ef1_fdr), alpha = .5) +
  geom_hline(yintercept = 0, lwd = 0.5)+
  geom_vline(xintercept = 0, lwd = 0.5)+
  scale_size_continuous(name = 'KDA \u0394 FDR\nef1-ef0', range = c(.5,3))+ 
  # ggrepel::geom_label_repel(
  #   data = subset(tmp, d > 0), aes(label = paste0(Gene,'\n', go)),
  #   min.segment.length = 0, size = 2.5, max.overlaps = 12)+
  scale_color_identity(guide = 'none')+
  geom_smooth(method = 'lm', color = 'grey20',lty=2)+
  labs(y = 'CRISPRbrain phenotype score, absolute value',
       x = 'KDA FDR, -log10',
       title = paste0(c,', ',m,', ',e)) + 
  facet_grid(dir~filt, scales = 'free_x')
```


## Immune Response
```{r}
# leading edge genes that were traced
input.gene.list <- enr.bd %>% 
  filter(
    Biodomain == 'Immune Response',
    padj < 0.01,
    NES > 1.7
  ) %>% 
  pull(leadingEdge_genes) %>% 
  unlist() %>% 
  unique()

# synIDs of BD-specific NWs
nw.tbl = nw.dirs %>% 
  filter(bd == 'Immune Response') %>% 
  select(bd, bd.filt, filt, dir, id)
nw.tbl <- tibble(
  base_nw = c('undir','undir_node','undir_edge','undir_node_edge',
              'dir','dir_node','dir_edge','dir_node_edge'),
  dir = c('undirected','undirected','undirected','undirected',
          'directed','directed','directed','directed'),
  filt = c('none','node','edge','node_edge',
           'none','node','edge','node_edge')
  ) %>% 
  left_join(nw.tbl, ., by = c('dir','filt'))

# synIDs of BD-specific wKDA results
kda.tbl = kda.dirs %>% 
  filter(bd == 'Immune Response') %>% 
  select(bd, filt, dir, ef, id)

```

### NW properties
```{r}
# summarize NW properties
nw.tbl = bind_cols(
  nw.tbl,
  map_dfr(
    1:nrow(nw.tbl),
    ~ {
      nw = read_graph( synGet(nw.tbl$id[.x])$path, format = 'graphml' )
      tibble(
        n_nodes = nw %>% V %>% length,
        n_edges = nw %>% E %>% length,
        edge_per_node = n_edges/n_nodes,
        avg_node_degree = degree(nw, V(nw)) %>% mean(),
        avg_path_length = nw %>% average.path.length,
        assortativity_coef = nw %>% assortativity(., types1 = V(.)),
        connected_components = nw %>% no.clusters,
        missing = setdiff( input.gene.list, names(V( eval(parse(text = nw.tbl$base_nw[.x])) )) ) %>% list(),
        added = setdiff( names(V(nw)), input.gene.list ) %>% list()
      )
      }
    )
) 
```

Global properties of biodomain-filtered path traced networks
```{r fig.width=7, fig.height=8}
nw.tbl %>%
  filter(bd.filt) %>%
  mutate(
    network = paste( dir, filt, sep = '_') # bd.filt,
  ) %>% 
  rowwise() %>%
  mutate( missing = length(unique(unlist(missing))),
          added = length(unique(unlist(added)))
  ) %>% 
  select(network, n_nodes:added) %>% 
  pivot_longer(cols = c(-network), 
               names_to = 'properties', 
               values_to = 'val') %>% 
  mutate(network = factor(network, 
                       levels = c('undirected_none',
                                  'undirected_node',
                                  'undirected_edge',
                                  'undirected_node_edge',
                                  'directed_none',
                                  'directed_node',
                                  'directed_edge',
                                  'directed_node_edge')) ,
         properties = factor(properties, 
                             levels = c('n_nodes',
                                        'n_edges',
                                        'missing',
                                        'added',
                                        'edge_per_node', 
                                        'avg_node_degree',
                                        'avg_path_length',
                                        'assortativity_coef',
                                        'connected_components'
                                        )) 
         ) %>% 
  ggplot(aes(network, val)) +
  geom_bar(stat = 'identity', position = 'dodge')+
  theme(legend.position = 'top',
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))+
  labs(y = '',x = '')+
  # scale_y_log10()+
  facet_wrap(~properties, scales = 'free_y', ncol = 2)

```

### KDA results
```{r}
kd.res = kda.tbl %>% 
  # filter(dir == 'undirected') %>% 
  group_by(bd,filt,dir) %>%
  summarise( kd = list(read_kda_res(id[ef == 0],id[ef == 1])) ) %>% 
  unnest(kd) %>%  
  left_join(., 
            biodom %>% select(MODULE = GOterm_Name, Biodomain, color, abbr, label), 
            by = 'MODULE') %>% 
  ungroup() %>% 
  group_by(bd, filt, dir) %>% 
  arrange(MODULE, desc(ef1_fdr)) %>% 
  mutate(top_kd = if_else( duplicated(MODULE), 0, 1)) %>% 
  relocate(top_kd, .after = 'MEMBER') %>% 
  ungroup()

ir.kd.res <- kd.res
```

```{r fig.width=16,fig.height=8}
# p2 = 
kd.res %>% 
  # filter( ef1_fdr > -log10(0.05)
  #        # , MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
  #        , delta_fdr > 0
  #        ) %>%
  mutate(dir = fct_relevel(dir, c('undirected','directed')),
         filt = fct_relevel(filt, c('none','node','edge','node_edge'))) %>% 
  ggplot(aes( ef1_fdr, delta_fdr ))+
  labs(x = 'wKDA FDR ef1, -log10', y = '\u0394 FDR, ef1 - ef0', title = unique(kd.res$bd))+
  # geom_abline(intercept = 0, slope =1, lty= 2, lwd = .5)+
  geom_smooth(method = 'glm', lty = 2, lwd = .5, color = 'grey20')+
  geom_vline(xintercept = 0, lwd = .5)+ geom_hline(yintercept = 0, lwd = .5) +
  geom_point(alpha = .2, size = 1, aes(color = color) )+
  geom_point(data = subset(kd.res, ef1_fdr > -log10(0.05) & top_kd == 1 & delta_fdr > 0)
             , alpha = .6, size = 2, aes(color = color))+
  ggrepel::geom_label_repel(
    data = subset( kd.res, ef1_fdr > -log10(0.05)
                   & top_kd == 1
                   & MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
                   & delta_fdr > 0
                   ), 
    aes(label = paste0(NODE, '\n', MODULE, '\n', Biodomain)),
    size = 2, alpha = .7, min.segment.length = 0)+
  facet_wrap(dir~filt, scales = 'free', ncol = 4)+ #, scales = 'free'
  scale_color_identity(guide = 'none') #; plotly::ggplotly(p)

# plotly::ggplotly(p2)
```

### KD ~ Biodomains

```{r, fig.width=10}
kd.res %>% 
  filter(ef1_fdr > -log10(0.05)
         # , MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
         , delta_fdr > 0
         , top_kd == 1
         ) %>%
  mutate(pair = paste0(NODE,':',MODULE)) %>% 
  group_by(filt, dir, Biodomain) %>% 
  summarise(n_term = length(unique(MODULE)),
            n_node = length(unique(NODE)),
            n_kd = length(unique(pair)),
            # terms = list(unique(MODULE)),
            min_fdr = signif( 10^-max(ef1_fdr), digits = 3),
            max_delta = signif( max(delta_fdr), digits = 3) ) %>% 
  full_join(., 
            biodom %>% group_by(Biodomain) %>% mutate(n_go = length(unique(GO_ID))) %>% 
              select(Biodomain, n_go, abbr:color) %>% distinct(), 
            by = 'Biodomain') %>% 
  ungroup() %>%
  mutate(fxn_bd_term = n_term / n_go) %>% 
  filter(!is.na(filt), !is.na(dir)) %>% 
  mutate(#dir = fct_relevel(dir, c('undirected','directed')),
         filt = fct_relevel(filt, c('none','node','edge','node_edge')),
         Biodomain = fct_reorder(Biodomain, n_term)) %>% 
  arrange(Biodomain, desc(n_term), desc(max_delta)) %>% 
  ggplot(aes(n_term, Biodomain))+
  geom_segment(aes(yend=Biodomain, xend=0), color = 'grey50')+
  geom_point(aes(size = max_delta, color = color))+
  scale_color_identity()+
  labs(y='', 
       title = paste0(unique(kd.res$bd), ' Network Key Drivers'),
       subtitle = 'Biodomain GO terms')+ 
  theme(legend.position = 'bottom')+
  facet_wrap(dir~filt, ncol = 4)
```


```{r, fig.width=10}
kd.res %>% 
  filter(ef1_fdr > -log10(0.05)
         # , MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
         , delta_fdr > 0
         , top_kd == 1
         ) %>%
  mutate(pair = paste0(NODE,':',MODULE)) %>% 
  group_by(filt, dir, Biodomain) %>% 
  summarise(n_term = length(unique(MODULE)),
            n_node = length(unique(NODE)),
            n_kd = length(unique(pair)),
            # terms = list(unique(MODULE)),
            min_fdr = signif( 10^-max(ef1_fdr), digits = 3),
            max_delta = signif( max(delta_fdr), digits = 3) ) %>% 
  full_join(., 
            biodom %>% select(Biodomain, abbr:color) %>% distinct(), 
            by = 'Biodomain') %>% 
  arrange(desc(n_node), desc(max_delta), .by_group = T) %>% 
  ungroup() %>% 
  filter(!is.na(filt), !is.na(dir)) %>% 
  mutate(#dir = fct_relevel(dir, c('undirected','directed')),
         filt = fct_relevel(filt, c('none','node','edge','node_edge')),
         Biodomain = fct_reorder(Biodomain, n_node)) %>%
  ggplot(aes(n_node, Biodomain))+
  geom_segment(aes(yend=Biodomain, xend=0), color = 'grey50')+
  geom_point(aes(size = max_delta, color = color))+
  scale_color_identity()+
  labs(y='', 
       title = paste0(unique(kd.res$bd), ' Network Key Drivers'),
       subtitle = 'Nodes')+ 
  theme(legend.position = 'bottom')+
  facet_wrap(dir~filt, ncol = 4)
```

```{r fig.width=10,fig.height=10}
tmp <- kd.res %>% 
  filter( 
    ef1_fdr > -log10(0.05)
    # , MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
    , delta_fdr > 0 ,
    dir == 'undirected'
    , filt == 'node'
         )

ggplot(tmp, aes( ef1_fdr, delta_fdr ))+
  labs(x = 'wKDA FDR ef1, -log10', y = '\u0394 FDR, ef1 - ef0', 
       title = paste0(unique(tmp$bd), ': ', unique(tmp$dir),', ',unique(tmp$filt)),
       subtitle = 'signif KDs (EF1 FDR < 0.05), \u0394 FDR > 0, for GSEA-enriched terms'
       )+
  # geom_abline(intercept = 0, slope =1, lty= 2, lwd = .5)+
  geom_vline(xintercept = 0, lwd = .5)+ geom_hline(yintercept = 0, lwd = .5) +
  geom_point(alpha = .2, size = 1, aes(color = color) )+
  geom_point(data = subset(kd.res, ef1_fdr > -log10(0.05) & top_kd == 1 & delta_fdr > 0)
             , alpha = .6, size = 2, aes(color = color))+
  geom_smooth(method = 'glm', lty = 2, lwd = .5, color = 'grey20')+
  # ggrepel::geom_label_repel(
  #   data = subset( kd.res, ef1_fdr > -log10(0.05)
  #                  & top_kd == 1
  #                  & MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
  #                  & delta_fdr > 0
  #                  ),
  #   aes(label = paste0(NODE, '\n', MODULE, '\n', Biodomain)),
  #   size = 2, alpha = .7, min.segment.length = 0)+
  facet_wrap(~Biodomain)+ #, scales = 'free'
  scale_color_identity(guide = 'none') #; plotly::ggplotly(p)

# plotly::ggplotly(p2)
```

```{r}
kd.res %>% 
  filter(ef1_fdr > -log10(0.05)
         # , MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
         , delta_fdr > 0
         , top_kd == 1
         ) %>% 
  group_by(filt, dir, Biodomain) %>% 
  summarise(n_term = length(unique(MODULE)),
            # terms = list(unique(MODULE)),
            min_fdr = signif( 10^-max(ef1_fdr), digits = 3),
            max_delta = signif( max(delta_fdr), digits = 3) ) %>% 
  arrange(desc(n_term), desc(max_delta), .by_group = T) %>%
  DT::datatable(rownames = F, filter = 'top')
```
### Top KDs
```{r}
kd.summary = kd.res %>% 
  filter(ef1_fdr > -log10(0.05)
         , MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
         , delta_fdr > 0
         ) %>% 
  group_by(NODE, filt, dir) %>% 
  summarise(n_bd = length(unique(Biodomain)),
            bds = list(unique(Biodomain)),
            n_term = length(unique(MODULE)),
            terms = list(unique(MODULE)),
            min_fdr = signif( 10^-max(ef1_fdr), digits = 3),
            max_delta = signif( max(delta_fdr), digits = 3) ) %>% 
  arrange(desc(n_bd), desc(max_delta)) %>% 
  mutate(LE_gene = if_else(NODE %in% input.gene.list, 'Y', 'N')) %>% 
  relocate(LE_gene, .after = 'NODE')

DT::datatable(kd.summary %>% select(-bds, -terms), rownames = F, filter = 'top')
```

```{r}
kd.res %>% 
  filter(ef1_fdr > -log10(0.05)
         , top_kd == 1
         , MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
         , delta_fdr > 0
         ) %>% 
  select(bd, dir, filt, NODE, MODULE, Biodomain, MEMBER, contains('fdr')) %>% 
  arrange(desc(delta_fdr), desc(ef1_fdr)) %>% 
  mutate(LE_gene = if_else(NODE %in% input.gene.list, 'Y', 'N')) %>% 
  relocate(LE_gene, .after = 'NODE') %>% 
  DT::datatable(., rownames = F, filter = 'top') %>% 
  DT::formatSignif(columns = c('ef0_fdr','ef1_fdr','delta_fdr'))
```



### KD subnetworks
pull NW to view subgraphs
```{r}
nw = nw.tbl %>% 
  filter(
    dir == 'undirected', 
    filt == 'node', 
    bd.filt == T
    ) %>% 
  pull(id) %>% 
  synGet(.) %>% 
  .$path %>% 
  read_graph(., format = 'graphml' )
```

```{r fig.width=12,fig.height=8}
p = suppressWarnings( plot_kd_subnet(nw, kd = 'ALOX5',term = 'regulation of oxidative stress-induced cell death') )
p
```

```{r fig.width=12,fig.height=8}
p = suppressWarnings( plot_kd_subnet(nw, kd = 'IKBKG', term = 'I-kappaB kinase/NF-kappaB signaling') )
p
```

```{r fig.width=12,fig.height=8}
p = suppressWarnings( plot_kd_subnet(nw, kd = 'PRKCA', term = 'extrinsic component of cytoplasmic side of plasma membrane') )
p
```

```{r fig.width=12,fig.height=8}
p = suppressWarnings( plot_kd_subnet(nw, kd = 'TRAF2', term = 'tumor necrosis factor-mediated signaling pathway') )
p
```


### KDs ~ CBrain phenotypes
```{r fig.width=10, fig.height=5}
# crispr brain phenotype hits (any) vs non-hits
cb.hits = simple %>% filter(`Hit Class` != 'Non-Hit') %>% 
  pull(Gene) %>% unique()
cb.nonhits = simple %>% filter( (Gene %in% cb.hits)==F ) %>% 
  pull(Gene) %>% unique()

# ID key drivers from different parameter sets
comb = kd.res %>% select(filt, dir) %>% distinct() %>% arrange(dir,filt)
comb$kd.hits = map(
  1:nrow(comb),
  ~ kd.res %>% filter(ef1_fdr > -log10(0.05), 
                      filt == comb$filt[.x],
                      dir == comb$dir[.x]) %>% pull(NODE) %>% unique()
)
comb$kd.nonhits = map(
  1:nrow(comb),
  ~ kd.res %>% filter( (NODE %in% comb$kd.hits[[.x]])==F ) %>% 
    pull(NODE) %>% unique()
)

# calculate fisher stats 
comb = map_dfr(
  1:nrow(comb),
  ~ bind_cols(
      pheno_kd = intersect(cb.hits, comb$kd.hits[[.x]]) %>% length(),
      noPheno_kd = intersect(cb.nonhits, comb$kd.hits[[.x]]) %>% length(),
      pheno_nokd = intersect(cb.hits, comb$kd.nonhits[[.x]]) %>% length(),
      noPheno_nokd = intersect(cb.nonhits, comb$kd.nonhits[[.x]]) %>% length()
    ) %>% 
    rowwise() %>% mutate(
      fisher.p = matrix(c(pheno_kd, noPheno_kd, pheno_nokd, noPheno_nokd), 
                        nrow = 2) %>% 
      fisher.test( ., alt = 'g') %>% broom::tidy() %>% pull(p.value)
    )
) %>% 
  bind_cols(comb, .)

# make plots for each comb
plist = map(
  1:nrow(comb),
  ~ plot( eulerr::euler(
    c(pheno = length(cb.hits),
      kd = length(comb$kd.hits[[.x]]), 
      'pheno&kd' = comb$pheno_kd[.x])
    , quantities = T )
    ) %>% 
    ggplotify::as.ggplot() + 
    ggtitle(label = kd.res$bd %>% unique,
            subtitle = paste0(
            'dir: ', comb$dir[.x],', filt: ', comb$filt[.x],
            '\nFisher p = ', comb$fisher.p[.x] %>% signif(digits = 2) )
            ) 
)

cowplot::plot_grid(plotlist = plist, ncol = 4)


```


linear regression  ~ KDA FDR
```{r}
tmp <- kd.res %>% inner_join( simple,., by =c('Gene'='NODE')) %>% 
  group_by(cell,mode,expt, bd, filt, dir) %>% 
  mutate(lm = lm(abs(gene_score)~ef1_fdr) %>% broom::tidy() %>% 
           filter(term != '(Intercept)') %>% 
           mutate(r.squared = lm(abs(gene_score)~ef1_fdr) %>% 
                    broom::glance() %>% pull(r.squared)) %>% list()) %>% 
  unnest(lm)  %>% 
  select(cell, mode, expt, bd.nw = bd, nw.filt = filt, nw.dir=dir, term:r.squared) %>% distinct() %>% 
  filter(p.value < 0.05) %>% 
  arrange(desc(statistic),p.value)

tmp %>% 
  DT::datatable(rownames = F, filter = 'top', caption = 'abs(gene_score) ~ ef1_fdr', options = list(pageLength = 6)) %>% #
  DT::formatSignif(columns = c('statistic', 'std.error','r.squared', 'p.value', 'estimate'))
```

```{r fig.width=10, fig.height=5}
c = 'Glutamatergic Neuron'
m = 'CRISPRi'
e = 'Survival'

kd.res %>% inner_join( simple,., by =c('Gene'='NODE')) %>%
  filter(
    cell == c,
    mode == m,
    expt == e,
    ef1_fdr > -log10(0.2)
    ) %>% 
  ggplot( aes( ef1_fdr, abs(gene_score) )) +
  geom_point(#data = subset(tmp, d > 0),
             aes(color = color,  size = delta_fdr), alpha = .5) +
  geom_hline(yintercept = 0, lwd = 0.5)+
  geom_vline(xintercept = 0, lwd = 0.5)+
  scale_size_continuous(name = 'KDA \u0394 FDR\nef1-ef0', range = c(.5,3))+ 
  # ggrepel::geom_label_repel(
  #   data = subset(tmp, d > 0), aes(label = paste0(Gene,'\n', go)),
  #   min.segment.length = 0, size = 2.5, max.overlaps = 12)+
  scale_color_identity(guide = 'none')+
  geom_smooth(method = 'lm', color = 'grey20',lty=2)+
  labs(y = 'CRISPRbrain phenotype score, absolute value',
       x = 'KDA FDR, -log10',
       title = paste0(c,', ',m,', ',e)) + 
  facet_grid(dir~filt, scales = 'free_x')
```

linear regression ~  KDA delta FDR e1/e0
```{r}
tmp <- kd.res %>% inner_join( simple,., by =c('Gene'='NODE')) %>% 
  group_by(cell,mode,expt, bd, filt, dir) %>% 
  mutate(lm = lm(abs(gene_score)~delta_fdr) %>% broom::tidy() %>% 
           filter(term != '(Intercept)') %>% 
           mutate(r.squared = lm(abs(gene_score)~delta_fdr) %>% 
                    broom::glance() %>% pull(r.squared)) %>% list()) %>% 
  unnest(lm) %>% 
  select(cell, mode, expt, bd, filt, dir, term:r.squared) %>% distinct() %>% 
  filter(p.value < 0.05) %>% 
  arrange(desc(statistic),p.value) 

tmp %>% 
  DT::datatable(rownames = F, filter = 'top', caption = 'abs(gene_score) ~ \u0394 fdr (ef1-ef0)', options = list(pageLength = 6)) %>% #
  DT::formatSignif(columns = c('statistic', 'std.error','r.squared', 'p.value', 'estimate'))
```

```{r fig.width=10, fig.height=5}
c = 'iTF-Microglia'
m = 'CRISPRi'
e = 'Phagocytosis'

kd.res %>% inner_join( simple,., by =c('Gene'='NODE')) %>%
  filter(
    cell == c,
    mode == m,
    expt == e,
    ef1_fdr > -log10(0.2)
    ) %>% 
  ggplot( aes( delta_fdr, abs(gene_score) )) +
  geom_point(#data = subset(tmp, d > 0),
             aes(color = color,  size = ef1_fdr), alpha = .5) +
  geom_hline(yintercept = 0, lwd = 0.5)+
  geom_vline(xintercept = 0, lwd = 0.5)+
  scale_size_continuous(name = 'KDA \u0394 FDR\nef1-ef0', range = c(.5,3))+ 
  # ggrepel::geom_label_repel(
  #   data = subset(tmp, d > 0), aes(label = paste0(Gene,'\n', go)),
  #   min.segment.length = 0, size = 2.5, max.overlaps = 12)+
  scale_color_identity(guide = 'none')+
  geom_smooth(method = 'lm', color = 'grey20',lty=2)+
  labs(y = 'CRISPRbrain phenotype score, absolute value',
       x = 'KDA FDR, -log10',
       title = paste0(c,', ',m,', ',e)) + 
  facet_grid(dir~filt, scales = 'free_x')
```

## Lipid Metabolism
```{r}
# leading edge genes that were traced
input.gene.list <- enr.bd %>% 
  filter(
    Biodomain == 'Lipid Metabolism',
    padj < 0.01,
    NES > 1.7
  ) %>% 
  pull(leadingEdge_genes) %>% 
  unlist() %>% 
  unique()

# synIDs of BD-specific NWs
nw.tbl = nw.dirs %>% 
  filter(bd == 'Lipid Metabolism') %>% 
  select(bd, bd.filt, filt, dir, id)
nw.tbl <- tibble(
  base_nw = c('undir','undir_node','undir_edge','undir_node_edge',
              'dir','dir_node','dir_edge','dir_node_edge'),
  dir = c('undirected','undirected','undirected','undirected',
          'directed','directed','directed','directed'),
  filt = c('none','node','edge','node_edge',
           'none','node','edge','node_edge')
  ) %>% 
  left_join(nw.tbl, ., by = c('dir','filt'))

# synIDs of BD-specific wKDA results
kda.tbl = kda.dirs %>% 
  filter(bd == 'Lipid Metabolism') %>% 
  select(bd, filt, dir, ef, id)

```

### NW properties
```{r}
# summarize NW properties
nw.tbl = bind_cols(
  nw.tbl,
  map_dfr(
    1:nrow(nw.tbl),
    ~ {
      nw = read_graph( synGet(nw.tbl$id[.x])$path, format = 'graphml' )
      tibble(
        n_nodes = nw %>% V %>% length,
        n_edges = nw %>% E %>% length,
        edge_per_node = n_edges/n_nodes,
        avg_node_degree = degree(nw, V(nw)) %>% mean(),
        avg_path_length = nw %>% average.path.length,
        assortativity_coef = nw %>% assortativity(., types1 = V(.)),
        connected_components = nw %>% no.clusters,
        missing = setdiff( input.gene.list, names(V( eval(parse(text = nw.tbl$base_nw[.x])) )) ) %>% list(),
        added = setdiff( names(V(nw)), input.gene.list ) %>% list()
      )
      }
    )
) 
```

Global properties of biodomain-filtered path traced networks
```{r fig.width=7, fig.height=8}
nw.tbl %>%
  filter(bd.filt) %>%
  mutate(
    network = paste( dir, filt, sep = '_') # bd.filt,
  ) %>% 
  rowwise() %>%
  mutate( missing = length(unique(unlist(missing))),
          added = length(unique(unlist(added)))
  ) %>% 
  select(network, n_nodes:added) %>% 
  pivot_longer(cols = c(-network), 
               names_to = 'properties', 
               values_to = 'val') %>% 
  mutate(network = factor(network, 
                       levels = c('undirected_none',
                                  'undirected_node',
                                  'undirected_edge',
                                  'undirected_node_edge',
                                  'directed_none',
                                  'directed_node',
                                  'directed_edge',
                                  'directed_node_edge')) ,
         properties = factor(properties, 
                             levels = c('n_nodes',
                                        'n_edges',
                                        'missing',
                                        'added',
                                        'edge_per_node', 
                                        'avg_node_degree',
                                        'avg_path_length',
                                        'assortativity_coef',
                                        'connected_components'
                                        )) 
         ) %>% 
  ggplot(aes(network, val)) +
  geom_bar(stat = 'identity', position = 'dodge')+
  theme(legend.position = 'top',
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))+
  labs(y = '',x = '')+
  # scale_y_log10()+
  facet_wrap(~properties, scales = 'free_y', ncol = 2)

```

### KDA results
```{r}
kd.res = kda.tbl %>% 
  # filter(dir == 'undirected') %>% 
  group_by(bd,filt,dir) %>%
  summarise( kd = list(read_kda_res(id[ef == 0],id[ef == 1])) ) %>% 
  unnest(kd) %>%  
  left_join(., 
            biodom %>% select(MODULE = GOterm_Name, Biodomain, color, abbr, label), 
            by = 'MODULE') %>% 
  ungroup() %>% 
  group_by(bd, filt, dir) %>% 
  arrange(MODULE, desc(ef1_fdr)) %>% 
  mutate(top_kd = if_else( duplicated(MODULE) , 0, 1)) %>% 
  relocate(top_kd, .after = 'MEMBER') %>% 
  ungroup()
  
lm.kd.res <- kd.res
```

```{r fig.width=16,fig.height=8}
# p2 = 
kd.res %>% 
  # filter( ef1_fdr > -log10(0.05)
  #        # , MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
  #        , delta_fdr > 0
  #        ) %>%
  mutate(dir = fct_relevel(dir, c('undirected','directed')),
         filt = fct_relevel(filt, c('none','node','edge','node_edge'))) %>% 
  ggplot(aes( ef1_fdr, delta_fdr ))+
  labs(x = 'wKDA FDR ef1, -log10', y = '\u0394 FDR, ef1 - ef0', title = unique(kd.res$bd))+
  # geom_abline(intercept = 0, slope =1, lty= 2, lwd = .5)+
  geom_smooth(method = 'glm', lty = 2, lwd = .5, color = 'grey20')+
  geom_vline(xintercept = 0, lwd = .5)+ geom_hline(yintercept = 0, lwd = .5) +
  geom_point(alpha = .2, size = 1, aes(color = color) )+
  geom_point(data = subset(kd.res, ef1_fdr > -log10(0.05) & top_kd == 1 & delta_fdr > 0)
             , alpha = .6, size = 2, aes(color = color))+
  ggrepel::geom_label_repel(
    data = subset( kd.res, ef1_fdr > -log10(0.05)
                   & top_kd == 1
                   & MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
                   & delta_fdr > 0
                   ), 
    aes(label = paste0(NODE, '\n', MODULE, '\n', Biodomain)),
    size = 2, alpha = .7, min.segment.length = 0)+
  facet_wrap(dir~filt, scales = 'free', ncol = 4)+ #, scales = 'free'
  scale_color_identity(guide = 'none') #; plotly::ggplotly(p)

# plotly::ggplotly(p2)
```

### KD ~ Biodomains

```{r, fig.width=10}
kd.res %>% 
  filter(ef1_fdr > -log10(0.05)
         # , MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
         , delta_fdr > 0
         , top_kd == 1
         ) %>%
  mutate(pair = paste0(NODE,':',MODULE)) %>% 
  group_by(filt, dir, Biodomain) %>% 
  summarise(n_term = length(unique(MODULE)),
            n_node = length(unique(NODE)),
            n_kd = length(unique(pair)),
            # terms = list(unique(MODULE)),
            min_fdr = signif( 10^-max(ef1_fdr), digits = 3),
            max_delta = signif( max(delta_fdr), digits = 3) ) %>% 
  full_join(., 
            biodom %>% group_by(Biodomain) %>% mutate(n_go = length(unique(GO_ID))) %>% 
              select(Biodomain, n_go, abbr:color) %>% distinct(), 
            by = 'Biodomain') %>% 
  ungroup() %>%
  mutate(fxn_bd_term = n_term / n_go) %>% 
  filter(!is.na(filt), !is.na(dir)) %>% 
  mutate(#dir = fct_relevel(dir, c('undirected','directed')),
         filt = fct_relevel(filt, c('none','node','edge','node_edge')),
         Biodomain = fct_reorder(Biodomain, n_term)) %>% 
  arrange(Biodomain, desc(n_term), desc(max_delta)) %>% 
  ggplot(aes(n_term, Biodomain))+
  geom_segment(aes(yend=Biodomain, xend=0), color = 'grey50')+
  geom_point(aes(size = max_delta, color = color))+
  scale_color_identity()+
  labs(y='', 
       title = paste0(unique(kd.res$bd), ' Network Key Drivers'),
       subtitle = 'Biodomain GO terms')+ 
  theme(legend.position = 'bottom')+
  facet_wrap(dir~filt, ncol = 4)
```

```{r, fig.width=10}
kd.res %>% 
  filter(ef1_fdr > -log10(0.05)
         # , MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
         , delta_fdr > 0
         , top_kd == 1
         ) %>%
  mutate(pair = paste0(NODE,':',MODULE)) %>% 
  group_by(filt, dir, Biodomain) %>% 
  summarise(n_term = length(unique(MODULE)),
            n_node = length(unique(NODE)),
            n_kd = length(unique(pair)),
            # terms = list(unique(MODULE)),
            min_fdr = signif( 10^-max(ef1_fdr), digits = 3),
            max_delta = signif( max(delta_fdr), digits = 3),
            mean_delta = signif( mean(delta_fdr), digits = 3)) %>% 
  full_join(., 
            biodom %>% group_by(Biodomain) %>% mutate(n_go = length(unique(GO_ID))) %>% 
              select(Biodomain, n_go, abbr:color) %>% distinct(), 
            by = 'Biodomain') %>% 
  ungroup() %>%
  mutate(fxn_bd_term = n_term / n_go) %>% 
  filter(!is.na(filt), !is.na(dir)) %>% 
  mutate(#dir = fct_relevel(dir, c('undirected','directed')),
         filt = fct_relevel(filt, c('none','node','edge','node_edge')),
         Biodomain = fct_reorder(Biodomain, mean_delta)) %>% 
  arrange(Biodomain, desc(mean_delta), desc(max_delta)) %>% 
  ggplot(aes(mean_delta, Biodomain))+
  geom_segment(aes(yend=Biodomain, xend=0), color = 'grey50')+
  geom_point(aes(size = n_term, color = color))+
  scale_color_identity()+
  labs(y='', 
       title = paste0(unique(kd.res$bd), ' Network Key Drivers'),
       subtitle = 'Biodomain GO terms')+ 
  theme(legend.position = 'bottom')+
  facet_wrap(dir~filt, ncol = 4)
```

```{r, fig.width=10}
kd.res %>% 
  filter(ef1_fdr > -log10(0.05)
         # , MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
         , delta_fdr > 0
         , top_kd == 1
         ) %>%
  mutate(pair = paste0(NODE,':',MODULE)) %>% 
  group_by(filt, dir, Biodomain) %>% 
  summarise(n_term = length(unique(MODULE)),
            n_node = length(unique(NODE)),
            n_kd = length(unique(pair)),
            # terms = list(unique(MODULE)),
            min_fdr = signif( 10^-max(ef1_fdr), digits = 3),
            max_delta = signif( max(delta_fdr), digits = 3) ) %>% 
  full_join(., 
            biodom %>% select(Biodomain, abbr:color) %>% distinct(), 
            by = 'Biodomain') %>% 
  arrange(desc(n_node), desc(max_delta), .by_group = T) %>% 
  ungroup() %>% 
  filter(!is.na(filt), !is.na(dir)) %>% 
  mutate(#dir = fct_relevel(dir, c('undirected','directed')),
         filt = fct_relevel(filt, c('none','node','edge','node_edge')),
         Biodomain = fct_reorder(Biodomain, n_node)) %>%
  ggplot(aes(n_node, Biodomain))+
  geom_segment(aes(yend=Biodomain, xend=0), color = 'grey50')+
  geom_point(aes(size = max_delta, color = color))+
  scale_color_identity()+
  labs(y='', 
       title = paste0(unique(kd.res$bd), ' Network Key Drivers'),
       subtitle = 'Nodes')+ 
  theme(legend.position = 'bottom')+
  facet_wrap(dir~filt, ncol = 4)
```

```{r fig.width=10,fig.height=10}
tmp <- kd.res %>% 
  filter( 
    ef1_fdr > -log10(0.05)
    # , MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
    , delta_fdr > 0 ,
    dir == 'undirected'
    , filt == 'node'
         )

ggplot(tmp, aes( ef1_fdr, delta_fdr ))+
  labs(x = 'wKDA FDR ef1, -log10', y = '\u0394 FDR, ef1 - ef0', 
       title = paste0(unique(tmp$bd), ': ', unique(tmp$dir),', ',unique(tmp$filt)),
       subtitle = 'signif KDs (EF1 FDR < 0.05), \u0394 FDR > 0, for GSEA-enriched terms'
       )+
  # geom_abline(intercept = 0, slope =1, lty= 2, lwd = .5)+
  geom_vline(xintercept = 0, lwd = .5)+ geom_hline(yintercept = 0, lwd = .5) +
  geom_point(alpha = .2, size = 1, aes(color = color) )+
  geom_point(data = subset(kd.res, ef1_fdr > -log10(0.05) & top_kd == 1 & delta_fdr > 0)
             , alpha = .6, size = 2, aes(color = color))+
  geom_smooth(method = 'glm', lty = 2, lwd = .5, color = 'grey20')+
  # ggrepel::geom_label_repel(
  #   data = subset( kd.res, ef1_fdr > -log10(0.05)
  #                  & top_kd == 1
  #                  & MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
  #                  & delta_fdr > 0
  #                  ),
  #   aes(label = paste0(NODE, '\n', MODULE, '\n', Biodomain)),
  #   size = 2, alpha = .7, min.segment.length = 0)+
  facet_wrap(~Biodomain)+ #, scales = 'free'
  scale_color_identity(guide = 'none') #; plotly::ggplotly(p)

# plotly::ggplotly(p2)
```

```{r}
kd.res %>% 
  filter(ef1_fdr > -log10(0.05)
         # , MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
         , delta_fdr > 0
         , top_kd == 1
         ) %>% 
  group_by(filt, dir, Biodomain) %>% 
  summarise(n_term = length(unique(MODULE)),
            # terms = list(unique(MODULE)),
            min_fdr = signif( 10^-max(ef1_fdr), digits = 3),
            max_delta = signif( max(delta_fdr), digits = 3) ) %>% 
  arrange(desc(n_term), desc(max_delta), .by_group = T) %>%
  DT::datatable(rownames = F, filter = 'top')
```
### Top KDs
```{r}
kd.summary = kd.res %>% 
  filter(ef1_fdr > -log10(0.05)
         , MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
         , delta_fdr > 0
         ) %>% 
  group_by(NODE, filt, dir) %>% 
  summarise(n_bd = length(unique(Biodomain)),
            bds = list(unique(Biodomain)),
            n_term = length(unique(MODULE)),
            terms = list(unique(MODULE)),
            min_fdr = signif( 10^-max(ef1_fdr), digits = 3),
            max_delta = signif( max(delta_fdr), digits = 3) ) %>% 
  arrange(desc(n_bd), desc(max_delta)) %>% 
  mutate(LE_gene = if_else(NODE %in% input.gene.list, 'Y', 'N')) %>% 
  relocate(LE_gene, .after = 'NODE')

DT::datatable(kd.summary %>% select(-bds, -terms), rownames = F, filter = 'top')
```

```{r}
kd.res %>% 
  filter(ef1_fdr > -log10(0.05)
         , top_kd == 1
         , MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]
         , delta_fdr > 0
         ) %>% 
  select(bd, dir, filt, NODE, MODULE, MEMBER, contains('fdr')) %>% 
  arrange(desc(delta_fdr), desc(ef1_fdr)) %>% 
  mutate(LE_gene = if_else(NODE %in% input.gene.list, 'Y', 'N')) %>% 
  relocate(LE_gene, .after = 'NODE') %>% 
  DT::datatable(., rownames = F, filter = 'top') %>% 
  DT::formatSignif(columns = c('ef0_fdr','ef1_fdr','delta_fdr'))
```


### KD subnetworks
pull NW to view subgraphs
```{r}
nw = nw.tbl %>% 
  filter(
    dir == 'undirected', 
    filt == 'node', 
    bd.filt == T
    ) %>% 
  pull(id) %>% 
  synGet(.) %>% 
  .$path %>% 
  read_graph(., format = 'graphml' )
```

```{r fig.width=12,fig.height=8}
p = suppressWarnings( plot_kd_subnet(nw, kd = 'RAB5C',term = 'clathrin-coated vesicle membrane') )
p
```

```{r fig.width=12,fig.height=8}
p = suppressWarnings( plot_kd_subnet(nw, kd = 'ACOX1', term = 'fatty acid oxidation') )
p
```

```{r fig.width=12,fig.height=8}
p = suppressWarnings( plot_kd_subnet(nw, kd = 'ITGB2', term = 'cell-substrate adhesion') )
p
```

```{r fig.width=12,fig.height=8}
p = suppressWarnings( plot_kd_subnet(nw, kd = 'SYT1', term = 'synaptic vesicle recycling') )
p
```

```{r fig.width=12,fig.height=8}
p = suppressWarnings( plot_kd_subnet(nw, kd = 'TLN1', term = 'cell-matrix adhesion') )
p
```

### KDs ~ CBrain phenotypes
```{r fig.width=10, fig.height=5}
# crispr brain phenotype hits (any) vs non-hits
cb.hits = simple %>% filter(`Hit Class` != 'Non-Hit') %>% 
  pull(Gene) %>% unique()
cb.nonhits = simple %>% filter( (Gene %in% cb.hits)==F ) %>% 
  pull(Gene) %>% unique()

# ID key drivers from different parameter sets
comb = kd.res %>% select(filt, dir) %>% distinct() %>% arrange(dir,filt)
comb$kd.hits = map(
  1:nrow(comb),
  ~ kd.res %>% filter(ef1_fdr > -log10(0.05), 
                      filt == comb$filt[.x],
                      dir == comb$dir[.x]) %>% pull(NODE) %>% unique()
)
comb$kd.nonhits = map(
  1:nrow(comb),
  ~ kd.res %>% filter( (NODE %in% comb$kd.hits[[.x]])==F ) %>% 
    pull(NODE) %>% unique()
)

# calculate fisher stats 
comb = map_dfr(
  1:nrow(comb),
  ~ bind_cols(
      pheno_kd = intersect(cb.hits, comb$kd.hits[[.x]]) %>% length(),
      noPheno_kd = intersect(cb.nonhits, comb$kd.hits[[.x]]) %>% length(),
      pheno_nokd = intersect(cb.hits, comb$kd.nonhits[[.x]]) %>% length(),
      noPheno_nokd = intersect(cb.nonhits, comb$kd.nonhits[[.x]]) %>% length()
    ) %>% 
    rowwise() %>% mutate(
      fisher.p = matrix(c(pheno_kd, noPheno_kd, pheno_nokd, noPheno_nokd), 
                        nrow = 2) %>% 
      fisher.test( ., alt = 'g') %>% broom::tidy() %>% pull(p.value)
    )
) %>% 
  bind_cols(comb, .)

# make plots for each comb
plist = map(
  1:nrow(comb),
  ~ plot( eulerr::euler(
    c(pheno = length(cb.hits),
      kd = length(comb$kd.hits[[.x]]), 
      'pheno&kd' = comb$pheno_kd[.x])
    , quantities = T )
    ) %>% 
    ggplotify::as.ggplot() + 
    ggtitle(label = kd.res$bd %>% unique,
            subtitle = paste0(
            'dir: ', comb$dir[.x],', filt: ', comb$filt[.x],
            '\nFisher p = ', comb$fisher.p[.x] %>% signif(digits = 2) )
            ) 
)

cowplot::plot_grid(plotlist = plist, ncol = 4)


```

linear regression  ~ KDA FDR
```{r}
tmp <- kd.res %>% inner_join( simple,., by =c('Gene'='NODE')) %>% 
  group_by(cell,mode,expt, bd, filt, dir) %>% 
  mutate(lm = lm(abs(gene_score)~ef1_fdr) %>% broom::tidy() %>% 
           filter(term != '(Intercept)') %>% 
           mutate(r.squared = lm(abs(gene_score)~ef1_fdr) %>% 
                    broom::glance() %>% pull(r.squared)) %>% list()) %>% 
  unnest(lm)  %>% 
  select(cell, mode, expt, bd.nw = bd, nw.filt = filt, nw.dir=dir, term:r.squared) %>% distinct() %>% 
  filter(p.value < 0.05) %>% 
  arrange(desc(statistic),p.value)

tmp %>% 
  DT::datatable(rownames = F, filter = 'top', caption = 'abs(gene_score) ~ ef1_fdr', options = list(pageLength = 6)) %>% #
  DT::formatSignif(columns = c('statistic', 'std.error','r.squared', 'p.value', 'estimate'))
```

```{r fig.width=10, fig.height=5}
c = 'iAstrocyte'
m = 'CRISPRi'
e = 'LAMP1-ITC'

kd.res %>% inner_join( simple,., by =c('Gene'='NODE')) %>%
  filter(
    cell == c,
    mode == m,
    expt == e,
    ef1_fdr > -log10(0.2)
    ) %>% 
  ggplot( aes( ef1_fdr, abs(gene_score) )) +
  geom_point(#data = subset(tmp, d > 0),
             aes(color = color,  size = delta_fdr), alpha = .5) +
  geom_hline(yintercept = 0, lwd = 0.5)+
  geom_vline(xintercept = 0, lwd = 0.5)+
  scale_size_continuous(name = 'KDA \u0394 FDR\nef1-ef0', range = c(.5,3))+ 
  # ggrepel::geom_label_repel(
  #   data = subset(tmp, d > 0), aes(label = paste0(Gene,'\n', go)),
  #   min.segment.length = 0, size = 2.5, max.overlaps = 12)+
  scale_color_identity(guide = 'none')+
  geom_smooth(method = 'lm', color = 'grey20',lty=2)+
  labs(y = 'CRISPRbrain phenotype score, absolute value',
       x = 'KDA FDR, -log10',
       title = paste0(c,', ',m,', ',e)) + 
  facet_grid(dir~filt, scales = 'free_x')
```

linear regression ~  KDA delta FDR e1/e0
```{r}
tmp <- kd.res %>% inner_join( simple,., by =c('Gene'='NODE')) %>% 
  group_by(cell,mode,expt, bd, filt, dir) %>% 
  mutate(lm = lm(abs(gene_score)~delta_fdr) %>% broom::tidy() %>% 
           filter(term != '(Intercept)') %>% 
           mutate(r.squared = lm(abs(gene_score)~delta_fdr) %>% 
                    broom::glance() %>% pull(r.squared)) %>% list()) %>% 
  unnest(lm) %>% 
  select(cell, mode, expt, bd, filt, dir, term:r.squared) %>% distinct() %>% 
  filter(p.value < 0.05) %>% 
  arrange(desc(statistic),p.value) 

tmp %>% 
  DT::datatable(rownames = F, filter = 'top', caption = 'abs(gene_score) ~ \u0394 fdr (ef1-ef0)', options = list(pageLength = 6)) %>% #
  DT::formatSignif(columns = c('statistic', 'std.error','r.squared', 'p.value', 'estimate'))
```

## Synapse
<WIP>

## Mitochondrial Metabolism



<WIP>

# Session
```{r}
sessionInfo()
```

