---
title: "Network Filtering Analysis"
author: "Greg Cary"
date: "`r Sys.Date()`"
output: 
  html_document: 
    fig_width: 5
    fig_height: 4
  html_notebook:
    code_folding: hide
    theme: spacelab
    css: style.css
    toc: true
    toc_float: true
---


```{r setup}
library(synapser)
# library(paxtoolsr)
# library(org.Hs.eg.db)
# library(clusterProfiler)
# library(HotNetvieweR)
library(igraph)
library(tidygraph)
library(tidyverse)

# source(paste0(here::here(),'/../biodom_tally.R'))
# source(paste0(here::here(),'/../biodom_enr.R'))
# source(paste0(here::here(),'/../biodom_enr_plots.R'))

theme_set(theme_bw())
```

# Gather data
Grab relevant data from synapse, including:  
1) Target Risk Scores ([syn25575156](https://www.synapse.org/#!Synapse:syn25575156){target="_blank"}) and Omics Scores ([syn22758536](https://www.synapse.org/#!Synapse:syn22758536){target="_blank"})  
2) Biodomain Definitions ([syn25428992](https://www.synapse.org/#!Synapse:syn25428992){target="_blank"})  
3) Pathway Commons Full Graph, v12 ([syn51080932](https://www.synapse.org/#!Synapse:syn51080932){target="_blank"})  
4) Human Protein Atlas tissue immunohistochemistry micro array data ([syn51074598](https://www.synapse.org/#!Synapse:syn51074598){target="_blank"})  
5) RNA Brain GTEx ([syn51074639](https://www.synapse.org/#!Synapse:syn51074639){target="_blank"})  
6) AMP-AD cohort pairwise partial correlations ([ROSMAP](https://www.synapse.org/#!Synapse:syn51061790){target="_blank"}, [Mayo](https://www.synapse.org/#!Synapse:syn51061614){target="_blank"}, [MSBB](https://www.synapse.org/#!Synapse:syn51061324){target="_blank"}); these are quite large! (> 6 GB), wait to load until performing this analysis  
7) SEA-AD single cell data ([syn51441105](https://www.synapse.org/#!Synapse:syn51441105){target="_blank"})  
```{r message=FALSE, warning=FALSE}
synLogin()

# target risk scores
scores <- read_csv(synTableQuery('select * from syn25575156', 
                                 includeRowIdAndRowVersion = F)$filepath)
omics <- read_csv(synTableQuery('select * from syn22758536', 
                                includeRowIdAndRowVersion = F)$filepath)

# biological domain annotations
biodom <- full_join(
  # biodomains
  readRDS(synGet('syn25428992')$path),
  # domain labels
  read_csv(synGet('syn26856828')$path),
  by = c('Biodomain'='domain')
) %>%
  mutate(Biodomain = case_when(Biodomain == 'none' ~ NA_character_, T ~ Biodomain))

# pathway commons graph
net <- igraph::read_graph(synGet('syn51080932')$path, format = 'graphml') 

# Human protein atlas info
tissue.array <- read_csv(synGet('syn51074598')$path)
brain.gtex <- read_csv(synGet('syn51074639')$path)

# single cell
seaad <- read_csv(synGet('syn51197803')$path, guess_max = 2e5)
seaad.broad <- read_csv(synGet('syn51441105')$path, guess_max = 2e5)
```


Extract the core NW tables
```{r message=FALSE}
net.tbl <- igraph::as_data_frame(net)

v.attr <- tibble( na = vertex.attributes(net) ) %>%
  t() %>% as_tibble(rownames = NA, .name_repair = 'unique') %>% unnest(everything()) %>%
  rename_with(., ~names(vertex.attributes(net)), everything())

e.attr <- tibble( ea = edge.attributes(net) ) %>% 
  t() %>% as_tibble(rownames = NA, .name_repair = 'unique') %>% unnest(everything()) %>% 
  rename_with(., ~names(edge.attributes(net)), everything())
```

# NODE: Human Protein Atlas 

Specify brain tissue types
```{r}
brain.tissues <- c(
 "caudate", "cerebellum", "cerebral cortex", "hippocampus", 
 "hypothalamus", "pituitary gland", "dorsal raphe", 
 "choroid plexus", "substantia nigra"
)

brain.genes <- tissue.array %>% filter(
  Tissue %in% brain.tissues, 
  Level %in% c('Low','Medium','High','Ascending','Descending'),
  Reliability %in% c('Enhanced','Supported','Approved')
) %>% pull(Gene.name) %>% unique()

not.brain <- tissue.array %>% filter(
  Tissue %in% brain.tissues,
  Level %in% c('Not detected'),
  Reliability %in% c('Enhanced','Supported','Approved')
) %>% pull(Gene.name) %>% unique()

```


```{r}
# also "brain genes":
# scores %>% filter(isScored_omics == 'Y', OmicsScore > 0) %>% pull(GeneName) %>% unique()

brain.gtex %>% 
  mutate(hpa = case_when(Gene.name %in% brain.genes ~ 
                           paste0('brain (n = ', length(intersect(Gene.name, brain.genes)),' genes)'),
                         Gene.name %in% not.brain ~ 
                           paste0('not brain (n = ', length(intersect(Gene.name,not.brain)),' genes)'),
                         T ~ NA_character_)) %>% 
  filter(!is.na(hpa)) %>% 
  ggplot(aes( log10(nTPM), fill = hpa))+
  geom_density(aes(color = hpa), alpha = .1)+
  # geom_histogram(position = 'dodge')+
  # scale_y_log10()+
  scale_fill_discrete('')+scale_color_discrete('')+
  theme(legend.position = 'top')
```

```{r}
# also "brain genes":
tad.deg <- scores %>% filter(isScored_omics == 'Y', OmicsScore > 0) %>% pull(GeneName) %>% unique()

brain.gtex %>% 
  mutate(hpa = case_when(Gene.name %in% tad.deg ~ paste0('TAD DEG (n = ', length(intersect(Gene.name,tad.deg)),' genes)'),
                         T ~ paste0('not TAD DEG (n = ', length(setdiff(Gene.name, tad.deg)),' genes)'),
                         )) %>% 
  filter(!is.na(hpa)) %>% 
  ggplot(aes( log10(nTPM), fill = hpa))+
  geom_density(aes(color = hpa), alpha = .1)+
  # geom_histogram(position = 'dodge')+
  # scale_y_log10()+
  scale_fill_discrete('')+scale_color_discrete('')+
  theme(legend.position = 'top')
```

```{r}
# also "brain genes":
tad.deg <- scores %>% filter(isScored_omics == 'Y', OmicsScore > 0) %>% pull(GeneName) %>% unique()

brain.gtex %>% 
  mutate(
  hpa = case_when(
    Gene.name %in% brain.genes ~ 
      paste0('HPA brain (n = ', length(intersect(Gene.name, brain.genes)),' genes)'),
    Gene.name %in% tad.deg ~ paste0('TAD DEG (n = ', length(intersect(Gene.name,tad.deg)),' genes)'),
    Gene.name %in% not.brain ~ paste0('HPA not brain (n = ', length(intersect(Gene.name,not.brain)),' genes)'),
    T ~ paste0('other (n = ', length(setdiff(Gene.name, union(union(brain.genes, tad.deg), not.brain))) ,' genes)')
    )) %>% 
  ggplot(aes( log10(nTPM), fill = hpa))+
  geom_density(aes(color = hpa), alpha = .1)+
  # geom_histogram(position = 'dodge')+
  # scale_y_log10()+
  scale_fill_discrete('')+scale_color_discrete('')+
  guides(fill = guide_legend(nrow=2))+
  theme(legend.position = 'top')
```

# NODE: SEA-AD single cell data

## subclass
### both dimensions

```{r}
t = .9

tmp = seaad.broad %>% 

  # filter(gene %in% not.brain) %>% 
  # mutate(hpa = 'not') %>% 

  mutate(
      hpa = case_when(
          gene %in% brain.genes ~ 'brain',
          gene %in% not.brain ~ 'not',
          gene %in% tad.deg ~ 'deg',
          T ~ 'other'
      )
  ) %>%

  group_by(cellType, hpa) %>% 
  summarise( 
    exp = quantile(upperQ_exp, t), 
    fxn = quantile(fxn_exp, t)
    ) 

# bind_rows(
#     tmp, 
#     tmp %>% filter(hpa == 'not') %>% mutate(exp = exp + .142, fxn = fxn + .142, hpa = 'new')
#   ) %>% 
tmp %>% 
  ggplot(aes(fxn, exp, group = hpa))+
  geom_smooth(method = 'lm', color = 'grey20', lwd = .5, lty = 2)+
  # geom_abline(intercept = 1.5294, slope = -2.562569)+
  geom_abline(intercept = 2.3, slope = -2.5)+
  annotate(geom = 'text', x = .65, y = 0, label = 'y = -2.5x + 2.3', hjust = 0)+
  geom_point(aes(color = cellType, shape = hpa), size = 2, alpha = .5)+
  labs(y = 'quantile expression', x = 'quantile fraction expressing',
       subtitle = paste0('plotting quantile: ', t))

```


```{r}
t = .9

seaad.broad %>% 
  
  # filter(gene %in% not.brain) %>% 
  # mutate(hpa = 'not') %>% 

  mutate(
      hpa = case_when(
          gene %in% brain.genes ~ 'brain',
          gene %in% not.brain ~ 'not',
          gene %in% tad.deg ~ 'deg',
          T ~ 'other'
      )
  ) %>%
  filter(hpa == 'not') %>%

  group_by(cellType, hpa) %>%
  summarise( exp = quantile(upperQ_exp, t), 
             fxn = quantile(fxn_exp, t)
             ) %>% 
  lm(exp~fxn, data = .) %>% 
  broom::tidy()
```

```{r}
x = map_dfr(
    seq(1.5,3.5,.01),
    ~{
        seaad.broad %>% 
            filter( upperQ_exp >= -2.5 * fxn_exp + .x) %>% 
            summarise(
                int = .x,
                n.brain = length(intersect(gene, brain.genes )),
                n.not = length(intersect(gene,not.brain)),
                n.deg = length(intersect(gene,tad.deg)),
                n.other = length(unique(setdiff(gene, union(union(brain.genes, tad.deg), not.brain)))),
                diff.b = (n.brain - n.not),
                pct.b = 100*(diff.b/n.brain),
                diff.d = n.deg - n.not,
                pct.d = 100*(diff.d/n.brain)
            )
    }
) %>% 
  arrange(desc(diff.b), desc(pct.d));

qplot(x$int, x$diff.b, geom = 'line')

DT::datatable(x)
```

```{r}
t = .9

thresh = seaad.broad %>% 
  filter(gene %in% not.brain) %>%
  group_by(broad, cellType) %>%
  summarise( 
    exp1 = quantile(upperQ_exp, t),
    fxn1 = quantile(fxn_exp, t)
  ) %>% 
  mutate(
    exp = exp1+.142,
    fxn = fxn1+.142,
    hpa = 'new.dat'
  ) 

seaad.broad %>% 

  mutate(
    hpa = case_when(
        gene %in% brain.genes ~ 'brain',
        gene %in% not.brain ~ 'not',
        gene %in% tad.deg ~ 'deg',
        T ~ 'other')
      ) %>% 
  ggplot(aes(fxn_exp, upperQ_exp, group = hpa))+
  geom_abline(intercept = 2.3, slope = -2.5)+
  # annotate(geom = 'text', x = .65, y = 0, label = 'y = -2.5x + 2.5', hjust = 0)+
  geom_point(data = thresh, aes(x = fxn, y = exp), size = 2, alpha = .5)+
  geom_smooth(method = 'lm', aes(color = hpa), lwd = .5, lty = 2)+
  labs(y = 'expression', x = 'fraction expressing'
       #, subtitle = paste0('plotting quantile: ', t)
       )+
  facet_wrap(~broad, scales = 'free')

```
```{r}
t = .9

thresh = seaad.broad %>% 
  filter(gene %in% not.brain) %>%
  group_by(broad, cellType) %>%
  summarise( 
    exp1 = quantile(upperQ_exp, t),
    fxn1 = quantile(fxn_exp, t)
  ) %>% 
  mutate(
    exp = exp1+.142,
    fxn = fxn1+.142,
    hpa = 'new.dat'
  ) 

seaad.broad %>% 
  mutate(
    hpa = case_when(
        gene %in% brain.genes ~ 'brain',
        gene %in% not.brain ~ 'not',
        gene %in% tad.deg ~ 'deg',
        T ~ 'other')
      ) %>% 

  # group_by(cellType) %>%
  # filter(
  #   fxn_exp >= thresh$fxn[ which(thresh$cellType == cellType) ] %>% unique(),
  #   upperQ_exp >= thresh$exp[ which(thresh$cellType == cellType) ] %>% unique(),
  #   .preserve = T
  # ) %>%
  # ungroup() %>%
  
  filter( upperQ_exp >= -2.5 * fxn_exp + 2.3) %>%

  ggplot(aes(fxn_exp, upperQ_exp, group = hpa))+
  geom_abline(intercept = 2.3, slope = -2.5)+
  # annotate(geom = 'text', x = .65, y = 0, label = 'y = -2.5x + 2.5', hjust = 0)+
  geom_point(data = thresh, aes(x = fxn, y = exp), size = 2, alpha = .5)+
  geom_smooth(method = 'lm', aes(color = hpa), lwd = .5, lty = 2)+
  labs(y = 'expression', x = 'fraction expressing'
       #, subtitle = paste0('plotting quantile: ', t)
       )+
  facet_wrap(~broad, scales = 'free')

```

```{r fig.width=8, fig.height=6}
seaad.broad %>% 
  ggplot(aes(upperQ_exp, fxn_exp))+ 
  geom_bin2d(aes(fill = ..count.. ))+
  viridis::scale_fill_viridis(trans = 'log10', option = 'A')+
  ggtitle('no filter')+
  facet_wrap(~broad)
```

```{r fig.width=8, fig.height=6}
thresh = seaad.broad %>% 
  filter(gene %in% not.brain) %>%
  group_by(broad, cellType) %>%
  summarise( 
    exp1 = quantile(upperQ_exp, t),
    fxn1 = quantile(fxn_exp, t)
  ) %>% 
  mutate(
    exp = exp1+.142,
    fxn = fxn1+.142,
    hpa = 'new.dat'
  ) 

seaad.broad %>% 
  mutate(
    hpa = case_when(
        gene %in% brain.genes ~ 'brain',
        gene %in% tad.deg ~ 'deg',
        gene %in% not.brain ~ 'not',
        T ~ 'other')
      ) %>% 
  filter(!is.na(hpa)) %>%     

  # group_by(cellType) %>%
  # filter(
  #   fxn_exp >= thresh$fxn[ which(thresh$cellType == cellType) ] %>% unique(),
  #   upperQ_exp >= thresh$exp[ which(thresh$cellType == cellType) ] %>% unique(),
  #   .preserve = T
  # ) %>%
  # ungroup() %>%

  filter( upperQ_exp >= -2.5 * fxn_exp + 2.3) %>%

  # group_by(cellType, hpa) %>% 
  # mutate( exp = quantile(upperQ_exp, .9), 
  #         fxn = quantile(fxn_exp, .9)
  #         ) %>% 
  # group_by(cellType) %>%
  # filter(  ) %>%
  # ungroup() %>% 
  
  mutate(
    n = case_when(
      gene %in% brain.genes ~ length(intersect(gene, brain.genes)),
      gene %in% tad.deg ~ length(intersect(gene,tad.deg)),
      gene %in% not.brain ~ length(intersect(gene,not.brain)),
      T ~ length(unique(setdiff(gene, union(union(brain.genes, tad.deg), not.brain))))
      )) %>%
  ggplot(aes(upperQ_exp, fxn_exp))+ 
  geom_bin2d(aes(fill = ..count.. ))+
  viridis::scale_fill_viridis(trans = 'log10', option = 'A')+
  facet_wrap(~broad)
```

```{r, fig.width=8, fig.height=8}

seaad.broad %>% 
  mutate(
    hpa = case_when(
      gene %in% brain.genes ~ 'brain.genes',
      gene %in% tad.deg ~ 'tad.deg',
      gene %in% not.brain ~ 'not.brain',
      T ~ 'other')
  ) %>% 
  filter(!is.na(hpa)) %>% 
  group_by(hpa) %>% 
  mutate(
    n = length(unique(gene)),
    hpa1 = paste0(hpa, ', ', n)
    ) %>% 
  ggplot(aes(upperQ_exp, fxn_exp))+ 
  geom_bin2d(aes(fill = ..count.. ))+
  viridis::scale_fill_viridis(trans = 'log10', option = 'A')+
  ggtitle('no filter')+
  facet_grid(broad~hpa1)
 
```

```{r, fig.width=8, fig.height=8}

thresh = seaad.broad %>% 
  filter(gene %in% not.brain) %>%
  group_by(broad, cellType) %>%
  summarise( 
    exp1 = quantile(upperQ_exp, t),
    fxn1 = quantile(fxn_exp, t)
  ) %>% 
  mutate(
    exp = exp1+.142,
    fxn = fxn1+.142,
    hpa = 'new.dat'
  ) 

seaad.broad %>% 
  mutate(
    hpa = case_when(
        gene %in% brain.genes ~ 'brain',
        gene %in% tad.deg ~ 'tad.deg',
        gene %in% not.brain ~ 'not.brain',
        T ~ 'other')
      ) %>% 
  filter(!is.na(hpa)) %>%     

  # group_by(cellType) %>%
  # filter(
  #   fxn_exp >= thresh$fxn[ which(thresh$cellType == cellType) ] %>% unique(),
  #   upperQ_exp >= thresh$exp[ which(thresh$cellType == cellType) ] %>% unique(),
  #   .preserve = T
  # ) %>%
  # ungroup() %>%
  
  filter( upperQ_exp >= -2.5 * fxn_exp + 2.3) %>%
  
  # filter( upperQ_exp >= 2 | (upperQ_exp >= 1.33 & fxn_exp >= 0.2) ) %>%

  # group_by(cellType, hpa) %>%
  # mutate(top_exp = quantile(upperQ_exp, 0.75),
  #        top_fxn = quantile(fxn_exp, 0.95)) %>%
  # group_by(cellType) %>%
  # filter( upperQ_exp > unique(top_exp[hpa == 'not.brain']) ,
  #         fxn_exp > unique(top_fxn[hpa == 'not.brain']) ) %>%
  # ungroup() %>%
  
  group_by(hpa) %>% 
  mutate(
    n = length(unique(gene)),
    hpa1 = paste0(hpa, ', ', n)
    ) %>% 
  ggplot(aes(upperQ_exp, fxn_exp))+ 
  geom_bin2d(aes(fill = ..count.. ))+
  viridis::scale_fill_viridis(trans = 'log10', option = 'A')+
  ggtitle('filtered')+
  facet_grid(broad~hpa1)
 
```


### fxn expressed
```{r}
# also "brain genes":
# scores %>% filter(isScored_omics == 'Y', OmicsScore > 0) %>% pull(GeneName) %>% unique()

seaad.broad %>% 
  # filter(is.na(group)) %>% 
  mutate(
    hpa = case_when(
      gene %in% brain.genes ~ paste0('HPA brain (n = ', length(intersect(gene, brain.genes)),' genes)'),
      gene %in% tad.deg ~ paste0('TAD DEG (n = ', length(intersect(gene,tad.deg)),' genes)'),
      gene %in% not.brain ~ paste0('HPA not brain (n = ', length(intersect(gene,not.brain)),' genes)'),
      T ~ paste0('other (n = ', length(unique(setdiff(gene, union(union(brain.genes, tad.deg), not.brain)))) ,' genes)')
      )
  ) %>% 
  filter(!is.na(hpa)) %>% 
  ggplot(aes( fxn_exp, fill = hpa))+
  geom_density(aes(color = hpa), alpha = .1)+
  # geom_histogram(position = 'dodge')+
  # scale_y_log10()+
  scale_fill_discrete('')+scale_color_discrete('')+
  guides(fill = guide_legend(nrow=2))+
  ggforce::facet_zoom(xlim = c(0,.25), ylim = c(0,5))+
  theme(legend.position = 'top')
```

```{r fig.width=6, fig.height=13}
# seaad.broad %>% group_by(cellType) %>% summarise(mn = median(fraction_expressed))

seaad.broad %>% 
  mutate(
    hpa = case_when(
      gene %in% brain.genes ~ paste0('HPA brain (n = ', length(intersect(gene, brain.genes)),' genes)'),
      gene %in% tad.deg ~ paste0('TAD DEG (n = ', length(intersect(gene,tad.deg)),' genes)'),
      gene %in% not.brain ~ paste0('HPA not brain (n = ', length(intersect(gene,not.brain)),' genes)'),
      T ~ paste0('other (n = ', length(unique(setdiff(gene, union(union(brain.genes, tad.deg), not.brain)))) ,' genes)')
      )
  ) %>% 
  group_by(cellType, hpa) %>% 
  mutate(top_exp = quantile(upperQ_exp, 0.75),
         top_fxn = quantile(fxn_exp, 0.75)) %>% 
  ggplot(., aes(fxn_exp, cellType, fill = hpa)) + 
  geom_violin(scale = 'width', draw_quantiles = c(.5)) +
  geom_point(aes(x = top_fxn, color = hpa))+
  # stat_summary(fun = function(x) quantile(x,0.5), geom="point", size=2, color="red", position = 'dodge')+
  # ggforce::facet_zoom(xlim = c(0,0.08), horizontal = F)
  coord_cartesian(xlim = c(0,0.25))

```

```{r}
# also "brain genes":
# scores %>% filter(isScored_omics == 'Y', OmicsScore > 0) %>% pull(GeneName) %>% unique()

seaad.broad %>% 
  # filter(is.na(group)) %>% 
  mutate(
    hpa = case_when(
      gene %in% brain.genes ~ paste0('HPA brain (n = ', length(intersect(gene, brain.genes)),' genes)'),
      gene %in% tad.deg ~ paste0('TAD DEG (n = ', length(intersect(gene,tad.deg)),' genes)'),
      gene %in% not.brain ~ paste0('HPA not brain (n = ', length(intersect(gene,not.brain)),' genes)'),
      T ~ paste0('other (n = ', length(unique(setdiff(gene, union(union(brain.genes, tad.deg), not.brain)))) ,' genes)')
      )
  ) %>% 
  filter(!is.na(hpa)) %>% 
  ggplot(aes( fxn_exp, fill = hpa))+
  # geom_density(aes(color = hpa), alpha = .1)+
  geom_histogram(position = 'dodge')+
  # scale_y_log10()+
  scale_fill_discrete('')+scale_color_discrete('')+
  guides(fill = guide_legend(nrow=2))+
  ggforce::facet_zoom(xlim = c(0,.25), ylim = c(0,1e5))+
  theme(legend.position = 'top')
```

```{r}
# also "brain genes":
# scores %>% filter(isScored_omics == 'Y', OmicsScore > 0) %>% pull(GeneName) %>% unique()

seaad.broad %>% 
  # filter( upperQ_exp >= 2 | (upperQ_exp >= 1.33 & fxn_exp >= 0.2) ) %>%
  mutate(
    hpa = case_when(
      gene %in% brain.genes ~ 'brain.genes',
      gene %in% tad.deg ~ 'tad.deg',
      gene %in% not.brain ~ 'not.brain',
      T ~ 'other')
  ) %>% 
  filter(!is.na(hpa)) %>% 

  # group_by(cellType, hpa) %>% 
  # mutate(top_exp = quantile(upperQ_exp, 0.75),
  #        top_fxn = quantile(fxn_exp, 0.95)) %>% 
  # group_by(cellType) %>%  
  # filter( upperQ_exp > unique(top_exp[hpa == 'not.brain']) ,
  #         fxn_exp > unique(top_fxn[hpa == 'not.brain']) ) %>% 
  # ungroup() %>% 
  
  filter( upperQ_exp >= -2.5 * fxn_exp + 2.3) %>%
  
  # filter( upperQ_exp >= 2 | (upperQ_exp >= 1.33 & fxn_exp >= 0.2) ) %>%

  group_by(hpa) %>% 
  mutate(
    n = length(unique(gene)),
    hpa1 = paste0(hpa, ', ', n)
    ) %>% 
  
  ggplot(aes( fxn_exp, fill = hpa1))+
  # geom_density(aes(color = hpa1), alpha = .1)+
  geom_histogram(position = 'dodge')+
  # scale_y_log10()+
  scale_fill_discrete('')+scale_color_discrete('')+
  guides(fill = guide_legend(nrow=2))+
  ggforce::facet_zoom(xlim = c(0,.25), ylim = c(0,1e5))+
  theme(legend.position = 'top')
```



```{r}
# also "brain genes":
# scores %>% filter(isScored_omics == 'Y', OmicsScore > 0) %>% pull(GeneName) %>% unique()

seaad.broad %>% 
  # filter( upperQ_exp >= 2 | (upperQ_exp >= 1.33 & fxn_exp >= 0.2) ) %>%
  mutate(
    hpa = case_when(
      gene %in% brain.genes ~ 'brain.genes',
      gene %in% tad.deg ~ 'tad.deg',
      gene %in% not.brain ~ 'not.brain',
      T ~ 'other')
  ) %>% 
  filter(!is.na(hpa)) %>% 

  # group_by(cellType, hpa) %>% 
  # mutate(top_exp = quantile(upperQ_exp, 0.75),
  #        top_fxn = quantile(fxn_exp, 0.95)) %>% 
  # group_by(cellType) %>%  
  # filter( upperQ_exp > unique(top_exp[hpa == 'not.brain']) ,
  #         fxn_exp > unique(top_fxn[hpa == 'not.brain']) ) %>% 
  # ungroup() %>% 
  
  filter( upperQ_exp >= -2.5 * fxn_exp + 2.3) %>%
  
  # filter( upperQ_exp >= 2 | (upperQ_exp >= 1.33 & fxn_exp >= 0.2) ) %>%

  group_by(hpa) %>% 
  mutate(
    n = length(unique(gene)),
    hpa1 = paste0(hpa, ', ', n)
    ) %>% 
  
  ggplot(aes( fxn_exp, color = hpa1))+
  geom_density( alpha = .1)+
  # geom_histogram(position = 'dodge')+
  # scale_y_log10()+
  geom_vline(xintercept = 0.2, lty = 2)+
  scale_fill_discrete('')+scale_color_discrete('')+
  guides(fill = guide_legend(nrow=2))+
  ggforce::facet_zoom(xlim = c(0,.25), ylim = c(0,1.7))+#
  theme(legend.position = 'top')
```
```{r fig.width=6, fig.height=13}
# seaad.broad %>% group_by(cellType) %>% summarise(mn = median(fraction_expressed))

seaad.broad %>% 
  # filter( upperQ_exp >= 2 | (upperQ_exp >= 1.33 & fxn_exp >= 0.2) ) %>%
  mutate(
    hpa = case_when(
      gene %in% brain.genes ~ 'brain.genes',
      gene %in% tad.deg ~ 'tad.deg',
      gene %in% not.brain ~ 'not.brain',
      T ~ 'other')
  ) %>% 
  filter(!is.na(hpa)) %>% 

  # group_by(cellType, hpa) %>% 
  # mutate(top_exp = quantile(upperQ_exp, 0.75),
  #        top_fxn = quantile(fxn_exp, 0.95)) %>% 
  # group_by(cellType) %>%  
  # filter( upperQ_exp > unique(top_exp[hpa == 'not.brain']) ,
  #         fxn_exp > unique(top_fxn[hpa == 'not.brain']) ) %>% 
  # ungroup() %>% 

  filter( upperQ_exp >= -2.5 * fxn_exp + 2.3) %>%
  
  # filter( upperQ_exp >= 2 | (upperQ_exp >= 1.33 & fxn_exp >= 0.2) ) %>%

  group_by(hpa) %>% 
  mutate(
    n = length(unique(gene)),
    hpa1 = paste0(hpa, ', ', n)
    ) %>% 

  ggplot(., aes(fxn_exp, cellType, fill = hpa1)) + 
  geom_violin(scale = 'width', draw_quantiles = c(.5), trim = F) +
  # geom_point(aes(x = top_fxn, color = hpa))+
  # stat_summary(fun = function(x) quantile(x,0.5), geom="point", size=2, color="red", position = 'dodge')+
  # ggforce::facet_zoom(xlim = c(0,0.08), horizontal = F)
  coord_cartesian(xlim = c(0,1))

```


### avg expression

```{r}
# also "brain genes":
# scores %>% filter(isScored_omics == 'Y', OmicsScore > 0) %>% pull(GeneName) %>% unique()

seaad.broad %>% 
  # filter(is.na(group)) %>% 
  mutate(
    hpa = case_when(
      gene %in% brain.genes ~ paste0('HPA brain (n = ', length(intersect(gene, brain.genes)),' genes)'),
      gene %in% tad.deg ~ paste0('TAD DEG (n = ', length(intersect(gene,tad.deg)),' genes)'),
      gene %in% not.brain ~ paste0('HPA not brain (n = ', length(intersect(gene,not.brain)),' genes)'),
      T ~ paste0('other (n = ', length(unique(setdiff(gene, union(union(brain.genes, tad.deg), not.brain)))) ,' genes)')
      )
  ) %>% 
  filter(!is.na(hpa)) %>% 
  ggplot(aes( (upperQ_exp), fill = hpa))+
  geom_density(aes(color = hpa), alpha = .1)+
  # geom_histogram(position = 'dodge')+
  # scale_y_log10()+
  scale_fill_discrete('')+scale_color_discrete('')+
  guides(fill = guide_legend(nrow=2))+
  ggforce::facet_zoom(xlim = c(0,2), ylim = c(0,1.3) )+
  theme(legend.position = 'top')

```

```{r fig.width=6, fig.height=13, warning=FALSE}
# seaad.broad %>% group_by(cellType) %>% summarise(mn = median(fraction_expressed))

seaad.broad %>% 
  mutate(
    hpa = case_when(
      gene %in% brain.genes ~ paste0('HPA brain (n = ', length(intersect(gene, brain.genes)),' genes)'),
      gene %in% tad.deg ~ paste0('TAD DEG (n = ', length(intersect(gene,tad.deg)),' genes)'),
      gene %in% not.brain ~ paste0('HPA not brain (n = ', length(intersect(gene,not.brain)),' genes)'),
      T ~ paste0('other (n = ', length(unique(setdiff(gene, union(union(brain.genes, tad.deg), not.brain)))) ,' genes)')
      )
  ) %>% 
  group_by(cellType, hpa) %>% 
  mutate(top_exp = quantile(upperQ_exp, 0.75),
         top_fxn = quantile(fxn_exp, 0.75)) %>% 
  ggplot(., aes(upperQ_exp, cellType, fill = hpa)) + 
  geom_violin(scale = 'width', draw_quantiles = c(.5)) +
  # geom_point(aes(x = top_exp, color = hpa))+
  # stat_summary(fun = function(x) quantile(x,0.5), geom="point", size=2, color="red", position = 'dodge')+
  # ggforce::facet_zoom(xlim = c(0,0.08), horizontal = F)
  coord_cartesian(xlim = c(0,6))

```


```{r}
# also "brain genes":
# scores %>% filter(isScored_omics == 'Y', OmicsScore > 0) %>% pull(GeneName) %>% unique()

seaad.broad %>% 
  # filter(is.na(group)) %>% 
  mutate(
    hpa = case_when(
      gene %in% brain.genes ~ paste0('HPA brain (n = ', length(intersect(gene, brain.genes)),' genes)'),
      gene %in% tad.deg ~ paste0('TAD DEG (n = ', length(intersect(gene,tad.deg)),' genes)'),
      gene %in% not.brain ~ paste0('HPA not brain (n = ', length(intersect(gene,not.brain)),' genes)'),
      T ~ paste0('other (n = ', length(unique(setdiff(gene, union(union(brain.genes, tad.deg), not.brain)))) ,' genes)')
      )
  ) %>% 
  # group_by(cellType, hpa) %>% 
  # mutate(md_exp = quantile(upperQ_exp, 0.5),
  #        fivepct_exp = quantile(upperQ_exp, 0.95), 
  #        fivepct_fxn = quantile(fxn_exp, .5)) %>% 
  filter(!is.na(hpa)) %>% 
  ggplot(aes( (upperQ_exp), fill = hpa))+
  # geom_density(aes(color = hpa), alpha = .1)+
  geom_histogram(position = 'dodge')+
  # scale_y_log10()+
  scale_fill_discrete('')+scale_color_discrete('')+
  guides(fill = guide_legend(nrow=2))+
  ggforce::facet_zoom(xlim = c(0,2), ylim = c(0,3.5e4) )+
  theme(legend.position = 'top')

```

```{r}
# also "brain genes":
# scores %>% filter(isScored_omics == 'Y', OmicsScore > 0) %>% pull(GeneName) %>% unique()

seaad.broad %>% 
  # filter( upperQ_exp >= 2 | (upperQ_exp >= 1.33 & fxn_exp >= 0.2) ) %>%
  mutate(
    hpa = case_when(
      gene %in% brain.genes ~ 'brain.genes',
      gene %in% tad.deg ~ 'tad.deg',
      gene %in% not.brain ~ 'not.brain',
      T ~ 'other')
  ) %>% 
  filter(!is.na(hpa)) %>% 

  # group_by(cellType, hpa) %>% 
  # mutate(top_exp = quantile(upperQ_exp, 0.75),
  #        top_fxn = quantile(fxn_exp, 0.95)) %>% 
  # group_by(cellType) %>%  
  # filter( upperQ_exp > unique(top_exp[hpa == 'not.brain']) ,
  #         fxn_exp > unique(top_fxn[hpa == 'not.brain']) ) %>% 
  # ungroup() %>% 
  
  filter( upperQ_exp >= -2.5 * fxn_exp + 2.3) %>%
  
  # filter( upperQ_exp >= 2 | (upperQ_exp >= 1.33 & fxn_exp >= 0.2) ) %>%

  group_by(hpa) %>% 
  mutate(
    n = length(unique(gene)),
    hpa1 = paste0(hpa, ', ', n)
    ) %>% 
  
  ggplot(aes( upperQ_exp, fill = hpa1))+
  # geom_density(aes(color = hpa), alpha = .1)+
  geom_histogram(position = 'dodge')+
  # scale_y_log10()+
  scale_fill_discrete('')+scale_color_discrete('')+
  guides(fill = guide_legend(nrow=2))+
  ggforce::facet_zoom(xlim = c(0,2), ylim = c(0,3.5e4) )+
  theme(legend.position = 'top')
```


```{r}
# also "brain genes":
# scores %>% filter(isScored_omics == 'Y', OmicsScore > 0) %>% pull(GeneName) %>% unique()

seaad.broad %>% 
  # filter( upperQ_exp >= 2 | (upperQ_exp >= 1.33 & fxn_exp >= 0.2) ) %>%
  mutate(
    hpa = case_when(
      gene %in% brain.genes ~ 'brain.genes',
      gene %in% tad.deg ~ 'tad.deg',
      gene %in% not.brain ~ 'not.brain',
      T ~ 'other')
  ) %>% 
  filter(!is.na(hpa)) %>% 

  # group_by(cellType, hpa) %>% 
  # mutate(top_exp = quantile(upperQ_exp, 0.75),
  #        top_fxn = quantile(fxn_exp, 0.95)) %>% 
  # group_by(cellType) %>%  
  # filter( upperQ_exp > unique(top_exp[hpa == 'not.brain']) ,
  #         fxn_exp > unique(top_fxn[hpa == 'not.brain']) ) %>% 
  # ungroup() %>% 

  filter( upperQ_exp >= -2.5 * fxn_exp + 2.3) %>%
  
  # filter( upperQ_exp >= 2 | (upperQ_exp >= 1.33 & fxn_exp >= 0.2) ) %>%

  group_by(hpa) %>% 
  mutate(
    n = length(unique(gene)),
    hpa1 = paste0(hpa, ', ', n)
    ) %>% 

  ggplot(aes( upperQ_exp, color = hpa1 ))+
  geom_density( alpha = .1)+
  # geom_histogram(position = 'dodge')+
  # scale_y_log10()+
  scale_fill_discrete('')+scale_color_discrete('')+
  guides(color = guide_legend(nrow=2))+
  ggforce::facet_zoom(xlim = c(0,2), ylim = c(0,1.3) )+
  theme(legend.position = 'top')
```

```{r fig.width=6, fig.height=13, warning=FALSE}
# seaad.broad %>% group_by(cellType) %>% summarise(mn = median(fraction_expressed))

seaad.broad %>% 
  # filter( upperQ_exp >= 2 | (upperQ_exp >= 1.33 & fxn_exp >= 0.2) ) %>%
  mutate(
    hpa = case_when(
      gene %in% brain.genes ~ 'brain.genes',
      gene %in% tad.deg ~ 'tad.deg',
      gene %in% not.brain ~ 'not.brain',
      T ~ 'other')
  ) %>% 
  filter(!is.na(hpa)) %>% 

  # group_by(cellType, hpa) %>% 
  # mutate(top_exp = quantile(upperQ_exp, 0.75),
  #        top_fxn = quantile(fxn_exp, 0.95)) %>% 
  # group_by(cellType) %>%  
  # filter( upperQ_exp > unique(top_exp[hpa == 'not.brain']) ,
  #         fxn_exp > unique(top_fxn[hpa == 'not.brain']) ) %>% 
  # ungroup() %>% 

  filter( upperQ_exp >= -2.5 * fxn_exp + 2.3) %>%
  
  # filter( upperQ_exp >= 2 | (upperQ_exp >= 1.33 & fxn_exp >= 0.2) ) %>%

  group_by(hpa) %>% 
  mutate(
    n = length(unique(gene)),
    hpa1 = paste0(hpa, ', ', n)
    ) %>% 
  
  ggplot(., aes(upperQ_exp, cellType, fill = hpa1)) + 
  geom_violin(scale = 'width', draw_quantiles = c(.5), trim = F) +
  # geom_point(aes(x = top_exp, color = hpa))+
  # stat_summary(fun = function(x) quantile(x,0.5), geom="point", size=2, color="red", position = 'dodge')+
  # ggforce::facet_zoom(xlim = c(0,0.08), horizontal = F)
  coord_cartesian(xlim = c(0,6))

```


### celltype-specific genes
```{r}
# McKenzie brain cell type specfic expression PMID 29892006
url='https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5995803/bin/41598_2018_27293_MOESM2_ESM.xlsx'
httr::GET(url, httr::write_disk(tf <- tempfile(fileext = ".xlsx")))

# readxl::excel_sheets(tf)
# [1] "top_all_enrich"        "top_human_enrich"      "top_mouse_enrich"     
# [4] "top_all_expression"    "top_human_expression"  "top_mouse_expression" 
# [7] "top_all_specificity"   "top_human_specificity" "top_mouse_specificity"

ct_spec = readxl::read_xlsx(tf,sheet = 'top_all_enrich', skip = 1)

ct_spec %>% 
  group_by(Celltype) %>% 
  summarise(mn = median(grand_mean), sd = sd(grand_mean), mn_sd = mn+sd) %>% 
  arrange(desc(mn_sd))

dups = ct_spec$gene[which(duplicated(ct_spec$gene))] %>% unique() 
```

```{r}
ct_spec %>% 
  filter(!(gene %in% dups)) %>% 
  group_by(Celltype) %>% 
  mutate(mn = median(grand_mean), sd = sd(grand_mean), mn_sd = mn+sd) %>% 
  ggplot(aes(grand_mean, color = Celltype))+
  geom_density()+
  geom_vline(aes(xintercept = mn_sd, color = Celltype))

```


```{r fig.width=7, fig.height=3, warning=FALSE}
# seaad.broad = read_csv('/projects/carter-lab/caryg/seaAD/data/seaAD_broad_summaryCounts.csv')
# seaad.broad = read_csv('/projects/carter-lab/caryg/seaAD/data/seaAD_broad_upperQ_summaryCounts.csv')

ct_spec %>% 
  filter(!(gene %in% dups)) %>% 
  group_by(Celltype) %>% 
  mutate(mn = median(grand_mean), sd = sd(grand_mean), mn_sd = mn+sd) %>% 
  filter(grand_mean > mn_sd) %>% 
  select(gene, Celltype) %>% 
  distinct() %>% 
  inner_join(seaad.broad, ., by = 'gene') %>% 

  # filter( upperQ_exp >= -2.5 * fxn_exp + 2.5) %>%

  ggplot(., aes(broad, upperQ_exp, fill = Celltype)) + 
  geom_violin(scale = 'width', draw_quantiles = c(.5), trim = F) 

```

```{r fig.width=7, fig.height=3}
# seaad.broad = read_csv('/projects/carter-lab/caryg/seaAD/data/seaAD_broad_summaryCounts.csv')
# seaad.broad = read_csv('/projects/carter-lab/caryg/seaAD/data/seaAD_broad_upperQ_summaryCounts.csv')

ct_spec %>% 
  filter(!(gene %in% dups)) %>% 
  group_by(Celltype) %>% 
  mutate(mn = median(grand_mean), sd = sd(grand_mean), mn_sd = mn+sd) %>% 
  filter(grand_mean > mn_sd) %>% 
  select(gene, Celltype) %>% 
  distinct() %>% 
  inner_join(seaad.broad, ., by = 'gene') %>% 

  filter( upperQ_exp >= -2.5 * fxn_exp + 2.3) %>%

  ggplot(., aes(broad, upperQ_exp, fill = Celltype)) + 
  geom_violin(scale = 'width', draw_quantiles = c(.5), trim = F) 

```

## supertype
```{r}
seaad = read_csv('/projects/carter-lab/caryg/seaAD/data/seaAD_upperQ_summaryCounts.csv')
```
### both dimensions

```{r}
t = .9

tmp = seaad %>% 

  # filter(gene %in% not.brain) %>% 
  # mutate(hpa = 'not') %>% 

  mutate(
      hpa = case_when(
          gene %in% brain.genes ~ 'brain',
          gene %in% not.brain ~ 'not',
          gene %in% tad.deg ~ 'deg',
          T ~ 'other'
      )
  ) %>%

  group_by(cellType, hpa) %>% 
  summarise( 
    exp = quantile(upperQ_exp, t), 
    fxn = quantile(fxn_exp, t)
    ) 

# bind_rows(
#     tmp, 
#     tmp %>% filter(hpa == 'not') %>% mutate(exp = exp + .142, fxn = fxn + .142, hpa = 'new')
#   ) %>% 
tmp %>% 
  ggplot(aes(fxn, exp, group = hpa))+
  geom_smooth(method = 'lm', color = 'grey20', lwd = .5, lty = 2)+
  # geom_abline(intercept = 1.5294, slope = -2.562569)+
  geom_abline(intercept = 2.3, slope = -2.5)+
  annotate(geom = 'text', x = .65, y = 0, label = 'y = -2.5x + 2.3', hjust = 0)+
  geom_point(aes(color = cellType, shape = hpa), size = 2, alpha = .5)+
  guides(color = 'none')+
  labs(y = 'quantile expression', x = 'quantile fraction expressing',
       subtitle = paste0('plotting quantile: ', t))

```


```{r}
t = .9

seaad %>% 
  
  # filter(gene %in% not.brain) %>% 
  # mutate(hpa = 'not') %>% 

  mutate(
      hpa = case_when(
          gene %in% brain.genes ~ 'brain',
          gene %in% not.brain ~ 'not',
          gene %in% tad.deg ~ 'deg',
          T ~ 'other'
      )
  ) %>%
  filter(hpa == 'not') %>%

  group_by(cellType, hpa) %>%
  summarise( exp = quantile(upperQ_exp, t), 
             fxn = quantile(fxn_exp, t)
             ) %>% 
  lm(exp~fxn, data = .) %>% 
  broom::tidy()
```

```{r}
x = map_dfr(
    seq(1.5,3,.1),
    ~{
        seaad %>% 
            filter( upperQ_exp >= -2.5 * fxn_exp + .x) %>% 
            summarise(
                int = .x,
                n.brain = length(intersect(gene, brain.genes )),
                n.not = length(intersect(gene,not.brain)),
                n.deg = length(intersect(gene,tad.deg)),
                n.other = length(unique(setdiff(gene, union(union(brain.genes, tad.deg), not.brain)))),
                diff.b = (n.brain - n.not),
                pct.b = 100*(diff.b/n.brain),
                diff.d = n.deg - n.not,
                pct.d = 100*(diff.d/n.brain)
            )
    }
) %>% 
  arrange(desc(diff.b), desc(pct.d));

qplot(x$int, x$diff.b, geom = 'line')

DT::datatable(x)
```

```{r}
t = .9

thresh = seaad %>% 
  filter(gene %in% not.brain) %>%
  group_by(broad, cellType) %>%
  summarise( 
    exp1 = quantile(upperQ_exp, t),
    fxn1 = quantile(fxn_exp, t)
  ) %>% 
  mutate(
    exp = exp1+.142,
    fxn = fxn1+.142,
    hpa = 'new.dat'
  ) 

seaad %>% 

  mutate(
    hpa = case_when(
        gene %in% brain.genes ~ 'brain',
        gene %in% not.brain ~ 'not',
        gene %in% tad.deg ~ 'deg',
        T ~ 'other')
      ) %>% 
  ggplot(aes(fxn_exp, upperQ_exp, group = hpa))+
  geom_abline(intercept = 2.3, slope = -2.5)+
  # annotate(geom = 'text', x = .65, y = 0, label = 'y = -2.5x + 2.5', hjust = 0)+
  geom_point(data = thresh, aes(x = fxn, y = exp), size = 2, alpha = .5)+
  geom_smooth(method = 'lm', aes(color = hpa), lwd = .5, lty = 2)+
  labs(y = 'expression', x = 'fraction expressing'
       #, subtitle = paste0('plotting quantile: ', t)
       )+
  facet_wrap(~broad, scales = 'free')

```


```{r}
t = .9

thresh = seaad %>% 
  filter(gene %in% not.brain) %>%
  group_by(broad, cellType) %>%
  summarise( 
    exp1 = quantile(upperQ_exp, t),
    fxn1 = quantile(fxn_exp, t)
  ) %>% 
  mutate(
    exp = exp1+.142,
    fxn = fxn1+.142,
    hpa = 'new.dat'
  ) 

seaad %>% 
  mutate(
    hpa = case_when(
        gene %in% brain.genes ~ 'brain',
        gene %in% not.brain ~ 'not',
        gene %in% tad.deg ~ 'deg',
        T ~ 'other')
      ) %>% 

  # group_by(cellType) %>%
  # filter(
  #   fxn_exp >= thresh$fxn[ which(thresh$cellType == cellType) ] %>% unique(),
  #   upperQ_exp >= thresh$exp[ which(thresh$cellType == cellType) ] %>% unique(),
  #   .preserve = T
  # ) %>%
  # ungroup() %>%
  
  filter( upperQ_exp >= -2.5 * fxn_exp + 2.3) %>%

  ggplot(aes(fxn_exp, upperQ_exp, group = hpa))+
  geom_abline(intercept = 2.3, slope = -2.5)+
  # annotate(geom = 'text', x = .65, y = 0, label = 'y = -2.5x + 2.5', hjust = 0)+
  geom_point(data = thresh, aes(x = fxn, y = exp), size = 2, alpha = .5)+
  geom_smooth(method = 'lm', aes(color = hpa), lwd = .5, lty = 2)+
  labs(y = 'expression', x = 'fraction expressing'
       #, subtitle = paste0('plotting quantile: ', t)
       )+
  facet_wrap(~broad, scales = 'free')

```

```{r fig.width=8, fig.height=6}
seaad %>% 
  ggplot(aes(upperQ_exp, fxn_exp))+ 
  geom_bin2d(aes(fill = ..count.. ))+
  viridis::scale_fill_viridis(trans = 'log10', option = 'A')+
  ggtitle('no filter')+
  facet_wrap(~broad)
```

```{r fig.width=8, fig.height=6}
thresh = seaad %>% 
  filter(gene %in% not.brain) %>%
  group_by(broad, cellType) %>%
  summarise( 
    exp1 = quantile(upperQ_exp, t),
    fxn1 = quantile(fxn_exp, t)
  ) %>% 
  mutate(
    exp = exp1+.142,
    fxn = fxn1+.142,
    hpa = 'new.dat'
  ) 

seaad %>% 
  mutate(
    hpa = case_when(
        gene %in% brain.genes ~ 'brain',
        gene %in% tad.deg ~ 'deg',
        gene %in% not.brain ~ 'not',
        T ~ 'other')
      ) %>% 
  filter(!is.na(hpa)) %>%     

  # group_by(cellType) %>%
  # filter(
  #   fxn_exp >= thresh$fxn[ which(thresh$cellType == cellType) ] %>% unique(),
  #   upperQ_exp >= thresh$exp[ which(thresh$cellType == cellType) ] %>% unique(),
  #   .preserve = T
  # ) %>%
  # ungroup() %>%

  filter( upperQ_exp >= -2.5 * fxn_exp + 2.3) %>%

  # group_by(cellType, hpa) %>% 
  # mutate( exp = quantile(upperQ_exp, .9), 
  #         fxn = quantile(fxn_exp, .9)
  #         ) %>% 
  # group_by(cellType) %>%
  # filter(  ) %>%
  # ungroup() %>% 
  
  ggplot(aes(upperQ_exp, fxn_exp))+ 
  geom_bin2d(aes(fill = ..count.. ))+
  viridis::scale_fill_viridis(trans = 'log10', option = 'A')+
  facet_wrap(~broad)
```

```{r, fig.width=8, fig.height=8}

seaad %>% 
  mutate(
    hpa = case_when(
      gene %in% brain.genes ~ 'brain.genes',
      gene %in% tad.deg ~ 'tad.deg',
      gene %in% not.brain ~ 'not.brain',
      T ~ 'other')
  ) %>% 
  filter(!is.na(hpa)) %>% 
  group_by(hpa) %>% 
  mutate(
    n = length(unique(gene)),
    hpa1 = paste0(hpa, ', ', n)
    ) %>% 
  ggplot(aes(upperQ_exp, fxn_exp))+ 
  geom_bin2d(aes(fill = ..count.. ))+
  viridis::scale_fill_viridis(trans = 'log10', option = 'A')+
  ggtitle('no filter')+
  facet_grid(broad~hpa1)
 
```

```{r, fig.width=8, fig.height=8}

thresh = seaad %>% 
  filter(gene %in% not.brain) %>%
  group_by(broad, cellType) %>%
  summarise( 
    exp1 = quantile(upperQ_exp, t),
    fxn1 = quantile(fxn_exp, t)
  ) %>% 
  mutate(
    exp = exp1+.142,
    fxn = fxn1+.142,
    hpa = 'new.dat'
  ) 

seaad %>% 
  mutate(
    hpa = case_when(
        gene %in% brain.genes ~ 'brain',
        gene %in% tad.deg ~ 'tad.deg',
        gene %in% not.brain ~ 'not.brain',
        T ~ 'other')
      ) %>% 
  filter(!is.na(hpa)) %>%     

  # group_by(cellType) %>%
  # filter(
  #   fxn_exp >= thresh$fxn[ which(thresh$cellType == cellType) ] %>% unique(),
  #   upperQ_exp >= thresh$exp[ which(thresh$cellType == cellType) ] %>% unique(),
  #   .preserve = T
  # ) %>%
  # ungroup() %>%
  
  filter( upperQ_exp >= -2.5 * fxn_exp + 2.3) %>%
  
  # filter( upperQ_exp >= 2 | (upperQ_exp >= 1.33 & fxn_exp >= 0.2) ) %>%

  # group_by(cellType, hpa) %>%
  # mutate(top_exp = quantile(upperQ_exp, 0.75),
  #        top_fxn = quantile(fxn_exp, 0.95)) %>%
  # group_by(cellType) %>%
  # filter( upperQ_exp > unique(top_exp[hpa == 'not.brain']) ,
  #         fxn_exp > unique(top_fxn[hpa == 'not.brain']) ) %>%
  # ungroup() %>%
  
  group_by(hpa) %>% 
  mutate(
    n = length(unique(gene)),
    hpa1 = paste0(hpa, ', ', n)
    ) %>% 
  ggplot(aes(upperQ_exp, fxn_exp))+ 
  geom_bin2d(aes(fill = ..count.. ))+
  viridis::scale_fill_viridis(trans = 'log10', option = 'A')+
  ggtitle('filtered')+
  facet_grid(broad~hpa1)
 
```


### fxn expressed
```{r}
# also "brain genes":
# scores %>% filter(isScored_omics == 'Y', OmicsScore > 0) %>% pull(GeneName) %>% unique()

seaad %>% 
  # filter(is.na(group)) %>% 
  mutate(
    hpa = case_when(
      gene %in% brain.genes ~ paste0('HPA brain (n = ', length(intersect(gene, brain.genes)),' genes)'),
      gene %in% tad.deg ~ paste0('TAD DEG (n = ', length(intersect(gene,tad.deg)),' genes)'),
      gene %in% not.brain ~ paste0('HPA not brain (n = ', length(intersect(gene,not.brain)),' genes)'),
      T ~ paste0('other (n = ', length(unique(setdiff(gene, union(union(brain.genes, tad.deg), not.brain)))) ,' genes)')
      )
  ) %>% 
  filter(!is.na(hpa)) %>% 
  ggplot(aes( fxn_exp, fill = hpa))+
  geom_density(aes(color = hpa), alpha = .1)+
  # geom_histogram(position = 'dodge')+
  # scale_y_log10()+
  scale_fill_discrete('')+scale_color_discrete('')+
  guides(fill = guide_legend(nrow=2))+
  ggforce::facet_zoom(xlim = c(0,.25), ylim = c(0,5))+
  theme(legend.position = 'top')
```

```{r fig.width=6, fig.height=13}
# seaad %>% group_by(cellType) %>% summarise(mn = median(fraction_expressed))

seaad %>% 
  mutate(
    hpa = case_when(
      gene %in% brain.genes ~ paste0('HPA brain (n = ', length(intersect(gene, brain.genes)),' genes)'),
      gene %in% tad.deg ~ paste0('TAD DEG (n = ', length(intersect(gene,tad.deg)),' genes)'),
      gene %in% not.brain ~ paste0('HPA not brain (n = ', length(intersect(gene,not.brain)),' genes)'),
      T ~ paste0('other (n = ', length(unique(setdiff(gene, union(union(brain.genes, tad.deg), not.brain)))) ,' genes)')
      )
  ) %>% 
  # group_by(cellType, hpa) %>% 
  # mutate(top_exp = quantile(upperQ_exp, 0.75),
  #        top_fxn = quantile(fxn_exp, 0.75)) %>% 
  ggplot(., aes(fxn_exp, broad, fill = hpa)) + 
  geom_violin(scale = 'width', draw_quantiles = c(.5)) +
  # geom_point(aes(x = top_fxn, color = hpa))+
  # stat_summary(fun = function(x) quantile(x,0.5), geom="point", size=2, color="red", position = 'dodge')+
  # ggforce::facet_zoom(xlim = c(0,0.08), horizontal = F)
  coord_cartesian(xlim = c(0,0.25))

```

```{r}
# also "brain genes":
# scores %>% filter(isScored_omics == 'Y', OmicsScore > 0) %>% pull(GeneName) %>% unique()

seaad %>% 
  # filter(is.na(group)) %>% 
  mutate(
    hpa = case_when(
      gene %in% brain.genes ~ paste0('HPA brain (n = ', length(intersect(gene, brain.genes)),' genes)'),
      gene %in% tad.deg ~ paste0('TAD DEG (n = ', length(intersect(gene,tad.deg)),' genes)'),
      gene %in% not.brain ~ paste0('HPA not brain (n = ', length(intersect(gene,not.brain)),' genes)'),
      T ~ paste0('other (n = ', length(unique(setdiff(gene, union(union(brain.genes, tad.deg), not.brain)))) ,' genes)')
      )
  ) %>% 
  filter(!is.na(hpa)) %>% 
  ggplot(aes( fxn_exp, fill = hpa))+
  # geom_density(aes(color = hpa), alpha = .1)+
  geom_histogram(position = 'dodge')+
  # scale_y_log10()+
  scale_fill_discrete('')+scale_color_discrete('')+
  guides(fill = guide_legend(nrow=2))+
  ggforce::facet_zoom(xlim = c(0,.25), ylim = c(0,1e5))+
  theme(legend.position = 'top')
```

```{r}
# also "brain genes":
# scores %>% filter(isScored_omics == 'Y', OmicsScore > 0) %>% pull(GeneName) %>% unique()

seaad %>% 
  # filter( upperQ_exp >= 2 | (upperQ_exp >= 1.33 & fxn_exp >= 0.2) ) %>%
  mutate(
    hpa = case_when(
      gene %in% brain.genes ~ 'brain.genes',
      gene %in% tad.deg ~ 'tad.deg',
      gene %in% not.brain ~ 'not.brain',
      T ~ 'other')
  ) %>% 
  filter(!is.na(hpa)) %>% 

  # group_by(cellType, hpa) %>% 
  # mutate(top_exp = quantile(upperQ_exp, 0.75),
  #        top_fxn = quantile(fxn_exp, 0.95)) %>% 
  # group_by(cellType) %>%  
  # filter( upperQ_exp > unique(top_exp[hpa == 'not.brain']) ,
  #         fxn_exp > unique(top_fxn[hpa == 'not.brain']) ) %>% 
  # ungroup() %>% 
  
  filter( upperQ_exp >= -2.5 * fxn_exp + 2.3) %>%
  
  # filter( upperQ_exp >= 2 | (upperQ_exp >= 1.33 & fxn_exp >= 0.2) ) %>%

  group_by(hpa) %>% 
  mutate(
    n = length(unique(gene)),
    hpa1 = paste0(hpa, ', ', n)
    ) %>% 
  
  ggplot(aes( fxn_exp, fill = hpa1))+
  # geom_density(aes(color = hpa1), alpha = .1)+
  geom_histogram(position = 'dodge')+
  # scale_y_log10()+
  scale_fill_discrete('')+scale_color_discrete('')+
  guides(fill = guide_legend(nrow=2))+
  ggforce::facet_zoom(xlim = c(0,.25), ylim = c(0,1e5))+
  theme(legend.position = 'top')
```



```{r}
# also "brain genes":
# scores %>% filter(isScored_omics == 'Y', OmicsScore > 0) %>% pull(GeneName) %>% unique()

seaad %>% 
  # filter( upperQ_exp >= 2 | (upperQ_exp >= 1.33 & fxn_exp >= 0.2) ) %>%
  mutate(
    hpa = case_when(
      gene %in% brain.genes ~ 'brain.genes',
      gene %in% tad.deg ~ 'tad.deg',
      gene %in% not.brain ~ 'not.brain',
      T ~ 'other')
  ) %>% 
  filter(!is.na(hpa)) %>% 

  # group_by(cellType, hpa) %>% 
  # mutate(top_exp = quantile(upperQ_exp, 0.75),
  #        top_fxn = quantile(fxn_exp, 0.95)) %>% 
  # group_by(cellType) %>%  
  # filter( upperQ_exp > unique(top_exp[hpa == 'not.brain']) ,
  #         fxn_exp > unique(top_fxn[hpa == 'not.brain']) ) %>% 
  # ungroup() %>% 
  
  filter( upperQ_exp >= -2.5 * fxn_exp + 2.3) %>%
  
  # filter( upperQ_exp >= 2 | (upperQ_exp >= 1.33 & fxn_exp >= 0.2) ) %>%

  group_by(hpa) %>% 
  mutate(
    n = length(unique(gene)),
    hpa1 = paste0(hpa, ', ', n)
    ) %>% 
  
  ggplot(aes( fxn_exp, color = hpa1))+
  geom_density( alpha = .1)+
  # geom_histogram(position = 'dodge')+
  # scale_y_log10()+
  geom_vline(xintercept = 0.2, lty = 2)+
  scale_fill_discrete('')+scale_color_discrete('')+
  guides(fill = guide_legend(nrow=2))+
  ggforce::facet_zoom(xlim = c(0,.25), ylim = c(0,1.7))+#
  theme(legend.position = 'top')
```
```{r fig.width=6, fig.height=13}
# seaad %>% group_by(cellType) %>% summarise(mn = median(fraction_expressed))

seaad %>% 
  # filter( upperQ_exp >= 2 | (upperQ_exp >= 1.33 & fxn_exp >= 0.2) ) %>%
  mutate(
    hpa = case_when(
      gene %in% brain.genes ~ 'brain.genes',
      gene %in% tad.deg ~ 'tad.deg',
      gene %in% not.brain ~ 'not.brain',
      T ~ 'other')
  ) %>% 
  filter(!is.na(hpa)) %>% 

  # group_by(cellType, hpa) %>% 
  # mutate(top_exp = quantile(upperQ_exp, 0.75),
  #        top_fxn = quantile(fxn_exp, 0.95)) %>% 
  # group_by(cellType) %>%  
  # filter( upperQ_exp > unique(top_exp[hpa == 'not.brain']) ,
  #         fxn_exp > unique(top_fxn[hpa == 'not.brain']) ) %>% 
  # ungroup() %>% 

  filter( upperQ_exp >= -2.5 * fxn_exp + 2.3) %>%
  
  # filter( upperQ_exp >= 2 | (upperQ_exp >= 1.33 & fxn_exp >= 0.2) ) %>%

  group_by(hpa) %>% 
  mutate(
    n = length(unique(gene)),
    hpa1 = paste0(hpa, ', ', n)
    ) %>% 

  ggplot(., aes(fxn_exp, broad, fill = hpa1)) + 
  geom_violin(scale = 'width', draw_quantiles = c(.5), trim = F) +
  # geom_point(aes(x = top_fxn, color = hpa))+
  # stat_summary(fun = function(x) quantile(x,0.5), geom="point", size=2, color="red", position = 'dodge')+
  # ggforce::facet_zoom(xlim = c(0,0.08), horizontal = F)
  coord_cartesian(xlim = c(0,1))

```


### avg expression

```{r}
# also "brain genes":
# scores %>% filter(isScored_omics == 'Y', OmicsScore > 0) %>% pull(GeneName) %>% unique()

seaad %>% 
  # filter(is.na(group)) %>% 
  mutate(
    hpa = case_when(
      gene %in% brain.genes ~ 'brain.genes',
      gene %in% tad.deg ~ 'tad.deg',
      gene %in% not.brain ~ 'not.brain',
      T ~ 'other')
  ) %>% 
  filter(!is.na(hpa)) %>% 
  group_by(hpa) %>% 
  mutate(
    n = length(unique(gene)),
    hpa1 = paste0(hpa, ', ', n)
    ) %>% 
  ggplot(aes( (upperQ_exp), fill = hpa1))+
  geom_density(aes(color = hpa), alpha = .1)+
  # geom_histogram(position = 'dodge')+
  # scale_y_log10()+
  scale_fill_discrete('')+scale_color_discrete('')+
  guides(fill = guide_legend(nrow=2))+
  ggforce::facet_zoom(xlim = c(0,2), ylim = c(0,1.3) )+
  theme(legend.position = 'top')

```

```{r fig.width=6, fig.height=13, warning=FALSE}
# seaad %>% group_by(cellType) %>% summarise(mn = median(fraction_expressed))

seaad %>% 
  mutate(
    hpa = case_when(
      gene %in% brain.genes ~ 'brain.genes',
      gene %in% tad.deg ~ 'tad.deg',
      gene %in% not.brain ~ 'not.brain',
      T ~ 'other')
  ) %>% 
  filter(!is.na(hpa)) %>% 
  group_by(hpa) %>% 
  mutate(
    n = length(unique(gene)),
    hpa1 = paste0(hpa, ', ', n)
    ) %>% 
  # group_by(cellType, hpa) %>% 
  # mutate(top_exp = quantile(upperQ_exp, 0.75),
  #        top_fxn = quantile(fxn_exp, 0.75)) %>% 
  ggplot(., aes(upperQ_exp, broad, fill = hpa1)) + 
  geom_violin(scale = 'width', draw_quantiles = c(.5)) +
  # geom_point(aes(x = top_exp, color = hpa))+
  # stat_summary(fun = function(x) quantile(x,0.5), geom="point", size=2, color="red", position = 'dodge')+
  # ggforce::facet_zoom(xlim = c(0,0.08), horizontal = F)
  coord_cartesian(xlim = c(0,6))

```


```{r}
# also "brain genes":
# scores %>% filter(isScored_omics == 'Y', OmicsScore > 0) %>% pull(GeneName) %>% unique()

seaad %>% 
  # filter(is.na(group)) %>% 
  mutate(
    hpa = case_when(
      gene %in% brain.genes ~ 'brain.genes',
      gene %in% tad.deg ~ 'tad.deg',
      gene %in% not.brain ~ 'not.brain',
      T ~ 'other')
  ) %>% 
  filter(!is.na(hpa)) %>% 
  group_by(hpa) %>% 
  mutate(
    n = length(unique(gene)),
    hpa1 = paste0(hpa, ', ', n)
    ) %>% 
  ggplot(aes( (upperQ_exp), fill = hpa1))+
  # geom_density(aes(color = hpa), alpha = .1)+
  geom_histogram(position = 'dodge')+
  # scale_y_log10()+
  scale_fill_discrete('')+scale_color_discrete('')+
  guides(fill = guide_legend(nrow=2))+
  ggforce::facet_zoom(xlim = c(0,2), ylim = c(0,3.5e4) )+
  theme(legend.position = 'top')

```

```{r}
# also "brain genes":
# scores %>% filter(isScored_omics == 'Y', OmicsScore > 0) %>% pull(GeneName) %>% unique()

seaad %>% 
  # filter( upperQ_exp >= 2 | (upperQ_exp >= 1.33 & fxn_exp >= 0.2) ) %>%
  mutate(
    hpa = case_when(
      gene %in% brain.genes ~ 'brain.genes',
      gene %in% tad.deg ~ 'tad.deg',
      gene %in% not.brain ~ 'not.brain',
      T ~ 'other')
  ) %>% 
  filter(!is.na(hpa)) %>% 

  # group_by(cellType, hpa) %>% 
  # mutate(top_exp = quantile(upperQ_exp, 0.75),
  #        top_fxn = quantile(fxn_exp, 0.95)) %>% 
  # group_by(cellType) %>%  
  # filter( upperQ_exp > unique(top_exp[hpa == 'not.brain']) ,
  #         fxn_exp > unique(top_fxn[hpa == 'not.brain']) ) %>% 
  # ungroup() %>% 
  
  filter( upperQ_exp >= -2.5 * fxn_exp + 2.3) %>%
  
  # filter( upperQ_exp >= 2 | (upperQ_exp >= 1.33 & fxn_exp >= 0.2) ) %>%

  group_by(hpa) %>% 
  mutate(
    n = length(unique(gene)),
    hpa1 = paste0(hpa, ', ', n)
    ) %>% 
  
  ggplot(aes( upperQ_exp, fill = hpa1))+
  # geom_density(aes(color = hpa), alpha = .1)+
  geom_histogram(position = 'dodge')+
  # scale_y_log10()+
  scale_fill_discrete('')+scale_color_discrete('')+
  guides(fill = guide_legend(nrow=2))+
  ggforce::facet_zoom(xlim = c(0,2), ylim = c(0,3.5e4) )+
  theme(legend.position = 'top')
```


```{r}
# also "brain genes":
# scores %>% filter(isScored_omics == 'Y', OmicsScore > 0) %>% pull(GeneName) %>% unique()

seaad %>% 
  # filter( upperQ_exp >= 2 | (upperQ_exp >= 1.33 & fxn_exp >= 0.2) ) %>%
  mutate(
    hpa = case_when(
      gene %in% brain.genes ~ 'brain.genes',
      gene %in% tad.deg ~ 'tad.deg',
      gene %in% not.brain ~ 'not.brain',
      T ~ 'other')
  ) %>% 
  filter(!is.na(hpa)) %>% 

  # group_by(cellType, hpa) %>% 
  # mutate(top_exp = quantile(upperQ_exp, 0.75),
  #        top_fxn = quantile(fxn_exp, 0.95)) %>% 
  # group_by(cellType) %>%  
  # filter( upperQ_exp > unique(top_exp[hpa == 'not.brain']) ,
  #         fxn_exp > unique(top_fxn[hpa == 'not.brain']) ) %>% 
  # ungroup() %>% 

  filter( upperQ_exp >= -2.5 * fxn_exp + 2.3) %>%
  
  # filter( upperQ_exp >= 2 | (upperQ_exp >= 1.33 & fxn_exp >= 0.2) ) %>%

  group_by(hpa) %>% 
  mutate(
    n = length(unique(gene)),
    hpa1 = paste0(hpa, ', ', n)
    ) %>% 

  ggplot(aes( upperQ_exp, color = hpa1 ))+
  geom_density( alpha = .1)+
  # geom_histogram(position = 'dodge')+
  # scale_y_log10()+
  scale_fill_discrete('')+scale_color_discrete('')+
  guides(color = guide_legend(nrow=2))+
  ggforce::facet_zoom(xlim = c(0,2), ylim = c(0,1.3) )+
  theme(legend.position = 'top')
```

```{r fig.width=6, fig.height=13, warning=FALSE}
# seaad %>% group_by(cellType) %>% summarise(mn = median(fraction_expressed))

seaad %>% 
  # filter( upperQ_exp >= 2 | (upperQ_exp >= 1.33 & fxn_exp >= 0.2) ) %>%
  mutate(
    hpa = case_when(
      gene %in% brain.genes ~ 'brain.genes',
      gene %in% tad.deg ~ 'tad.deg',
      gene %in% not.brain ~ 'not.brain',
      T ~ 'other')
  ) %>% 
  filter(!is.na(hpa)) %>% 

  # group_by(cellType, hpa) %>% 
  # mutate(top_exp = quantile(upperQ_exp, 0.75),
  #        top_fxn = quantile(fxn_exp, 0.95)) %>% 
  # group_by(cellType) %>%  
  # filter( upperQ_exp > unique(top_exp[hpa == 'not.brain']) ,
  #         fxn_exp > unique(top_fxn[hpa == 'not.brain']) ) %>% 
  # ungroup() %>% 

  filter( upperQ_exp >= -2.5 * fxn_exp + 2.3) %>%
  
  # filter( upperQ_exp >= 2 | (upperQ_exp >= 1.33 & fxn_exp >= 0.2) ) %>%

  group_by(hpa) %>% 
  mutate(
    n = length(unique(gene)),
    hpa1 = paste0(hpa, ', ', n)
    ) %>% 
  
  ggplot(., aes(upperQ_exp, broad, fill = hpa1)) + 
  geom_violin(scale = 'width', draw_quantiles = c(.5), trim = F) +
  # geom_point(aes(x = top_exp, color = hpa))+
  # stat_summary(fun = function(x) quantile(x,0.5), geom="point", size=2, color="red", position = 'dodge')+
  # ggforce::facet_zoom(xlim = c(0,0.08), horizontal = F)
  coord_cartesian(xlim = c(0,6))

```

```{r}
seaad.expr <- seaad %>% 
  filter( upperQ_exp >= -2.5 * fxn_exp + 2.3 ) %>%
  pull(gene) %>% 
  unique()
```


# NODE: overall

```{r}
tot.nodes = v.attr$name
filt.nodes = union(seaad.expr, tad.deg) %>% union(., brain.genes) %>% intersect(.,v.attr$name) 

grid::grid.newpage()
grid::grid.draw(
  VennDiagram::venn.diagram(
        x = list(
          `PathCommons_NW\n(19087)` = v.attr$name %>% .[!is.na(.)], 
          `HumanProtAtlas_brain\n(4140)` = brain.genes %>% .[!is.na(.)],
          `SeaAD\n(10594)` = seaad.expr %>% .[!is.na(.)],
          `TreatAD_DEG\n(11910)` = tad.deg %>% .[!is.na(.)]
        ),
        filename = NULL,
        force.unique = T,
        lty = 0, alpha = .3 , 
        fill = c('light blue','yellow', 'green','purple'),
        
        sub = paste0('# Pathway Commons nodes: ', length(tot.nodes),
                     '\n# filtered nodes: ', length(filt.nodes), 
                     ' (', signif( 100*length(filt.nodes)/length(tot.nodes), digits = 4), '%)' ),
        
        cat.cex = .8,
        ext.pos = 180,
        ext.dist = -.1
        )
)

```


# EDGE: Pathway Commons Network

Specify the directed-edge types to filter the Pathway Commons graph  
```{r}
directed_edge_types = c("catalysis-precedes",
                        "controls-expression-of",
                        "controls-phosphorylation-of",
                        "controls-state-change-of",
                        "controls-transport-of"
                        )

# dir.net <- graph_from_data_frame(d = net.tbl %>% filter(interaction %in% directed_edge_types), directed = T)
```

How many edges from each source?  
```{r warning=FALSE}
bind_cols(
    sources = str_split(net.tbl$sources,',') %>% unlist %>% unique, 
    n_edge = map_dbl( 
        str_split(net.tbl$sources,',') %>% unlist %>% unique, 
        ~ net.tbl %>% filter(grepl(.x, sources)) %>% nrow() ),
    any_directed = map_lgl(
        str_split(net.tbl$sources,',') %>% unlist %>% unique, 
        ~ net.tbl %>% 
            mutate(directed = if_else(interaction %in% directed_edge_types, 'dir','undir') ) %>% 
            filter(grepl(.x, sources)) %>% pull(directed) %>% any(. == 'dir')
    )
) %>% 
  mutate(any_directed = if_else(is.na(any_directed), FALSE, TRUE),
         any_directed = factor(any_directed, levels=c('TRUE','FALSE'))) %>%
  arrange(desc(n_edge)) %>% mutate(sources = fct_relevel(sources, sources)) %>%
  ggplot(aes(sources, n_edge)) + geom_bar(stat = 'identity', aes(fill = any_directed)) +
  # scale_y_log10()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)
        , legend.position = 'top')
```

Which edge sources are (generally) well supported?  
```{r warning=FALSE}
bind_cols(
    sources = str_split(net.tbl$sources,',') %>% unlist %>% unique, 
    n_edge = map_dbl( 
      str_split(net.tbl$sources,',') %>% unlist %>% unique, 
      ~ net.tbl %>% filter(grepl(.x, sources)) %>% nrow() )
    , median_evidence_per_edge = map_dbl( 
      str_split(net.tbl$sources,',') %>% unlist %>% unique, 
      ~ net.tbl %>% filter(grepl(.x, sources)) %>% pull(n_edge_evidence) %>% median() )
    , any_directed = map_lgl(
        str_split(net.tbl$sources,',') %>% unlist %>% unique, 
        ~ net.tbl %>% 
            mutate(directed = if_else(interaction %in% directed_edge_types, 'dir','undir') ) %>% 
            filter(grepl(.x, sources)) %>% pull(directed) %>% any(. == 'dir') )
) %>% 
  mutate(any_directed = if_else(is.na(any_directed), FALSE, TRUE),
         any_directed = factor(any_directed, levels=c('TRUE','FALSE'))) %>%
  arrange(desc(n_edge)) %>% mutate(sources = fct_relevel(sources, sources)) %>% 
  ggplot(aes(n_edge, median_evidence_per_edge)) +
  geom_point( aes(color = any_directed )) + 
  scale_x_log10()+ 
  theme(legend.position = 'top')+
  ggrepel::geom_label_repel(aes(label = sources), size = 3)
  # theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) 
```

Distribution of evidence support for edges
```{r}
net.tbl %>% 
  mutate(directed = if_else(interaction %in% directed_edge_types, 'dir','undir') ) %>% 
  ggplot(aes(n_edge_evidence))+
  stat_ecdf(geom = 'line', aes(color = directed))+
  # geom_density(aes(fill = directed))+
  # geom_histogram(aes(fill = directed), position = position_dodge())+
  # scale_y_log10()+
  scale_x_log10()+
  geom_vline(xintercept = 2, lty = 2, lwd = .5)+
  labs(y = 'fraction of edges')
```
Distribution of evidence support for edges
```{r}
net.tbl %>% 
  mutate(directed = if_else(interaction %in% directed_edge_types, 'dir','undir') ) %>% 
  ggplot(aes(n_edge_types))+
  stat_ecdf(geom = 'line', aes(color = directed))+
  # geom_density(aes(fill = directed))+
  # geom_histogram(aes(fill = directed), position = position_dodge())+
  # scale_y_log10()+
  # scale_x_log10()+
  geom_vline(xintercept = 2, lty = 2, lwd = .5)+
  labs(y = 'fraction of edges')
```

Distribution of evidence support for edges
```{r}
net.tbl %>% 
  mutate(directed = if_else(interaction %in% directed_edge_types, 'dir','undir') ) %>% 
  ggplot(aes(n_source))+
  stat_ecdf(geom = 'line', aes(color = directed))+
  # geom_density(aes(fill = directed))+
  # geom_histogram(aes(fill = directed), position = position_dodge())+
  # scale_y_log10()+
  scale_x_log10()+
  geom_vline(xintercept = 2, lty = 2, lwd = .5)+
  labs(y = 'fraction of edges')
```

Distribution of evidence support for edges
```{r}
net.tbl %>% 
  mutate(directed = if_else(interaction %in% directed_edge_types, 'dir','undir') ) %>%
  filter(n_edge_evidence > 1
         | (n_edge_evidence == 1 & n_edge_types > 2 & n_source > 2)) %>% 
  ggplot(aes(n_edge))+
  # stat_ecdf(geom = 'line', aes(color = directed))+
  geom_histogram(color = 'grey20', fill = 'grey80')+
  
  # scale_x_log10()+
  # geom_vline(xintercept = 2, lty = 2, lwd = .5)+
  labs()
```

Distribution of evidence support for edges
```{r}
net.tbl %>% 
  # mutate(directed = if_else(interaction %in% directed_edge_types, 'dir','undir') ) %>% 
  ggplot(aes( n_edge_types, n_edge_evidence ))+
  geom_point()+
  geom_smooth(method = 'lm')+
  scale_y_log10()+
  # scale_x_log10()+
  # geom_vline(xintercept = 2, lty = 2, lwd = .5)+
  labs()
```

# EDGE: Pairwise partial correlations

Dropping this for the moment because:
1. the current pcor calculations would need to be recalculated on a tissue specific basis
2. the data are large, unwieldy, and of uncertain utility 

May return at a later time. 

<!-- ## ROSMAP -->
<!-- Load ROSMAP pairwise partial correlations -->
<!-- ```{r} -->
<!-- # st = Sys.time() -->
<!-- #  -->
<!-- # # download and pivot pcor table -->
<!-- # synLogin() -->
<!-- # rm.pcor <- read_csv(synGet('syn51061790')$path) %>%  -->
<!-- #   rename(gene1 = X1) %>%  -->
<!-- #   pivot_longer(cols = -gene1, names_to = 'gene2', values_to = 'pcor') %>%  -->
<!-- #   filter( gene1 != gene2 )  -->
<!-- #  -->
<!-- # cat('download: \n') -->
<!-- # Sys.time() - st -->
<!-- #  -->
<!-- # # get gene symbols corresponding to Ensembl IDs -->
<!-- # genes <- union(rm.pcor$gene1, rm.pcor$gene2) -->
<!-- # sym <- gprofiler2::gconvert( -->
<!-- #   genes,  -->
<!-- #   organism = 'hsapiens', -->
<!-- #   target = 'HGNC' -->
<!-- # ) %>%  -->
<!-- #   select( gene1 = input, gene2 = input, symbol1 = target, symbol2 = target) -->
<!-- #  -->
<!-- # cat('id conversion: \n') -->
<!-- # Sys.time() - st -->
<!-- #  -->
<!-- # # add symbols to table -->
<!-- # # remove genes without symbols (therefore not in NW) -->
<!-- # # & put genes in consistent order to reduce dataset size -->
<!-- # rm.pcor <-  -->
<!-- #   left_join( rm.pcor, sym %>% select(ends_with('1')), by = 'gene1') %>%  -->
<!-- #   left_join( .,       sym %>% select(ends_with('2')), by = 'gene2') %>%  -->
<!-- #   filter(!is.na(symbol1), !is.na(symbol2))  -->
<!-- # # %>%  -->
<!-- # #   mutate( -->
<!-- # #     T1=ifelse(symbol1 < symbol2, symbol1, symbol2), -->
<!-- # #     T2=ifelse(symbol1 < symbol2, symbol2, symbol1), -->
<!-- # #     edge = paste0(T1,':',T2) -->
<!-- # #   ) %>%  -->
<!-- # #   select(symbol1 = T1, symbol2 = T2, edge, pcor) %>% -->
<!-- # #   distinct() -->
<!-- #  -->
<!-- # cat('full process: \n') -->
<!-- # Sys.time() - st -->

<!-- rm.pcor = readRDS('data/rosmap_pcor.rds') -->
<!-- ``` -->

<!-- pcor distribution -->
<!-- ```{r} -->
<!-- rm.pcor %>%  -->
<!--   mutate(set = case_when(edge %in% e.attr$edge, 'PathCommonsNW','None')) %>%  -->
<!--   ggplot(aes( abs(pcor) )) + -->
<!--   # geom_histogram()+ -->
<!--   # scale_y_log10()+ -->
<!--   geom_density(aes(fill = set), alpha = .3)+ -->
<!--   theme_bw() -->
<!-- ``` -->

<!-- ```{r} -->
<!-- rm.pcor <- rm.pcor %>%  -->
<!--   filter(edge %in% e.attr$edge) -->
<!-- ``` -->

<!-- pcor distribution -->
<!-- ```{r} -->
<!-- rm.pcor %>%  -->
<!--   ggplot(aes(pcor)) + -->
<!--   geom_histogram()+ -->
<!--   scale_y_log10()+ -->
<!--   theme_bw() -->
<!-- ``` -->

<!-- pcor distribution -->
<!-- ```{r} -->
<!-- rm.pcor %>%  -->
<!--   mutate(set = if_else( edge %in% e.attr$edge[e.attr$n_evidence >= 2], '>= 2 PMID','< 2 PMID')) %>%  -->
<!--   ggplot(aes(pcor)) + -->
<!--   geom_histogram( aes(fill = set), position = 'dodge')+ -->
<!--   # scale_y_log10()+ -->
<!--   # geom_density(aes(fill = set), alpha = .3)+ -->
<!--   theme_bw() -->
<!-- ``` -->

<!-- ```{r} -->
<!-- rm.pcor %>%  -->
<!--   filter(  -->
<!--     abs(pcor) > mean(abs(pcor))+3*sd(abs(pcor)),  -->
<!--     edge %in% e.attr$edge[e.attr$n_evidence < 2] ) %>%  -->
<!--   ggplot(aes(pcor)) + -->
<!--   geom_histogram()+ -->
<!--   scale_y_log10()+ -->
<!--   # geom_density(aes(fill = set), alpha = .3)+ -->
<!--   theme_bw() -->

<!-- ``` -->

<!-- Classify pairs based on HPA expression and TREAT-AD DEG status -->
<!-- ```{r} -->
<!-- rm.pcor <- rm.pcor %>%  -->
<!--   mutate( -->
<!--     brain = case_when( -->
<!--       (gene1 %in% brain.genes.ensg & gene2 %in% brain.genes.ensg) ~ 'yes, both', -->
<!--       (gene1 %in% not.brain.ensg & gene2 %in% not.brain.ensg) ~ 'no, both', -->
<!--       (gene1 %in% brain.genes.ensg | gene2 %in% brain.genes.ensg) ~ 'yes, one', -->
<!--       (gene1 %in% not.brain.ensg | gene2 %in% not.brain.ensg) ~ 'no, one', -->
<!--       T ~ 'other' -->
<!--     ), -->
<!--     tad.deg = case_when( -->
<!--       (gene1 %in% tad.deg.ensg & gene2 %in% tad.deg.ensg) ~ 'yes, both', -->
<!--       (gene1 %in% tad.deg.ensg | gene2 %in% tad.deg.ensg) ~ 'yes, one', -->
<!--       !(gene1 %in% tad.deg.ensg & gene2 %in% tad.deg.ensg) ~ 'no, both', -->
<!--       T ~ 'other' -->
<!--     ) -->
<!--   )  -->
<!-- ``` -->


<!-- ```{r} -->
<!-- rm.pcor %>%  -->
<!--   ggplot( aes(pcor))+ -->
<!--   scale_y_log10()+ -->
<!--   # geom_density() -->
<!--   geom_histogram(aes(fill = brain), position = 'dodge') -->
<!-- ``` -->


<!-- ```{r} -->
<!-- rm.pcor %>%  -->
<!--   ggplot( aes( abs(pcor), fill = brain) )+ -->
<!--   scale_y_log10()+ -->
<!--   # geom_density(aes(color = brain), alpha = 0.1 ) -->
<!--   geom_histogram(aes(fill = brain), position = 'dodge') -->
<!-- ``` -->

<!-- ```{r} -->
<!-- rm.pcor %>%  -->
<!--   ggplot( aes( abs(pcor), fill = tad.deg))+ -->
<!--   scale_y_log10()+ -->
<!--   # geom_density(aes(color = tad.deg), alpha = 0.1 ) -->
<!--   geom_histogram(aes(fill = brain), position = 'dodge') -->
<!-- ``` -->

<!-- ```{r fig.width=8, fig.height=4} -->
<!-- x = rm.pcor %>%  -->
<!--      filter(gene1 %in% setdiff(brain.genes.ensg, not.brain.ensg)) %>%  -->
<!--      group_by(gene1) %>%  -->
<!--      summarise( -->
<!--          mean_bg = max((pcor[gene2 %in% setdiff(brain.genes.ensg, not.brain.ensg)]), na.rm = T), -->
<!--          mean_nbg = max((pcor[gene2 %in% setdiff(not.brain.ensg, brain.genes.ensg)]), na.rm = T) -->
<!--      )  -->
<!-- y = rm.pcor %>%  -->
<!--      filter(gene1 %in% setdiff(not.brain.ensg, brain.genes.ensg)) %>%  -->
<!--      group_by(gene1) %>%  -->
<!--      summarise( -->
<!--          mean_bg = max((pcor[gene2 %in% setdiff(brain.genes.ensg, not.brain.ensg)]), na.rm = T), -->
<!--          mean_nbg = max((pcor[gene2 %in% setdiff(not.brain.ensg, brain.genes.ensg)]), na.rm = T) -->
<!--      ) -->

<!-- cowplot::plot_grid(  -->
<!--     ggplot(x, aes(mean_bg, mean_nbg)) +  -->
<!--         geom_abline(intercept = 0, slope = 1, lty = 2, lwd = .5)+ -->
<!--         geom_smooth(method = 'lm', lwd = .5, color = 'grey20')+ -->
<!--         # coord_cartesian(xlim = c(0.05,0.15), ylim = c(0.05,0.15))+ -->
<!--       geom_point( alpha = .3 )+ -->
<!--         labs(title = 'brain genes', x = 'max  pcor\nbrain genes', y = 'max  pcor\nnon-brain genes'), -->
<!--     ggplot(y, aes(mean_bg, mean_nbg)) +  -->
<!--         geom_abline(intercept = 0, slope = 1, lty = 2, lwd = .5)+ -->
<!--         geom_smooth(method = 'lm', lwd = .5, color = 'grey20')+ -->
<!--         # coord_cartesian(xlim = c(0.05,0.15), ylim = c(0.05,0.15))+ -->
<!--       geom_point( alpha = .3 )+ -->
<!--         labs(title = 'non brain genes', x = 'max  pcor\nbrain genes', y = 'max  pcor\nnon-brain genes') -->
<!-- ) -->
<!-- ``` -->

<!-- ## Mayo -->

<!-- Load Mayo pairwise partial correlations -->
<!-- ```{r} -->
<!-- st = Sys.time() -->

<!-- # download and pivot pcor table -->
<!-- synLogin() -->
<!-- my.pcor <- read_csv(synGet('syn51061614')$path) %>%  -->
<!--   rename(gene1 = X1) %>%  -->
<!--   pivot_longer(cols = -gene1, names_to = 'gene2', values_to = 'pcor') %>%  -->
<!--   filter( gene1 != gene2 )  -->

<!-- cat('download: \n') -->
<!-- Sys.time() - st -->

<!-- # get gene symbols corresponding to Ensembl IDs -->
<!-- genes <- union(my.pcor$gene1, my.pcor$gene2) -->
<!-- sym <- gprofiler2::gconvert( -->
<!--   genes,  -->
<!--   organism = 'hsapiens', -->
<!--   target = 'HGNC' -->
<!-- ) %>%  -->
<!--   select( gene1 = input, gene2 = input, symbol1 = target, symbol2 = target) -->

<!-- cat('id conversion: \n') -->
<!-- Sys.time() - st -->

<!-- # add symbols to table -->
<!-- # remove genes without symbols (therefore not in NW) -->
<!-- # & put genes in consistent order to reduce dataset size -->
<!-- my.pcor <-  -->
<!--   left_join( my.pcor, sym %>% select(ends_with('1')), by = 'gene1') %>%  -->
<!--   left_join( .,       sym %>% select(ends_with('2')), by = 'gene2') %>%  -->
<!--   filter(!is.na(symbol1), !is.na(symbol2)) %>%  -->
<!--   mutate( -->
<!--     T1=ifelse(symbol1 < symbol2, symbol1, symbol2), -->
<!--     T2=ifelse(symbol1 < symbol2, symbol2, symbol1), -->
<!--     edge = paste0(T1,':',T2) -->
<!--   ) %>%  -->
<!--   select(symbol1 = T1, symbol2 = T2, edge, pcor) %>% -->
<!--   distinct() -->

<!-- cat('full process: \n') -->
<!-- Sys.time() - st -->


<!-- ``` -->

<!-- ## MSSM -->

<!-- Load Sinai pairwise partial correlations -->
<!-- ```{r} -->
<!-- st = Sys.time() -->

<!-- # download and pivot pcor table -->
<!-- synLogin() -->
<!-- ms.pcor <- read_csv(synGet('syn51061324')$path) %>%  -->
<!--   rename(gene1 = X1) %>%  -->
<!--   pivot_longer(cols = -gene1, names_to = 'gene2', values_to = 'pcor') %>%  -->
<!--   filter( gene1 != gene2 )  -->

<!-- cat('download: \n') -->
<!-- Sys.time() - st -->

<!-- # get gene symbols corresponding to Ensembl IDs -->
<!-- genes <- union(ms.pcor$gene1, ms.pcor$gene2) -->
<!-- sym <- gprofiler2::gconvert( -->
<!--   genes,  -->
<!--   organism = 'hsapiens', -->
<!--   target = 'HGNC' -->
<!-- ) %>%  -->
<!--   select( gene1 = input, gene2 = input, symbol1 = target, symbol2 = target) -->

<!-- cat('id conversion: \n') -->
<!-- Sys.time() - st -->

<!-- # add symbols to table -->
<!-- # remove genes without symbols (therefore not in NW) -->
<!-- # & put genes in consistent order to reduce dataset size -->
<!-- ms.pcor <-  -->
<!--   left_join( ms.pcor, sym %>% select(ends_with('1')), by = 'gene1') %>%  -->
<!--   left_join( .,       sym %>% select(ends_with('2')), by = 'gene2') %>%  -->
<!--   filter(!is.na(symbol1), !is.na(symbol2)) %>%  -->
<!--   mutate( -->
<!--     T1=ifelse(symbol1 < symbol2, symbol1, symbol2), -->
<!--     T2=ifelse(symbol1 < symbol2, symbol2, symbol1), -->
<!--     edge = paste0(T1,':',T2) -->
<!--   ) %>%  -->
<!--   select(symbol1 = T1, symbol2 = T2, edge, pcor) %>% -->
<!--   distinct() -->

<!-- cat('full process: \n') -->
<!-- Sys.time() - st -->


<!-- ``` -->

# EDGE: overall

<!-- ```{r} -->
<!-- tot.edge = e.attr$edge -->
<!-- filt.nodes = intersect(exp.filt.genes, fxn.filt.genes) %>%  -->
<!--                        union(., tad.deg) %>%  -->
<!--                        union(., brain.genes) %>%  -->
<!--                        intersect(.,v.attr$name)  -->

<!-- grid::grid.newpage() -->
<!-- grid::grid.draw( -->
<!--   VennDiagram::venn.diagram( -->
<!--         x = list( -->
<!--           PathCommons_NW = e.attr$edge %>% .[!is.na(.)],  -->
<!--           LitSupport = , -->
<!--           ROSMAP_pcor = , -->
<!--           Mayo_pcor = , -->
<!--           MSSM_pcor =  -->
<!--         ), -->
<!--         filename = NULL, -->
<!--         force.unique = T, -->
<!--         lty = 0, alpha = .3 ,  -->
<!--         fill = c('light blue','yellow', 'green','purple'), -->

<!--         sub = paste0('# Pathway Commons nodes: ', length(tot.nodes), -->
<!--                      '\n# filtered nodes: ', length(filt.nodes),  -->
<!--                      ' (', signif( 100*length(filt.nodes)/length(tot.nodes), digits = 4), '%)' ), -->

<!--         cat.cex = .8, -->
<!--         ext.pos = 180, -->
<!--         ext.dist = -.1 -->
<!--         ) -->
<!-- ) -->

<!-- ``` -->

# Summary
```{r}

# specify gene lists
hpa.brain <- tissue.array %>% 
  filter(
    Tissue %in% brain.tissues, 
    Level %in% c('Low','Medium','High','Ascending','Descending'),
    Reliability %in% c('Enhanced','Supported','Approved') ) %>% 
  pull(Gene.name) %>% unique()

tad.deg <- scores %>% 
  filter(isScored_omics == 'Y', OmicsScore > 0) %>% 
  pull(GeneName) %>% unique()

seaad.expr <- seaad %>% 
  filter( upperQ_exp >= -2.5 * fxn_exp + 2.3 ) %>%
  pull(gene) %>% unique()

brain.genes <- union(hpa.brain, tad.deg) %>% union(., seaad.expr)

# pull NW stats based on filter
nw.stats <- tibble(  
  
  dir = c(
    'undirected'
    ,'directed'
    
    ,'undirected'
    ,'directed'
    
    ,'undirected'
    ,'directed'
    
    ,'undirected'
    ,'directed'
    
    ,'undirected'
    ,'directed'
    
    ,'undirected'
    ,'directed'
    
    ,'undirected'
    ,'directed'
    
    ), 
  
  filt = c(
    'none'
    ,'none'
    
    ,'edge_evidence > 1'
    ,'edge_evidence > 1'
    
    ,'HPA_brain'
    ,'HPA_brain'
    
    ,'omics_detect'
    ,'omics_detect'
    
    ,'seaAD_detect'
    ,'seaAD_detect'
    
    ,'all_expr'
    ,'all_expr'

    ,'expr+evidence'
    ,'expr+evidence'

        
    ),
  
  nV = c( 
    net.tbl %>% 
      graph_from_data_frame %>% V %>% length
    , net.tbl %>% 
      filter(interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% V %>% length

    , net.tbl %>% 
      filter(n_edge_evidence > 1) %>% 
      graph_from_data_frame %>% V %>% length
    , net.tbl %>% 
      filter(n_edge_evidence > 1, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% V %>% length

    , net.tbl %>% 
      filter(from %in% hpa.brain & to %in% hpa.brain) %>% 
      graph_from_data_frame %>% V %>% length
    , net.tbl %>% 
      filter(from %in% hpa.brain & to %in% hpa.brain, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% V %>% length
    
    , net.tbl %>% 
      filter(from %in% tad.deg & to %in% tad.deg) %>% 
      graph_from_data_frame %>% V %>% length
    , net.tbl %>% 
      filter(from %in% tad.deg & to %in% tad.deg, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% V %>% length
    
    , net.tbl %>% 
      filter(from %in% seaad.expr & to %in% seaad.expr) %>% 
      graph_from_data_frame %>% V %>% length
    , net.tbl %>% 
      filter(from %in% seaad.expr & to %in% seaad.expr, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% V %>% length
    
    , net.tbl %>% 
      filter(from %in% brain.genes & to %in% brain.genes) %>% 
      graph_from_data_frame %>% V %>% length
    , net.tbl %>% 
      filter(from %in% brain.genes & to %in% brain.genes, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% V %>% length
    
    , net.tbl %>% 
      filter(n_edge_evidence > 1,
             from %in% brain.genes & to %in% brain.genes) %>% 
      graph_from_data_frame %>% V %>% length
    , net.tbl %>% 
      filter(n_edge_evidence > 1,
             from %in% brain.genes & to %in% brain.genes, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% V %>% length
    
    ),
  
  nE = c( 
    net.tbl %>% 
      graph_from_data_frame %>% E %>% length
    , net.tbl %>% 
      filter(interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% E %>% length
    
    , net.tbl %>% 
      filter(n_edge_evidence > 1) %>% 
      graph_from_data_frame %>% E %>% length
    , net.tbl %>% 
      filter(n_edge_evidence > 1, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% E %>% length
    
    , net.tbl %>% 
      filter(from %in% hpa.brain & to %in% hpa.brain) %>% 
      graph_from_data_frame %>% E %>% length
    , net.tbl %>% 
      filter(from %in% hpa.brain & to %in% hpa.brain, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% E %>% length
    
    , net.tbl %>% 
      filter(from %in% tad.deg & to %in% tad.deg) %>% 
      graph_from_data_frame %>% E %>% length
    , net.tbl %>% 
      filter(from %in% tad.deg & to %in% tad.deg, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% E %>% length
    
    , net.tbl %>% 
      filter(from %in% seaad.expr & to %in% seaad.expr) %>% 
      graph_from_data_frame %>% E %>% length
    , net.tbl %>% 
      filter(from %in% seaad.expr & to %in% seaad.expr, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% E %>% length
    
    , net.tbl %>% 
      filter(from %in% brain.genes & to %in% brain.genes) %>% 
      graph_from_data_frame %>% E %>% length
    , net.tbl %>% 
      filter(from %in% brain.genes & to %in% brain.genes, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% E %>% length
    
    , net.tbl %>% 
      filter(n_edge_evidence > 1,
             from %in% brain.genes & to %in% brain.genes) %>% 
      graph_from_data_frame %>% E %>% length
    , net.tbl %>% 
      filter(n_edge_evidence > 1,
             from %in% brain.genes & to %in% brain.genes, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% E %>% length
    
    ),
  
  avg_path_length = c(
    net.tbl %>% 
      graph_from_data_frame %>% average.path.length()
    , net.tbl %>% 
      filter(interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% average.path.length(directed = T)
    
    , net.tbl %>% 
      filter(n_edge_evidence > 1) %>% 
      graph_from_data_frame %>% average.path.length()
    , net.tbl %>% 
      filter(n_edge_evidence > 1, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% average.path.length(directed = T)
    
    , net.tbl %>% 
      filter(from %in% hpa.brain & to %in% hpa.brain) %>% 
      graph_from_data_frame %>% average.path.length()
    , net.tbl %>% 
      filter(from %in% hpa.brain & to %in% hpa.brain, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% average.path.length(directed = T)
    
    , net.tbl %>% 
      filter(from %in% tad.deg & to %in% tad.deg) %>% 
      graph_from_data_frame %>% average.path.length()
    , net.tbl %>% 
      filter(from %in% tad.deg & to %in% tad.deg, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% average.path.length(directed = T)
    
    , net.tbl %>% 
      filter(from %in% seaad.expr & to %in% seaad.expr) %>% 
      graph_from_data_frame %>% average.path.length()
    , net.tbl %>% 
      filter(from %in% seaad.expr & to %in% seaad.expr, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% average.path.length(directed = T)

    , net.tbl %>% 
      filter(from %in% brain.genes & to %in% brain.genes) %>% 
      graph_from_data_frame %>% average.path.length()
    , net.tbl %>% 
      filter(from %in% brain.genes & to %in% brain.genes, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% average.path.length(directed = T)
    
    , net.tbl %>% 
      filter(n_edge_evidence > 1,
             from %in% brain.genes & to %in% brain.genes) %>% 
      graph_from_data_frame %>% average.path.length()
    , net.tbl %>% 
      filter(n_edge_evidence > 1,
             from %in% brain.genes & to %in% brain.genes, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% average.path.length(directed = T)    
  ),
  
  assortativity_coef = c(
    net.tbl %>% 
      graph_from_data_frame %>% assortativity(., types1 = V(.))
    , net.tbl %>% 
      filter(interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% assortativity(., types1 = V(.))
    
    , net.tbl %>% 
      filter(n_edge_evidence > 1) %>% 
      graph_from_data_frame %>% assortativity(., types1 = V(.))
    , net.tbl %>% 
      filter(n_edge_evidence > 1, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% assortativity(., types1 = V(.))
    
    , net.tbl %>% 
      filter(from %in% hpa.brain & to %in% hpa.brain) %>% 
      graph_from_data_frame %>% assortativity(., types1 = V(.))
    , net.tbl %>% 
      filter(from %in% hpa.brain & to %in% hpa.brain, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% assortativity(., types1 = V(.))
    
    , net.tbl %>% 
      filter(from %in% tad.deg & to %in% tad.deg) %>% 
      graph_from_data_frame %>% assortativity(., types1 = V(.))
    , net.tbl %>% 
      filter(from %in% tad.deg & to %in% tad.deg, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% assortativity(., types1 = V(.))
    
    , net.tbl %>% 
      filter(from %in% seaad.expr & to %in% seaad.expr) %>% 
      graph_from_data_frame(directed=T) %>% assortativity(., types1 = V(.))
    , net.tbl %>% 
      filter(from %in% seaad.expr & to %in% seaad.expr, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% assortativity(., types1 = V(.))
    
    
    , net.tbl %>% 
      filter(from %in% brain.genes & to %in% brain.genes) %>% 
      graph_from_data_frame %>% assortativity(., types1 = V(.))
    , net.tbl %>% 
      filter(from %in% brain.genes & to %in% brain.genes, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame %>% assortativity(., types1 = V(.))
    
    
    , net.tbl %>% 
      filter(n_edge_evidence > 1,
             from %in% brain.genes & to %in% brain.genes) %>% 
      graph_from_data_frame %>% assortativity(., types1 = V(.))
    , net.tbl %>% 
      filter(n_edge_evidence > 1,
             from %in% brain.genes & to %in% brain.genes, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame %>% assortativity(., types1 = V(.))
  ),
  
  connected_components = c(
    net.tbl %>% 
      graph_from_data_frame %>% no.clusters()
    , net.tbl %>% 
      filter(interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% no.clusters()
    
    , net.tbl %>% 
      filter(n_edge_evidence > 1) %>% 
      graph_from_data_frame %>% no.clusters()
    , net.tbl %>% 
      filter(n_edge_evidence > 1, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% no.clusters()
    
    , net.tbl %>% 
      filter(from %in% hpa.brain & to %in% hpa.brain) %>% 
      graph_from_data_frame %>% no.clusters()
    , net.tbl %>% 
      filter(from %in% hpa.brain & to %in% hpa.brain, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% no.clusters()
    
    , net.tbl %>% 
      filter(from %in% tad.deg & to %in% tad.deg) %>% 
      graph_from_data_frame %>% no.clusters()
    , net.tbl %>% 
      filter(from %in% tad.deg & to %in% tad.deg, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% no.clusters()
    
    , net.tbl %>% 
      filter(from %in% seaad.expr & to %in% seaad.expr) %>% 
      graph_from_data_frame %>% no.clusters()
    , net.tbl %>% 
      filter(from %in% seaad.expr & to %in% seaad.expr, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% no.clusters()
    
    , net.tbl %>% 
      filter(from %in% brain.genes & to %in% brain.genes) %>% 
      graph_from_data_frame %>% no.clusters()
    , net.tbl %>% 
      filter(from %in% brain.genes & to %in% brain.genes, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% no.clusters()
    
    , net.tbl %>% 
      filter(n_edge_evidence > 1,
             from %in% brain.genes & to %in% brain.genes) %>% 
      graph_from_data_frame %>% no.clusters()
    , net.tbl %>% 
      filter(n_edge_evidence > 1,
             from %in% brain.genes & to %in% brain.genes, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% no.clusters()
  )
  
)

```

```{r, fig.width=10, fig.height=8}
nw.stats %>% 
  pivot_longer(cols = c(nV,nE,avg_path_length,assortativity_coef,connected_components), 
               names_to = 'prop', values_to = 'val') %>% 
  mutate(prop = factor(prop, levels = c('nV','nE', 'avg_path_length','assortativity_coef','connected_components'))
         , dir = factor(dir, levels = c('undirected','directed'))
         , filt = factor(filt, levels = c('none','edge_evidence > 1','HPA_brain','omics_detect','seaAD_detect', 
                                          'all_expr','expr+evidence'))
         ) %>% 
  ggplot(aes(filt, val, fill = dir)) +
  geom_bar(stat = 'identity', position = 'dodge')+
  theme(legend.position = 'top',
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))+
  facet_wrap(~prop, scales = 'free_y', ncol = 2)
```
# Session
```{r}
save.image(
  paste0(
    Sys.Date() %>% str_replace_all('-','_'),
    '_',
    'base_nw_filtering.Rdata')
  )
sessionInfo()
```

