---
title: "Network Filtering Analysis"
author: "Greg Cary"
date: "`r Sys.Date()`"
output: 
  html_document: 
    fig_width: 5
    fig_height: 4
  html_notebook:
    code_folding: hide
    theme: spacelab
    css: style.css
    toc: true
    toc_float: true
---

```{r setup}
library(synapser)
# library(paxtoolsr)
# library(org.Hs.eg.db)
# library(clusterProfiler)
# library(HotNetvieweR)
library(igraph)
library(tidygraph)
library(tidyverse)

source(paste0(here::here(),'/../biodom_tally.R'))
source(paste0(here::here(),'/../biodom_enr.R'))
source(paste0(here::here(),'/../biodom_enr_plots.R'))

theme_set(theme_bw())
```

Grab relevant data from synapse, including:  
1) Target Risk Scores ([syn25575156](https://www.synapse.org/#!Synapse:syn25575156){target="_blank"}) and Omics Scores ([syn22758536](https://www.synapse.org/#!Synapse:syn22758536){target="_blank"})  
2) Biodomain Definitions ([syn25428992](https://www.synapse.org/#!Synapse:syn25428992){target="_blank"})  
3) Pathway Commons Full Graph, v12 ([syn51080932](https://www.synapse.org/#!Synapse:syn51080932){target="_blank"})  
4) Human Protein Atlas tissue immunohistochemistry micro array data ([syn51074598](https://www.synapse.org/#!Synapse:syn51074598){target="_blank"})  
5) RNA Brain GTEx ([syn51074639](https://www.synapse.org/#!Synapse:syn51074639){target="_blank"})  
6) AMP-AD cohort pairwise partial correlations ([ROSMAP](https://www.synapse.org/#!Synapse:syn51061790){target="_blank"}, [Mayo](https://www.synapse.org/#!Synapse:syn51061614){target="_blank"}, [MSBB](https://www.synapse.org/#!Synapse:syn51061324){target="_blank"}); these are quite large! (> 6 GB), wait to load until performing this analysis  
7) SEA-AD single cell data ([syn51080312](https://www.synapse.org/#!Synapse:syn51080312){target="_blank"}); this is a large file (> 2 GB), wait to load until performing this analysis  
```{r message=FALSE, warning=FALSE}
synLogin()

# target risk scores
scores <- read_csv(synTableQuery('select * from syn25575156', includeRowIdAndRowVersion = F)$filepath)
omics <- read_csv(synTableQuery('select * from syn22758536',  includeRowIdAndRowVersion = F)$filepath)

# biological domain annotations
biodom <- full_join(
  # biodomains
  readRDS(synGet('syn25428992')$path),
  # domain labels
  read_csv(synGet('syn26856828')$path),
  by = c('Biodomain'='domain')
) %>%
  mutate(Biodomain = case_when(Biodomain == 'none' ~ NA_character_, T ~ Biodomain))

# pathway commons graph
net <- igraph::read_graph(synGet('syn51080932')$path, format = 'graphml') 

# Human protein atlas info
tissue.array <- read_csv(synGet('syn51074598')$path)
brain.gtex <- read_csv(synGet('syn51074639')$path)
```

# Pathway Commons Network

Extract the core NW tables
```{r message=FALSE}
net.tbl <- igraph::as_data_frame(net)

v.attr <- tibble( na = vertex.attributes(net) ) %>%
  t() %>% as_tibble(rownames = NA, .name_repair = 'unique') %>% unnest(everything()) %>%
  rename_with(., ~names(vertex.attributes(net)), everything())

e.attr <- tibble( ea = edge.attributes(net) ) %>% 
  t() %>% as_tibble(rownames = NA, .name_repair = 'unique') %>% unnest(everything()) %>% 
  rename_with(., ~names(edge.attributes(net)), everything())
```


Specify the directed-edge types to filter the Pathway Commons graph  
```{r}
directed_edge_types = c("catalysis-precedes",
                        "controls-expression-of",
                        "controls-phosphorylation-of",
                        "controls-state-change-of",
                        "controls-transport-of"
                        )

# dir.net <- graph_from_data_frame(d = net.tbl %>% filter(interaction %in% directed_edge_types), directed = T)
```

How many edges from each source?  
```{r warning=FALSE}
bind_cols(
    sources = str_split(net.tbl$sources,',') %>% unlist %>% unique, 
    n_edge = map_dbl( 
        str_split(net.tbl$sources,',') %>% unlist %>% unique, 
        ~ net.tbl %>% filter(grepl(.x, sources)) %>% nrow() ),
    any_directed = map_lgl(
        str_split(net.tbl$sources,',') %>% unlist %>% unique, 
        ~ net.tbl %>% 
            mutate(directed = if_else(interaction %in% directed_edge_types, 'dir','undir') ) %>% 
            filter(grepl(.x, sources)) %>% pull(directed) %>% any(. == 'dir')
    )
) %>% 
  mutate(any_directed = if_else(is.na(any_directed), FALSE, TRUE),
         any_directed = factor(any_directed, levels=c('TRUE','FALSE'))) %>%
  arrange(desc(n_edge)) %>% mutate(sources = fct_relevel(sources, sources)) %>%
  ggplot(aes(sources, n_edge)) + geom_bar(stat = 'identity', aes(fill = any_directed)) +
  # scale_y_log10()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)
        , legend.position = 'top')
```

Which edge sources are (generally) well supported?  
```{r warning=FALSE}
bind_cols(
    sources = str_split(net.tbl$sources,',') %>% unlist %>% unique, 
    n_edge = map_dbl( 
      str_split(net.tbl$sources,',') %>% unlist %>% unique, 
      ~ net.tbl %>% filter(grepl(.x, sources)) %>% nrow() )
    , median_evidence_per_edge = map_dbl( 
      str_split(net.tbl$sources,',') %>% unlist %>% unique, 
      ~ net.tbl %>% filter(grepl(.x, sources)) %>% pull(n_edge_evidence) %>% median() )
    , any_directed = map_lgl(
        str_split(net.tbl$sources,',') %>% unlist %>% unique, 
        ~ net.tbl %>% 
            mutate(directed = if_else(interaction %in% directed_edge_types, 'dir','undir') ) %>% 
            filter(grepl(.x, sources)) %>% pull(directed) %>% any(. == 'dir') )
) %>% 
  mutate(any_directed = if_else(is.na(any_directed), FALSE, TRUE),
         any_directed = factor(any_directed, levels=c('TRUE','FALSE'))) %>%
  arrange(desc(n_edge)) %>% mutate(sources = fct_relevel(sources, sources)) %>% 
  ggplot(aes(n_edge, median_evidence_per_edge)) +
  geom_point( aes(color = any_directed )) + 
  scale_x_log10()+ 
  theme(legend.position = 'top')+
  ggrepel::geom_label_repel(aes(label = sources), size = 3)
  # theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) 
```

Distribution of evidence support for edges
```{r}
net.tbl %>% 
  mutate(directed = if_else(interaction %in% directed_edge_types, 'dir','undir') ) %>% 
  ggplot(aes(n_edge_evidence))+
  stat_ecdf(geom = 'line', aes(color = directed))+
  # geom_density(aes(fill = directed))+
  # geom_histogram(aes(fill = directed), position = position_dodge())+
  # scale_y_log10()+
  scale_x_log10()+
  geom_vline(xintercept = 2, lty = 2, lwd = .5)+
  labs(y = 'fraction of edges')
```

Distribution of evidence support for edges
```{r}
net.tbl %>% 
  mutate(directed = if_else(interaction %in% directed_edge_types, 'dir','undir') ) %>% 
  ggplot(aes(n_source))+
  stat_ecdf(geom = 'line', aes(color = directed))+
  # geom_density(aes(fill = directed))+
  # geom_histogram(aes(fill = directed), position = position_dodge())+
  # scale_y_log10()+
  scale_x_log10()+
  geom_vline(xintercept = 2, lty = 2, lwd = .5)+
  labs(y = 'fraction of edges')
```

Distribution of evidence support for edges
```{r}
net.tbl %>% 
  # mutate(directed = if_else(interaction %in% directed_edge_types, 'dir','undir') ) %>% 
  ggplot(aes( n_edge_types, n_edge_evidence ))+
  geom_point()+
  geom_smooth(method = 'lm')+
  scale_y_log10()+
  # scale_x_log10()+
  # geom_vline(xintercept = 2, lty = 2, lwd = .5)+
  labs()
```


# Human Protein Atlas 

Specify brain tissue types
```{r}
brain.tissues <- c(
 "caudate", "cerebellum", "cerebral cortex", "hippocampus", 
 "hypothalamus", "pituitary gland", "dorsal raphe", 
 "choroid plexus", "substantia nigra"
)

brain.genes <- tissue.array %>% filter(
  Tissue %in% brain.tissues, 
  Level %in% c('Low','Medium','High','Ascending','Descending'),
  Reliability %in% c('Enhanced','Supported','Approved')
) %>% pull(Gene.name) %>% unique()

not.brain <- tissue.array %>% filter(
  Tissue %in% brain.tissues,
  Level %in% c('Not detected'),
  Reliability %in% c('Enhanced','Supported','Approved')
) %>% pull(Gene.name) %>% unique()

```


```{r}
# also "brain genes":
# scores %>% filter(isScored_omics == 'Y', OmicsScore > 0) %>% pull(GeneName) %>% unique()

brain.gtex %>% 
  mutate(hpa = case_when(Gene.name %in% brain.genes ~ 
                           paste0('brain (n = ', length(intersect(Gene.name, brain.genes)),' genes)'),
                         Gene.name %in% not.brain ~ 
                           paste0('not brain (n = ', length(intersect(Gene.name,not.brain)),' genes)'),
                         T ~ NA_character_)) %>% 
  filter(!is.na(hpa)) %>% 
  ggplot(aes( log10(nTPM), fill = hpa))+
  geom_density(aes(color = hpa), alpha = .1)+
  # geom_histogram(position = 'dodge')+
  # scale_y_log10()+
  scale_fill_discrete('')+scale_color_discrete('')+
  theme(legend.position = 'top')
```

```{r}
# also "brain genes":
tad.deg <- scores %>% filter(isScored_omics == 'Y', OmicsScore > 0) %>% pull(GeneName) %>% unique()

brain.gtex %>% 
  mutate(hpa = case_when(Gene.name %in% tad.deg ~ paste0('TAD DEG (n = ', length(intersect(Gene.name,tad.deg)),' genes)'),
                         T ~ paste0('not TAD DEG (n = ', length(setdiff(Gene.name, tad.deg)),' genes)'),
                         )) %>% 
  filter(!is.na(hpa)) %>% 
  ggplot(aes( log10(nTPM), fill = hpa))+
  geom_density(aes(color = hpa), alpha = .1)+
  # geom_histogram(position = 'dodge')+
  # scale_y_log10()+
  scale_fill_discrete('')+scale_color_discrete('')+
  theme(legend.position = 'top')
```

```{r}
# also "brain genes":
tad.deg <- scores %>% filter(isScored_omics == 'Y', OmicsScore > 0) %>% pull(GeneName) %>% unique()

brain.gtex %>% 
  mutate(
  hpa = case_when(
    Gene.name %in% brain.genes ~ 
      paste0('HPA brain (n = ', length(intersect(Gene.name, brain.genes)),' genes)'),
    Gene.name %in% tad.deg ~ paste0('TAD DEG (n = ', length(intersect(Gene.name,tad.deg)),' genes)'),
    Gene.name %in% not.brain ~ paste0('HPA not brain (n = ', length(intersect(Gene.name,not.brain)),' genes)'),
    T ~ paste0('other (n = ', length(setdiff(Gene.name, union(union(brain.genes, tad.deg), not.brain))) ,' genes)')
    )) %>% 
  ggplot(aes( log10(nTPM), fill = hpa))+
  geom_density(aes(color = hpa), alpha = .1)+
  # geom_histogram(position = 'dodge')+
  # scale_y_log10()+
  scale_fill_discrete('')+scale_color_discrete('')+
  guides(fill = guide_legend(nrow=2))+
  theme(legend.position = 'top')
```

# SEA-AD single cell data
```{r}
seaad <- read_csv(synGet('syn51080312')$path, guess_max = 2e5)
```
```{r}
# also "brain genes":
# scores %>% filter(isScored_omics == 'Y', OmicsScore > 0) %>% pull(GeneName) %>% unique()

seaad %>% 
  # filter(is.na(group)) %>% 
  mutate(
    hpa = case_when(
      gene %in% brain.genes ~ paste0('HPA brain (n = ', length(intersect(gene, brain.genes)),' genes)'),
      gene %in% tad.deg ~ paste0('TAD DEG (n = ', length(intersect(gene,tad.deg)),' genes)'),
      gene %in% not.brain ~ paste0('HPA not brain (n = ', length(intersect(gene,not.brain)),' genes)'),
      T ~ paste0('other (n = ', length(unique(setdiff(gene, union(union(brain.genes, tad.deg), not.brain)))) ,' genes)')
      )
  ) %>% 
  filter(!is.na(hpa)) %>% 
  ggplot(aes( log10(mean), fill = hpa))+
  geom_density(aes(color = hpa), alpha = .1)+
  # geom_histogram(position = 'dodge')+
  # scale_y_log10()+
  scale_fill_discrete('')+scale_color_discrete('')+
  guides(fill = guide_legend(nrow=2))+
  theme(legend.position = 'top')
```

```{r}

seaad$gene %>% unique() %>% length() %>% print()

```

# Pairwise partial correlations

Specify Enesmbl IDs of brain gene lists
```{r}
brain.genes.ensg <- 
  tissue.array %>% filter(
    Tissue %in% brain.tissues, 
    Level %in% c('Low','Medium','High','Ascending','Descending'),
    Reliability %in% c('Enhanced','Supported','Approved')) %>% 
    pull(Gene) %>% unique()

not.brain.ensg <- tissue.array %>% filter(
  Tissue %in% brain.tissues,
  Level %in% c('Not detected'),
  Reliability %in% c('Enhanced','Supported','Approved')
) %>% pull(Gene) %>% unique()

tad.deg.ensg <- scores %>% filter(isScored_omics == 'Y', OmicsScore > 0) %>% pull(ENSG) %>% unique()
```

Load ROSMAP pairwise partial correlations
```{r}
rm.pcor <- read_csv(synGet('syn51061790')$path) %>% 
  rename(gene1 = X1) %>% 
  pivot_longer(cols = -gene1, names_to = 'gene2', values_to = 'pcor') %>% 
  filter(pcor < 1) 
```

Classify pairs based on HPA expression and TREAT-AD DEG status
```{r}
rm.pcor <- rm.pcor %>% 
  mutate(
    brain = case_when(
      (gene1 %in% brain.genes.ensg & gene2 %in% brain.genes.ensg) ~ 'yes, both',
      (gene1 %in% not.brain.ensg & gene2 %in% not.brain.ensg) ~ 'no, both',
      (gene1 %in% brain.genes.ensg | gene2 %in% brain.genes.ensg) ~ 'yes, one',
      (gene1 %in% not.brain.ensg | gene2 %in% not.brain.ensg) ~ 'no, one',
      T ~ 'other'
    ),
    tad.deg = case_when(
      (gene1 %in% tad.deg.ensg & gene2 %in% tad.deg.ensg) ~ 'yes, both',
      (gene1 %in% tad.deg.ensg | gene2 %in% tad.deg.ensg) ~ 'yes, one',
      !(gene1 %in% tad.deg.ensg & gene2 %in% tad.deg.ensg) ~ 'no, both',
      T ~ 'other'
    )
  ) 
```


```{r}
rm.pcor %>% 
  ggplot( aes(pcor))+
  scale_y_log10()+
  # geom_density()
  geom_histogram(aes(fill = brain), position = 'dodge')
```


```{r}
rm.pcor %>% 
  ggplot( aes( abs(pcor), fill = brain) )+
  scale_y_log10()+
  # geom_density(aes(color = brain), alpha = 0.1 )
  geom_histogram(aes(fill = brain), position = 'dodge')
```

```{r}
rm.pcor %>% 
  ggplot( aes( abs(pcor), fill = tad.deg))+
  scale_y_log10()+
  # geom_density(aes(color = tad.deg), alpha = 0.1 )
  geom_histogram(aes(fill = brain), position = 'dodge')
```

```{r fig.width=8, fig.height=4}
x = rm.pcor %>% 
     filter(gene1 %in% setdiff(brain.genes.ensg, not.brain.ensg)) %>% 
     group_by(gene1) %>% 
     summarise(
         mean_bg = max((pcor[gene2 %in% setdiff(brain.genes.ensg, not.brain.ensg)]), na.rm = T),
         mean_nbg = max((pcor[gene2 %in% setdiff(not.brain.ensg, brain.genes.ensg)]), na.rm = T)
     ) 
y = rm.pcor %>% 
     filter(gene1 %in% setdiff(not.brain.ensg, brain.genes.ensg)) %>% 
     group_by(gene1) %>% 
     summarise(
         mean_bg = max((pcor[gene2 %in% setdiff(brain.genes.ensg, not.brain.ensg)]), na.rm = T),
         mean_nbg = max((pcor[gene2 %in% setdiff(not.brain.ensg, brain.genes.ensg)]), na.rm = T)
     )

cowplot::plot_grid( 
    ggplot(x, aes(mean_bg, mean_nbg)) + 
        geom_abline(intercept = 0, slope = 1, lty = 2, lwd = .5)+
        geom_smooth(method = 'lm', lwd = .5, color = 'grey20')+
        # coord_cartesian(xlim = c(0.05,0.15), ylim = c(0.05,0.15))+
      geom_point( alpha = .3 )+
        labs(title = 'brain genes', x = 'max  pcor\nbrain genes', y = 'max  pcor\nnon-brain genes'),
    ggplot(y, aes(mean_bg, mean_nbg)) + 
        geom_abline(intercept = 0, slope = 1, lty = 2, lwd = .5)+
        geom_smooth(method = 'lm', lwd = .5, color = 'grey20')+
        # coord_cartesian(xlim = c(0.05,0.15), ylim = c(0.05,0.15))+
      geom_point( alpha = .3 )+
        labs(title = 'non brain genes', x = 'max  pcor\nbrain genes', y = 'max  pcor\nnon-brain genes')
)
```


# Summary
```{r}

# specify gene lists
hpa.brain <- tissue.array %>% 
  filter(
    Tissue %in% brain.tissues, 
    Level %in% c('Low','Medium','High','Ascending','Descending'),
    Reliability %in% c('Enhanced','Supported','Approved') ) %>% 
  pull(Gene.name) %>% unique()

tad.deg <- scores %>% 
  filter(isScored_omics == 'Y', OmicsScore > 0) %>% 
  pull(GeneName) %>% unique()

seaad.expr <- seaad %>% 
  filter(mean > 1) %>% 
  pull(gene) %>% unique()

brain.genes <- union(hpa.brain, tad.deg) %>% union(., seaad.expr)

# pull NW stats based on filter
nw.stats <- tibble(  
  
  dir = c(
    'undirected'
    ,'directed'
    
    ,'undirected'
    ,'directed'
    
    ,'undirected'
    ,'directed'
    
    ,'undirected'
    ,'directed'
    
    ,'undirected'
    ,'directed'
    
    ,'undirected'
    ,'directed'
    
    ,'undirected'
    ,'directed'
    
    ), 
  
  filt = c(
    'none'
    ,'none'
    
    ,'edge_evidence > 1'
    ,'edge_evidence > 1'
    
    ,'HPA_brain'
    ,'HPA_brain'
    
    ,'omics_detect'
    ,'omics_detect'
    
    ,'seaAD_detect'
    ,'seaAD_detect'
    
    ,'all_expr'
    ,'all_expr'

    ,'expr+evidence'
    ,'expr+evidence'

        
    ),
  
  nV = c( 
    net.tbl %>% 
      graph_from_data_frame %>% V %>% length
    , net.tbl %>% 
      filter(interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% V %>% length

    , net.tbl %>% 
      filter(n_edge_evidence > 1) %>% 
      graph_from_data_frame %>% V %>% length
    , net.tbl %>% 
      filter(n_edge_evidence > 1, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% V %>% length

    , net.tbl %>% 
      filter(from %in% hpa.brain & to %in% hpa.brain) %>% 
      graph_from_data_frame %>% V %>% length
    , net.tbl %>% 
      filter(from %in% hpa.brain & to %in% hpa.brain, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% V %>% length
    
    , net.tbl %>% 
      filter(from %in% tad.deg & to %in% tad.deg) %>% 
      graph_from_data_frame %>% V %>% length
    , net.tbl %>% 
      filter(from %in% tad.deg & to %in% tad.deg, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% V %>% length
    
    , net.tbl %>% 
      filter(from %in% seaad.expr & to %in% seaad.expr) %>% 
      graph_from_data_frame %>% V %>% length
    , net.tbl %>% 
      filter(from %in% seaad.expr & to %in% seaad.expr, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% V %>% length
    
    , net.tbl %>% 
      filter(from %in% brain.genes & to %in% brain.genes) %>% 
      graph_from_data_frame %>% V %>% length
    , net.tbl %>% 
      filter(from %in% brain.genes & to %in% brain.genes, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% V %>% length
    
    , net.tbl %>% 
      filter(n_edge_evidence > 1,
             from %in% brain.genes & to %in% brain.genes) %>% 
      graph_from_data_frame %>% V %>% length
    , net.tbl %>% 
      filter(n_edge_evidence > 1,
             from %in% brain.genes & to %in% brain.genes, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% V %>% length
    
    ),
  
  nE = c( 
    net.tbl %>% 
      graph_from_data_frame %>% E %>% length
    , net.tbl %>% 
      filter(interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% E %>% length
    
    , net.tbl %>% 
      filter(n_edge_evidence > 1) %>% 
      graph_from_data_frame %>% E %>% length
    , net.tbl %>% 
      filter(n_edge_evidence > 1, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% E %>% length
    
    , net.tbl %>% 
      filter(from %in% hpa.brain & to %in% hpa.brain) %>% 
      graph_from_data_frame %>% E %>% length
    , net.tbl %>% 
      filter(from %in% hpa.brain & to %in% hpa.brain, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% E %>% length
    
    , net.tbl %>% 
      filter(from %in% tad.deg & to %in% tad.deg) %>% 
      graph_from_data_frame %>% E %>% length
    , net.tbl %>% 
      filter(from %in% tad.deg & to %in% tad.deg, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% E %>% length
    
    , net.tbl %>% 
      filter(from %in% seaad.expr & to %in% seaad.expr) %>% 
      graph_from_data_frame %>% E %>% length
    , net.tbl %>% 
      filter(from %in% seaad.expr & to %in% seaad.expr, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% E %>% length
    
    , net.tbl %>% 
      filter(from %in% brain.genes & to %in% brain.genes) %>% 
      graph_from_data_frame %>% E %>% length
    , net.tbl %>% 
      filter(from %in% brain.genes & to %in% brain.genes, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% E %>% length
    
    , net.tbl %>% 
      filter(n_edge_evidence > 1,
             from %in% brain.genes & to %in% brain.genes) %>% 
      graph_from_data_frame %>% E %>% length
    , net.tbl %>% 
      filter(n_edge_evidence > 1,
             from %in% brain.genes & to %in% brain.genes, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% E %>% length
    
    ),
  
  avg_path_length = c(
    net.tbl %>% 
      graph_from_data_frame %>% average.path.length()
    , net.tbl %>% 
      filter(interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% average.path.length(directed = T)
    
    , net.tbl %>% 
      filter(n_edge_evidence > 1) %>% 
      graph_from_data_frame %>% average.path.length()
    , net.tbl %>% 
      filter(n_edge_evidence > 1, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% average.path.length(directed = T)
    
    , net.tbl %>% 
      filter(from %in% hpa.brain & to %in% hpa.brain) %>% 
      graph_from_data_frame %>% average.path.length()
    , net.tbl %>% 
      filter(from %in% hpa.brain & to %in% hpa.brain, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% average.path.length(directed = T)
    
    , net.tbl %>% 
      filter(from %in% tad.deg & to %in% tad.deg) %>% 
      graph_from_data_frame %>% average.path.length()
    , net.tbl %>% 
      filter(from %in% tad.deg & to %in% tad.deg, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% average.path.length(directed = T)
    
    , net.tbl %>% 
      filter(from %in% seaad.expr & to %in% seaad.expr) %>% 
      graph_from_data_frame %>% average.path.length()
    , net.tbl %>% 
      filter(from %in% seaad.expr & to %in% seaad.expr, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% average.path.length(directed = T)

    , net.tbl %>% 
      filter(from %in% brain.genes & to %in% brain.genes) %>% 
      graph_from_data_frame %>% average.path.length()
    , net.tbl %>% 
      filter(from %in% brain.genes & to %in% brain.genes, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% average.path.length(directed = T)
    
    , net.tbl %>% 
      filter(n_edge_evidence > 1,
             from %in% brain.genes & to %in% brain.genes) %>% 
      graph_from_data_frame %>% average.path.length()
    , net.tbl %>% 
      filter(n_edge_evidence > 1,
             from %in% brain.genes & to %in% brain.genes, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% average.path.length(directed = T)    
  ),
  
  assortativity_coef = c(
    net.tbl %>% 
      graph_from_data_frame %>% assortativity(., types1 = V(.))
    , net.tbl %>% 
      filter(interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% assortativity(., types1 = V(.))
    
    , net.tbl %>% 
      filter(n_edge_evidence > 1) %>% 
      graph_from_data_frame %>% assortativity(., types1 = V(.))
    , net.tbl %>% 
      filter(n_edge_evidence > 1, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% assortativity(., types1 = V(.))
    
    , net.tbl %>% 
      filter(from %in% hpa.brain & to %in% hpa.brain) %>% 
      graph_from_data_frame %>% assortativity(., types1 = V(.))
    , net.tbl %>% 
      filter(from %in% hpa.brain & to %in% hpa.brain, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% assortativity(., types1 = V(.))
    
    , net.tbl %>% 
      filter(from %in% tad.deg & to %in% tad.deg) %>% 
      graph_from_data_frame %>% assortativity(., types1 = V(.))
    , net.tbl %>% 
      filter(from %in% tad.deg & to %in% tad.deg, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% assortativity(., types1 = V(.))
    
    , net.tbl %>% 
      filter(from %in% seaad.expr & to %in% seaad.expr) %>% 
      graph_from_data_frame(directed=T) %>% assortativity(., types1 = V(.))
    , net.tbl %>% 
      filter(from %in% seaad.expr & to %in% seaad.expr, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% assortativity(., types1 = V(.))
    
    
    , net.tbl %>% 
      filter(from %in% brain.genes & to %in% brain.genes) %>% 
      graph_from_data_frame %>% assortativity(., types1 = V(.))
    , net.tbl %>% 
      filter(from %in% brain.genes & to %in% brain.genes, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame %>% assortativity(., types1 = V(.))
    
    
    , net.tbl %>% 
      filter(n_edge_evidence > 1,
             from %in% brain.genes & to %in% brain.genes) %>% 
      graph_from_data_frame %>% assortativity(., types1 = V(.))
    , net.tbl %>% 
      filter(n_edge_evidence > 1,
             from %in% brain.genes & to %in% brain.genes, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame %>% assortativity(., types1 = V(.))
  ),
  
  connected_components = c(
    net.tbl %>% 
      graph_from_data_frame %>% no.clusters()
    , net.tbl %>% 
      filter(interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% no.clusters()
    
    , net.tbl %>% 
      filter(n_edge_evidence > 1) %>% 
      graph_from_data_frame %>% no.clusters()
    , net.tbl %>% 
      filter(n_edge_evidence > 1, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% no.clusters()
    
    , net.tbl %>% 
      filter(from %in% hpa.brain & to %in% hpa.brain) %>% 
      graph_from_data_frame %>% no.clusters()
    , net.tbl %>% 
      filter(from %in% hpa.brain & to %in% hpa.brain, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% no.clusters()
    
    , net.tbl %>% 
      filter(from %in% tad.deg & to %in% tad.deg) %>% 
      graph_from_data_frame %>% no.clusters()
    , net.tbl %>% 
      filter(from %in% tad.deg & to %in% tad.deg, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% no.clusters()
    
    , net.tbl %>% 
      filter(from %in% seaad.expr & to %in% seaad.expr) %>% 
      graph_from_data_frame %>% no.clusters()
    , net.tbl %>% 
      filter(from %in% seaad.expr & to %in% seaad.expr, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% no.clusters()
    
    , net.tbl %>% 
      filter(from %in% brain.genes & to %in% brain.genes) %>% 
      graph_from_data_frame %>% no.clusters()
    , net.tbl %>% 
      filter(from %in% brain.genes & to %in% brain.genes, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% no.clusters()
    
    , net.tbl %>% 
      filter(n_edge_evidence > 1,
             from %in% brain.genes & to %in% brain.genes) %>% 
      graph_from_data_frame %>% no.clusters()
    , net.tbl %>% 
      filter(n_edge_evidence > 1,
             from %in% brain.genes & to %in% brain.genes, 
             interaction %in% directed_edge_types) %>% 
      graph_from_data_frame(directed=T) %>% no.clusters()
  )
  
)

```

```{r, fig.width=10, fig.height=8}
nw.stats %>% 
  pivot_longer(cols = c(nV,nE,avg_path_length,assortativity_coef,connected_components), names_to = 'prop', values_to = 'val') %>% 
  mutate(prop = factor(prop, levels = c('nV','nE', 'avg_path_length','assortativity_coef','connected_components'))
         , dir = factor(dir, levels = c('undirected','directed'))
         , filt = factor(filt, levels = c('none','edge_evidence > 1','HPA_brain','omics_detect','seaAD_detect', 
                                          'all_expr','expr+evidence'))
         ) %>% 
  ggplot(aes(filt, val, fill = dir)) +
  geom_bar(stat = 'identity', position = 'dodge')+
  theme(legend.position = 'top',
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))+
  facet_wrap(~prop, scales = 'free_y', ncol = 2)
```
# Session
```{r}
sessionInfo()
```

